### 2016-05-02 draft.tex
Initial commit

\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}
\modulolinenumbers[5]

\usepackage{amsmath,amsthm,amssymb,mathrsfs}

\journal{Journal of Combinatorial Theory, Series A}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

%% Ticketing System
\usepackage{etoolbox}
\usepackage{xparse}
\NewDocumentCommand{\openTickets}{ > {\SplitList {,} } m }{\ProcessList{#1}{\BoolInit}}
\newcommand{\BoolInit}[1]{\providetoggle{#1}\toggletrue{#1}}
\newcommand{\todo}[2]{%
  \providetoggle{#1}%
    \iftoggle{#1}{%
    {\color{red}#2}%
    }{#2}%
}

%% Ticket list
\openTickets{Manuel:convHull,Manuel:wlog,Manuel:invertability:assumption,Mark:log:bounds,Mark:proof:cor15,Manuel:proof:rewritten,Manuel:generic}

\providecommand{\norm}[1]{\left\|#1\right\|}
\providecommand{\abs}[1]{\left|#1\right|}
\providecommand{\span}{\text{span}}
\providecommand{\conv}{\text{conv}}
\providecommand{\epi}{\text{epi}}
\providecommand{\rk}[1]{\text{rank}\left(#1\right)}

\newcommand*{\Resize}[1]{\resizebox{\columnwidth}{!}{$#1$}}

\newcounter{thmcount}
\renewcommand{\thethmcount}{\arabic{thmcount}}
\renewcommand{\theequation}{\arabic{section}.\arabic{equation}}
\renewcommand{\thefigure}{\arabic{section}.\arabic{figure}}

\newtheorem{thm}[thmcount]{Theorem}
\newtheorem{cor}[thmcount]{Corollary}
\newtheorem{prop}[thmcount]{Proposition}

\theoremstyle{remark}
\newtheorem{rem}[thmcount]{Remark}

\theoremstyle{definition}
\newtheorem{defi}[thmcount]{Definition}
\newtheorem{alg}[thmcount]{Algorithm}

\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
\DeclareFontShape{U}{mathx}{m}{n}{
      <5> <6> <7> <8> <9> <10> gen * mathx
      <10.95> mathx10 <12> <14.4> <17.28> <20.74> <24.88> mathx12
      }{}
\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
\DeclareFontSubstitution{U}{mathx}{m}{n}
\DeclareMathSymbol{\temp}{\mathbin}{mathx}{'341}
\newcommand{\bigominus}{\raisebox{10pt}{$\temp$}}

% \newcommand{\todo}[1]{\textcolor{blue}{#1}}
\newcommand{\highlight}[1]{\textcolor{red}{#1}}

\begin{document}

\begin{frontmatter}

\title{Operations on Parametrised Polytopes\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

%% or include affiliations in footnotes:
\author{Rainer M. Schaich}
\ead{rainer.schaich@eng.ox.ac.uk}

\author{Mark Cannon\corref{correspondingauthor}}
\ead{mark.cannon@eng.ox.ac.uk}

\cortext[correspondingauthor]{Corresponding author}

\address{Department of Engineering Science, University of Oxford, Parks Road, OX1 3PJ, Oxford}

\begin{abstract}
The abstract goes here.
\end{abstract}

\begin{keyword}
keyword one \sep keyword two
\end{keyword}

\end{frontmatter}

\linenumbers

\section{Introduction}

\section{Preliminaries}

\section{Parametric Convexity}

In this section we define the property of \emph{parametric convexity} in the context of set valued maps (so called point-to-set maps, see e.g.~\cite{Hogan:1973}). This property is then used 
to demonstrate the convexity of a generalised Pontryagin difference. 
%
In this section we refer to sets $Y\subseteq\mathbb R^d$ and $Z\subseteq\mathbb R^n$, and we denote the power set of $Z$ as $\mathscr P(Z)$.
%
\begin{defi}[Parametric Convexity]\label{def:parametric:convexity}
Let $\mathcal W:Y\rightarrow \mathscr P(Z)$, where $Y\ni p\mapsto \mathcal W(p) \subset Z$, be a continuous point-to-set map. The map $\mathcal W$ is called \emph{parametrically convex} if it satisfies
%
  \begin{equation}\label{eq:def:parametrically:convex}
  \mathcal W(\lambda p_1 + (1-\lambda)p_2)\subseteq\lambda \mathcal W(p_1) \oplus (1-\lambda) \mathcal W(p_2)
  \end{equation}
%
  for all $p_1,p_2\in Y$ and $\lambda\in (0,1)$.
\end{defi}
%
Notice that Definition~\ref{def:parametric:convexity} does not require convexity of~$\mathcal W(p)$. However, we will only consider maps~$\mathcal W$ for which $\mathcal W(p)$ is convex for all fixed $p\in Y$.

\subsection{Properties of Parametrically Convex Maps}\label{ssec:properties:of:p:convex:maps}
%
We begin by introducing an equivalent characterisation of parametric convexity that provides an insight into the geometrical properties of 
point-to-set maps satisfying~\eqref{eq:def:parametrically:convex}.
This is based on a description of parametric convexity in terms of conditions on the graph of a point-to-set map.
%
\begin{defi}\label{def:graph:of:map}
Let $\mathcal W:Y\rightarrow \mathscr P(Z)$ be a continuous point-to-set map
such that $\mathcal W(p)$ is convex for all $p\in Y$, then 
%
\[
\mathscr G(\mathcal W) = \{(p,z) \in\mathbb R^{d+n}: z\in\mathcal W(p)\}
\]
%
denotes the \emph{graph} of $\mathcal W$,
%
\begin{equation*}  
\text{int}(\mathscr G(\mathcal W)) = \{(p,z) \in\mathbb R^{d+n} : \exists \epsilon>0, \, z+\epsilon \zeta\in \mathcal W(p) \forall \zeta\in\mathbb R^n\}
\end{equation*}
%
is its \emph{interior}, and
%
\[
  \partial \mathscr G(\mathcal W) = \mathscr G(\mathcal W)\setminus \textup{int}(\mathscr G(\mathcal W))
\]
%
denotes its \emph{boundary};
%
furthermore for any $(p,z)\in\partial\mathscr G(\mathcal W)$ the \emph{orientation cone} is defined as 
%
\[
  \mathcal N\mathcal W(p,z) = \{\zeta \in\mathbb R^n: z+\epsilon \zeta \not\in \mathcal W(p)\; \forall \epsilon>0\} .
\]
%
\end{defi}
%
\begin{rem}
%
Note that the orientation cone is defined in the space of the
\emph{set variable} $z$ rather than \emph{graph variable} $(p,z)$.
%
Furthermore, the orientation cone contains all directions that 
point out of the set $\mathcal W(p)$ and hence all linear combinations thereof.
%
\end{rem}
%
The central idea connecting parametric convexity of a set valued map $\mathcal W$ with properties of its graph $\mathscr G(\mathcal W)$ is stated next.
%
\begin{thm}\label{thm:p:convexity:graph}
The map $\mathcal W$ is parametrically convex iff for all $(p_1,z_1), (p_2,z_2)\in\partial\mathscr G(\mathcal W)$
with $p_1\neq p_2$ and $\mathcal N\mathcal W(p_1,z_1)\cap\mathcal N\mathcal W(p_2,z_2)\neq\emptyset$,
%
\begin{equation}\label{eq:graph:def:p:convexity}
\lambda (p_1,z_1) + (1-\lambda) (p_2,z_2) \not\in\textup{int} (\mathscr G(\mathcal W))
\end{equation}
%
holds for all $\lambda\in(0,1)$.
%
\end{thm}
%
\begin{proof}
%
Assume~\eqref{eq:graph:def:p:convexity} holds for $(p_1,z_1),(p_2,z_2)\in\partial\mathscr G(\mathcal W)$.
%
Then the extension of the definition of the Minkowski functional (see e.g.~\cite{Rudin:91}) to the graph $\mathscr G(\mathcal W)$,
\[
\mu_{\mathscr G(\mathcal W)} \bigl(
\mathcal W(p), z \bigr)
:= \min_\mu \{\mu \geq 0 : z \in \mu \mathcal W(p)\},
\]
yields $\mu_{\mathscr G(\mathcal W)}\left(\mathcal W(\lambda p_1 + (1-\lambda)p_2),\lambda z_1+(1-\lambda)z_2\right)\geq1$ for all $\lambda\in(0,1)$. Therefore $\lambda z_1 + (1-\lambda) z_2$
lies either outside the set $\mathcal W(\lambda p_1+(1-\lambda)p_2)$ or on its boundary for all $\lambda\in(0,1)$, and hence the set of all possible interpolation points 
%
\[
\begin{split}
  \lambda \mathcal W(p_1)\oplus (1-\lambda)\mathcal W(p_2) = \{&z : z=\lambda z_1 + (1-\lambda) z_2,\\ &z_1\in\mathcal  W(p_1),\, z_2\in\mathcal W(p_2)\}
\end{split}
\]
%
contains the set $\mathcal W(\lambda p_1 + (1-\lambda)p_2)$ for all $\lambda\in(0,1)$.
%

Now suppose that $\mathcal W$ is parametrically convex and that~\eqref{eq:graph:def:p:convexity} is not satisfied for 
some $(p_1,z_1),(p_2,z_2)\in\partial\mathscr G(\mathcal W)$ with $\mathcal N\mathcal W(p_1,z_1)\cap\mathcal 
N\mathcal W(p_2,z_2)\neq\emptyset$, 
%
i.e.~that there exists $\epsilon>0$ such that the ball
$B_\epsilon(\lambda z_1 + (1-\lambda)z_2 )$
is contained in $\mathcal W(\lambda p_1 + (1-\lambda)p_2)$ for some $\lambda \in (0,1)$.
%
But this implies that $\lambda z_1 + (1-\lambda) z_2 + \epsilon\zeta \in \mathcal W(\lambda p_1+(1-\lambda)p_2)$  for all $\zeta\in\mathbb R^n$ such that $\|\zeta\| = 1$, whereas
$\mathcal N\mathcal W(p_1,z_1)\cap\mathcal N\mathcal W(p_2,z_2)\neq\emptyset$ implies that there exists 
$\zeta \in\mathcal N\mathcal W(p_1,z_1)\cap\mathcal N\mathcal W(p_2,z_2)$ which cannot be represented as
$\zeta =\lambda \zeta_1+
(1-\lambda)\zeta_2$
with $z_1 + \epsilon \zeta_1\in\mathcal W(p_1)$ and $z_2  + \epsilon \zeta_2\in\mathcal W(p_2)$.
%
It follows that $\mathcal W$ cannot be parametrically convex in this case.
\end{proof}
%

Condition~\eqref{eq:graph:def:p:convexity} requires that the graph $\mathscr G(\mathcal W)$ is non-convex.
%
Indeed it is shown next that if $\mathscr G(\mathcal W)$ is strictly convex at any $(p,z)\in\partial \mathscr G (\mathcal W)$, then~\eqref{eq:graph:def:p:convexity} is violated and 
$\mathcal W$ cannot be parametrically convex.

%
\begin{cor}
%
Let $\mathcal W(p):=\{z\in\mathbb R^n: r(p,z)\leq0\}$ define a point-to-set
map where 
$r: \mathbb R^d \times\mathbb R^n \rightarrow \mathbb R$, $(p,z)\mapsto r(p,z)$ is a continuous function which is convex in $z \in\mathbb R^n$, 
then $\mathcal W$ is parametrically
convex iff the function $r$ is concave in $p\in\mathbb R^d$.
%
\end{cor}
%
\begin{proof}
First note that $r(p,z)$ is assumed to be a convex function of $z$ for any given value of $p$ so that $\mathcal W(p)$ is a convex set for each $p\in\mathbb R^d$.
%
Suppose that, for given $z\in\mathbb R^n$, $r(p,z)$ is a non-concave (i.e. 
strictly convex) function of $p$, for all $p$ in some region $\Omega\subseteq\mathbb R^d$. 
%
Then any convex subset $\mathcal C\subseteq\Omega$ will be such that $\mathscr 
G(\mathcal W)\vert_{\mathcal C}$ is a convex set.
%
Furthermore, for any $(p_1,z_1),(p_2,z_2)\in \partial\mathscr G(\mathcal W)\vert_{\mathcal C}$ we have
$\lambda (p_1,z_1) + (1-\lambda) (p_2,z_2) \in\mathrm{int} (\mathscr G(\mathcal W))\vert_{\mathcal C}$ for all $\lambda\in(0,1)$ since
$\mathscr G(\mathcal W)\vert_{\mathcal C}$ is strictly convex in $p$.
%
Hence~\eqref{eq:graph:def:p:convexity} is violated in this case, implying that $r(p,z)$ cannot be a non-concave function of $p$ in any non-empty set $\Omega$ if $\mathcal W$ is parametrically convex. 
%
Conversely, if $r(p,z)$ is concave in $p$ for all $p\in\mathbb R^d$, then the conditions of Theorem~\ref{thm:p:convexity:graph} necessarily hold.
\end{proof}
%
It is useful to be able to perform set certain set operations on point-to-set maps, therefore we define the parametric Pontryagin difference:
%
\begin{defi}[Parametric Pontryagin Difference]\label{def:parametric:pontryagin:difference}
  Let $S\subseteq Z$ and let $\mathcal W:Z\to\mathscr P(Z)$ be a continuous point-to-set map such that
  $\mathcal W(p)$ is convex for all $p\in Z$, then the \emph{parametric Pontryagin difference} 
  $S\ominus \mathcal W(S)$ is defined
%
\begin{equation}\label{eq:definition:parametric:pontryagin:difference}
    S\ominus \mathcal W(S) = \bigl\{z\in Z: \{z\} \oplus \mathcal W(z)\subseteq S\bigr\}.
  \end{equation}
%
\end{defi}
%
By a slight abuse of notation, $\mathcal{W}(S)$ is used in~(\ref{eq:definition:parametric:pontryagin:difference}) to indicate that $\mathcal{W}$ is a point-to-set map and that $S\ominus\mathcal{W}(S)$ denotes the parametric Pontryagin difference, rather than a fixed set and the conventional Pontryagin difference. 
%
In fact the definition~(\ref{eq:definition:parametric:pontryagin:difference}) indicates that $S\ominus \mathcal{W}(S)$ only depends on the value of $\mathcal{W}(z)$ on a subset of $S$. 
%
%
For the parametric Pontryagin difference of a convex set and a parametrically convex map we 
have the following result.
%
\begin{thm}\label{thm:convexity:of:pontryagin:difference}
Let $\mathcal W: Z\rightarrow\mathscr P(Z)$ be a given point-to-set map, then the parametric Pontryagin difference $S \ominus \mathcal W(S)$ is convex for every convex $S\subseteq Z$ if and only if $\mathcal W$ is parametrically convex.
\end{thm}
% \begin{thm}\label{thm:convexity:of:pontryagin:difference}
%   Let $S\subseteq X$ be a convex set and let $\mathcal W:X\rightarrow\mathscr P(X)$ be a parametrically convex point-to-set
%   map such that $\mathcal W(p)$ is convex for all $p\in X$, then $S\ominus \mathcal W(S)$ is convex.
% \end{thm}
%
\begin{proof}
To prove convexity of $S^\prime =  S\ominus \mathcal W( S)$ when $\mathcal W$ is parametrically convex we pick any $z_1,z_2\in S^\prime$, then
the definition of the parametric Pontryagin difference gives
\begin{equation}
  \{z_i\} \oplus \mathcal W(z_i) \subseteq S,\; i=1,2 
\end{equation}
%
and it can be verified that $S^\prime$ is convex by showing that line segments between all possible $z_1$ and $z_2$ are subsets of $S^\prime$. In particular, for all $\lambda \in (0,1)$ we have
\begin{align*}
  \{ \lambda z_1 + (1-&\lambda)z_2
  \}\oplus \mathcal W\left( \lambda z_1 + (1-\lambda)z_2\right)\\
  \subseteq&\left\{ \lambda z_1 + (1-\lambda)z_2
  \right\}\oplus \lambda \mathcal W(z_1) \oplus (1-\lambda)
  \mathcal W(z_2)\\
 = &\lambda\underbrace{(\{z_1\}\oplus \mathcal W(z_1))}_{\subseteq S}\oplus
  (1-\lambda)\underbrace{(\{z_2\}\oplus \mathcal W(z_2))}_{\subseteq S}\\
  \subseteq& S
\end{align*}
%
(where the last inclusion results from the convexity of $\mathcal S$), and it follows that
$\lambda z_1 + (1-\lambda) z_2 \in S^\prime$ for all $\lambda \in (0,1)$. 
%the property, which follows from Definition~\ref{def:parametric:pontryagin:difference}, that $S\subseteq Z$.
%

To demonstrate that parametric convexity of $\mathcal W$ is necessary for convexity of $S\ominus \mathcal W(S)$, suppose that condition~(\ref{eq:def:parametrically:convex}) does not hold and choose $z_1,z_2$ so that $\mathcal W(\lambda z_1 + (1-\lambda) z_2) \not\subseteq \lambda \mathcal W(z_1) \oplus (1-\lambda) \mathcal W (z_2)$ for some $\lambda \in (0,1)$. Then there exists a value of $\lambda\in(0,1)$ such that
\begin{align*}
  \{ \lambda z_1 + (1-&\lambda)z_2
  \}\oplus \mathcal W\left( \lambda z_1 + (1-\lambda)z_2\right)\\
  % \not\subseteq&\left\{ \lambda z_1 + (1-\lambda)z_2
  % \right\}\oplus \lambda \mathcal W(z_1) \oplus (1-\lambda)
  % \mathcal W(z_2)\\
 \not\subseteq &\lambda\bigl(\{z_1\}\oplus \mathcal W(z_1)\bigr)\oplus
  (1-\lambda)\bigl(\{z_2\}\oplus \mathcal W(z_2)\bigr) .
\end{align*}
Therefore if $S$ is a convex polyhedron constructed so that $\{z_1\}\oplus\mathcal W(z_1)$ and $\{z_2\}\oplus\mathcal W(z_2)$ contain points lying on the same facet of $S$ (this is always possible if $S^\prime=S\ominus \mathcal W(S)$ has a non-empty interior), then there exists $\lambda \in (0,1)$ such that $\lambda z_1 + (1-\lambda) z_2 \notin S^\prime$.
%
\end{proof}
%
Theorem~\ref{thm:convexity:of:pontryagin:difference} provides necessary and sufficient conditions for convexity of the parametric Pontryagin difference. Later we will show that the parametric Pontryagin difference between a polyhedral set and a piecewise affine polytopic parametric set is itself polyhedral.
%
%
%
%
\section{Polyhedral maps}
%
%
%
%
In this section we discuss point-to-set maps~$\mathcal W$ for which every realisation~$\mathcal W(p)$ is polyhedral and in particular
we study~$\mathcal W$ which depend on $p\in Y$ in a piecewise affine way. 
%
To the authors' best knowledge the the literature on piecewise polyhedral sets is limited, we refer to~\cite{Finzel:2000}, however properties of general set-valued maps are known and applicable, see e.g.~\cite{Aubin:1990}.

\begin{cor}\label{thm:polytopic:set:not:p:convex}
The polytopic parametric set valued map $\mathcal W(p):=\{z: a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\}$
is not parametrically convex for any non-zero matrix $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$.
\end{cor}
%
\begin{proof}
If $B\neq 0$, then the graph
%
\begin{equation*}
	\mathscr G(\mathcal W) = \{(p,z):a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\} ,
\end{equation*}
%
is convex and violates the conditions of Theorem~\ref{thm:p:convexity:graph}.
\end{proof}
%
\begin{cor}\label{thm:p:convexity:PWA:set:constant:num:verts}
The generic piecewise affine polytopic parametric point-to-set valued map 
%
\begin{equation}\label{eq:definition:PWA:polytopic:set:general}
  \mathcal W(p) := \Bigl\{z\in\mathbb R^n: a_i z \leq \max_{k}\{b_{i,k} + c_{i,k}p\} \; \forall i\in\mathbb N_m \Bigr\}
\end{equation}
%
is parametrically convex iff the number of vertices, $v_\kappa(p)$, and rays, $r_\eta(p)$, of~$\mathcal W(p)$ is constant for almost all $p\in Y$.
\end{cor}
%
\begin{proof}
For clarity this proof is divided in 3 parts:
\begin{enumerate}
\item Note that $h_i(p) = \max_{k} \{b_{i,k} + c_{i,k}p\}$ is a multi-parametric linear program (mpLP),
the solution of which is a piecewise affine function $h_i(p) = b_{i,k^\ast_i} + c_{i,k^\ast_i}p$, where $k^\ast_i(p)$ is piecewise constant on a polyhedral complex, see e.g.~\cite{spjotvold:2005}.
%
This means that there exists a finite partition of $Y\subseteq\mathbb R^d$ into convex polyhedra 
$\mathcal P_j$ such that $\bigcup_{j\in\mathbb N_t} \mathcal P_j = Y$ and 
${\bf{k}}^\ast(p) = (k_1^\ast(p),\dots,k_m^\ast(p))$ is constant for all $p \in \mathcal P_j$.
%
Hence the graph $\mathscr G(\mathcal W)$ is given by a finite union of polyhedra
%
\begin{equation*}
  \mathscr G(\mathcal W) = \bigcup_{j\in\mathbb N_t} \left\{z\in\mathbb R^n: a_i z \leq b_{i,k_i^\ast} + c_{i,k_i^\ast}p \; \forall i \in\mathbb N_m \right\}\bigr\vert_{\mathcal P_{j}}
\end{equation*}
%
and it follows that if the number of vertices or rays changes within any partition $\mathcal P_j$ then $\mathscr
G(\mathcal W)\vert_{\mathcal P_j}$ is a strictly convex polyhedron and Corollary~\ref{thm:polytopic:set:not:p:convex} applies.
%
\item Our attention is therefore concentrated on the boundaries of partitions $\mathcal P_j$, at points $p\in\mathcal P_{j_1} \cap \mathcal P_{j_2}$ where 
%some mpLP changes its solution, i.e. 
$\bigl(b_{i,k_i^\ast} + c_{i,k_{j_1}^\ast} p\bigr)\bigr\rvert_{\mathcal P_{j_1}} = 
\bigl(b_{i,k_{j_2}^\ast} + c_{i,k_{j_2}^\ast} p\bigr)\bigr\rvert_{\mathcal P_{j_2}}$.
%
Notice that a vertex $v_\kappa(p)$ is defined by \emph{active} and \emph{inactive} inequalities, namely $\mathcal A_\kappa(p)$ and
$\mathcal I_\kappa(p) = \mathbb N_m
%\{1,\dots,m\}
\setminus\mathcal A_\kappa(p)$ respectively, where
%
\begin{equation*}\begin{split}
  a_i v_\kappa(p) &= b_{i,k_i^\ast} + c_{i,k_i^\ast} p \quad\forall i\in\mathcal A_\kappa(p)\\
  a_i v_\kappa(p) &< b_{i,k_i^\ast} + c_{i,k_i^\ast} p \quad\forall i\in\mathcal I_\kappa(p) .
\end{split}\end{equation*}
%
Since $\mathcal W(p)$ is assumed to be generic, it has to be generic for almost every~$p\in Y$, which means it is \emph{simple}, i.e. each vertex is defined by exactly $n$ active inequalities $\abs{\mathcal A_\kappa(p)}=n$ for all $p\in Y$ and all $\kappa$.
%
Furthermore, since~$\mathcal W(p)$ is generic, only one element of ${\bf{k}}^\ast\vert_{\mathcal P_{j_1}}$
and ${\bf{k}}^\ast\vert_{\mathcal P_{j_2}}$ differs, that is, there exists a single index $i\in\mathbb N_m$ such that $k_i^\ast\vert_{\mathcal P_{j_1}}\neq k_i^\ast\vert_{\mathcal P_{j_2}}$.
%
Hence, in order for the number of vertices to change, there must be a hyperplane $fp=g$, such that the number of vertices for $fp \leq g$ is 
$N$ and for $fp>g$ is at least $N+1$.
%
It follows from the previous discussion that $\{p:fp=g\} = \textup{aff}\{\mathcal P_{j_1}\cap\mathcal P_{j_2}\}$ for some $j_1\neq j_2$.
%
In order for vertices $v_{\kappa_1}(p)$ and $v_{\kappa_2}(p)$ to merge, the index sets $\mathcal A_{\kappa_1}(p)$ and $\mathcal A_{\kappa_2}(p)$ have to differ by only one 
element, i.e.~$\mathcal A_{\kappa_1}(p) = \mathcal J\cup \{s\}$ and $\mathcal A_{\kappa_2}(p) = \mathcal J\cup\{u\}$ if $fp>g$.
%
Furthermore, for $p$ such that $fp\leq g$ we have $v_{\kappa_1}(p)=v_{\kappa_2}(p)$, implying that $\mathcal A_{\kappa_1}(p) = 
\mathcal A_{\kappa_2}(p)$.
%
Since only one change in the active index set is considered (due to non-degeneracy assumptions), we must have
$\mathcal A_{\kappa_1}(p) = \mathcal A_{\kappa_2}(p) = \mathcal J \cup \{s,u\}$.
%
Hence on the hyperplane $fp=g$, both the maximising index ${\bf{k}}^\ast(p)$ and the active index sets $\mathcal A_{\kappa_1}(p)$ 
and $\mathcal A_{\kappa_2}(p)$ must change, which implies that the problem is degenerate.
%
\item In order for a degenerate graph $\mathscr G(\mathcal W)$ to be parametrically convex, the vertices $v_{\kappa_1}(p)$ and $v_{\kappa_2}(p)$ must be identical for $fp\leq g$, and in particular their dependence on $p$ has to be identical.
%
This can be expressed using the implicit function theorem as follows
%
\begin{align*}
  \frac{d}{dp}\left(  {\bf{a}}_{\mathcal J\cup \{s\}} v_{\kappa_1}(p) - {\bf{b}}_{\mathcal J\cup \{s\}} - 
  {\bf{c}}_{\mathcal J\cup \{s\},{\bf{k}}^\ast} p\right) &= 0\\
  \frac{d}{dp}\left(  {\bf{a}}_{\mathcal J\cup \{u\}} v_{\kappa_2}(p) - {\bf{b}}_{\mathcal J\cup \{u\}} - 
  {\bf{c}}_{\mathcal J\cup \{u\},{\bf{k}}^\ast} p\right) &= 0
\end{align*}
%
implies
\begin{align*}
  {\bf{a}}_{\mathcal J\cup \{s\}} \frac{dv_{\kappa}}{dp} &= {\bf{c}}_{\mathcal J\cup \{s\},{\bf{k}}^\ast}\\
  {\bf{a}}_{\mathcal J\cup \{u\}} \frac{dv_{\kappa}}{dp} &= {\bf{c}}_{\mathcal J\cup \{u\},{\bf{k}}^\ast}
\end{align*}
%
and since we can assume that the inequalities are non-redundant for some right hand side, we find that 
%
\begin{equation}\label{eq:derivative:condition:on:index:sets}
  \frac{dv_\kappa}{dp} = {\bf{a}}_{\mathcal J\cup \{s\}}^{-1}{\bf{c}}_{\mathcal J\cup \{s\},{\bf{k}}^\ast} = 
  {\bf{a}}_{\mathcal J\cup \{u\}}^{-1}{\bf{c}}_{\mathcal J\cup \{u\},{\bf{k}}^\ast}
\end{equation}
%
has to hold for the degenerate graph to remain parametrically convex.
%
To complete the proof we note that~\eqref{eq:derivative:condition:on:index:sets} is a degenerate condition, in the sense that an arbitrarily small perturbation will result in $v_{\kappa_1}(p) \neq v_{\kappa_2}(p)$, and we therefore disregard this possibility.
\end{enumerate}
\vskip-1.15\baselineskip
\end{proof}
%
It is worth pointing out that Corollary~\ref{thm:p:convexity:PWA:set:constant:num:verts} can be reformulated in a numerically helpful way:
%
\begin{cor}\label{thm:combinatorical:equivalence:alternative}
The generic set~$\mathcal W(p)$ defined by~\eqref{eq:definition:PWA:polytopic:set:general} is parametrically convex if and only if, it is combinatorially equivalent for any $p_1,p_2\in Y\subseteq\mathbb R^d$ almost everywhere, i.e. $\mathcal W(p_1)\cong\mathcal W(p_2)$.
\end{cor}
%
\begin{proof}
Two polyhedra are combinatorially equivalent if there exists a bijection between all their faces which preserves the inclusion, see e.g.~\cite{Ziegler:1995}.
%
It is clear that as long as all complexes $\mathcal A_\kappa(p)=\mathcal A_\kappa$ are constant all faces of $\mathcal W(p)$ are defined as intersections of the same set of half spaces.
%
Although the shape of~$\mathcal W(p)$ might change its combinatorial structure does not, furthermore the combinatorial structure of $\mathcal W(p)$ is not affected by changes of the right hand side.
%
The \emph{Perles' Conjecture}, which was proven e.g. in~\cite{Kalai:1988}, states that the combinatorial structure of a simple polytope is uniquely determined by its graph, that is, as long as the graph of~$\mathcal W(p)$ remains unchanged so does its combinatorial structure.
%
The graph of a polytope is given by the vertices and the edges of a polytope, since we have that the number of vertices remains unchanged throughout~$Y$ for $\mathcal W(p)$ the graph $G(\mathcal W(p))$ has to have a constant number of vertices.
%
This is only possible if it is constant itself or it abruptly changes multiple edges, however changing multiple edges involves changing multiple active sets which is a degenerate case.
%
Notice that this result only applies to sets with full measure, where $\mathcal W(p)$ is non-degenerate.
%
It is possible that there exist zero-measure sets (points, lines, $n-1$-hyperplanes) in~$Y$ where $\mathcal W$ becomes singular, meaning not simple
and vertices may merge, however due to the fact that for parameters outside such sets the combinatorial structure is fixed, we can find a  continuous selection through these sets, in any sense we like.
%
This means in particular that we ignore the fact that locally $v_{\kappa_1}=v_{\kappa_2}$ and use a locally redundant representation $\mathcal W(p) = \conv_\kappa\{v_\kappa(p)\}$.
\end{proof}
%
This allows for efficient numerical treatment, since we know how the vertices are defined~$\mathcal A_\kappa = const.$.

In order to determine the Pontryagin difference between two sets one constructs the boundary of the Pontryagin difference. 
%
For this let $S = \{x\in\mathbb R^n:\Lambda_i x\leq \lambda_i,i\in\mathbb N_q\}$ and let $\mathcal W$ be defined by~\eqref{eq:definition:PWA:polytopic:set:general} satisfying Corollary~\ref{thm:p:convexity:PWA:set:constant:num:verts} and let $\mathcal W(x) = \conv_{i\in\mathbb N_v}\{v_i(x)\}\oplus\text{cone}_{i\in\mathbb N_r}\{r_i(x)\}$ be its V-representation.
%
Each inequality of $S$ must be satisfied for all admissible realisations $w\in\mathcal W(x)$ , that is:
%
\begin{equation*}\begin{split}
	\Lambda_i(x+w) &\overset{!}{\leq}\lambda_i\; \forall i\in\mathbb N_q, w\in\mathcal W(x)\\
	\Lambda_i x + \underbrace{\max_{w\in\mathcal W(x)} \Lambda_i w}_{(\dagger)} &\overset{!}{\leq} \lambda_i\; \forall i\in\mathbb N_q
\end{split}\end{equation*}
%
The term~$(\dagger)$ is mpLP and its solution is attained on an extremal of~$\mathcal W(x)$, i.e. on one of the vertices or rays $v_i(x)$, $r_i(x)$.
%
Solving the mpLP is not necessary, due to Corollary~\ref{thm:combinatorical:equivalence:alternative} we know that every vertex and ray is generated by a fixed linear map~($a_i v_\kappa(x) = b_{i,k^\ast_i} + c_{i,k^\ast_i}x$ for~$i\in\mathcal A_\kappa$).
%
Therefore instead of solving~$(\dagger)$ we simply replace it with all possible vertices and rays and perform a regular inequality reduction:
%
\begin{equation*}
	S\ominus\mathcal W(S) = \{x\in\mathbb R^n : \Lambda_i (x + v_j/r_j(x) ) \leq \lambda_i \; \forall i\in\mathbb N_q,j\in\mathbb N_{v/r}\}.
\end{equation*}
%
Since~$v_j(x)$ and~$r_j(x)$ are piecewise affine in~$x$, the set~$S\ominus\mathcal W(S)$ is a polyhedral set and has the description H-representation $S\ominus\mathcal W(S)=\{x\in\mathbb R^n:\Gamma_i x\leq \gamma_i\;i\in\mathbb N_u\}$.

\section{Computational Methods}
%
%
%
In the previous sections we have derived that for the Pontryagin difference between any convex set $S$ and a point-to-set map~$\mathcal W$ to be convex itself we require the parametric convexity property for~$\mathcal W$.
%
We have also seen that set-valued maps with polyhedral realisations $\mathcal W(p)$ the number of vertices and rays must not change throughout the parameter space~$Y$.
%
This might seem like a computationally challenging endeavour, however we will see that it suffices to solve a finite number of calculations.
%
For notational convenience let $d_i(p) = \max_k\{b_{i,k}+c_{i,k}p\}$ denote the right hand side of~\eqref{eq:definition:PWA:polytopic:set:general}, i.e. $\mathcal W(p) = \{z\in\mathbb R^d: a_i z\leq d_i(p)\;\forall i\in\mathbb N_m\}$.
%
It is equivalent to study~$d_i$ and its \emph{epigraph} 
%
$$
	\epi(d_i) = \{(p,t)\in\mathbb R^{d+1}: d_i(p)\leq t\}
$$
%
see e.g.~\cite{Gorokhovik:1993}.
%
On each $d$-dimensional face 
%
\begin{equation}\label{eq:conv:hull:facet:of:epigraph}
F_j = \underset{f}{\conv}\left\{\left(\begin{array}{c}p_{j,f}\\ t_{j,f}\end{array}\right)\right\}
\end{equation}
%
of $\epi(d_i)$ there exists a maximiser~$k_j$ such that~$d_i$ is defined by~$d_i(p)=b_{i,k_j}+c_{i,k_j}p$ for all $p\in\pi_d(F_j)$ or equivalently~$d_i(p)=\sum_{f}\lambda_f t_{j,f}$ with ${\bf{0}}\leq\lambda\leq{\bf{1}}$ such that $p=\sum_{f}\lambda_f p_{j,f}$.
%
Notice that if~\eqref{eq:conv:hull:facet:of:epigraph} is redundant, i.e. not all elements are vertices of $F_j$, the statement is still true, and we can write $d_i(p)$ as a convex combination of points.

Let~$\mathcal C$ be a polyhedral complex such that in each $d$-dimensional element~$\mathcal P_j\in\mathcal C$ the set-valued map is given by $\mathcal W(p) = \{z\in\mathbb R^n:a_i z\leq b_{i,k_j} + c_{i,k_k} p\}$. 
%
It is worth pointing out that we only assume any such polyhedral complex, in particular we do not consider it to be minimal, since the minimal such complex could have non-convex elements, those elements can however be partitioned such that every element of the non-minimal $\mathcal C$ are convex polyhedra. 
%
The set of vertices of elements in the complex coincides with the union of all vertices of $d$-dimensional faces of $\epi(d_i)$ for all $i\in\mathbb N_m$, i.e.
%
$$
	\bigcup_{P\in\mathcal C}\text{vert}(P) = \bigcup_{(\ast)} \text{vert}(\pi_d(F)) = \bigcup_{i\in\mathbb N_m}\pi_d(\text{vert}(\epi(d_i))),
$$
%
with $(\ast) = \{F: d-\text{dimensional face of } \epi(d_i) \text{ for some } i\in\mathbb N_m\}$.
%
It is now almost obvious that the graph $\mathscr G(\mathcal W\vert_P)$ on each $d$-dimensional element $P\in\mathcal C$ is entirely defined by the values of $\mathcal W(p_j)$ at the vertices $p_j\in\text{vert}(P)$.
%
In each~$P$ we have $\mathcal W(p) = \{z: a_i z\leq \sum_f \lambda_f t_{i,j,f}, \sum_f\lambda_f p_{j,f}=p, \sum_f\lambda=1,{\bf{0}}\leq\lambda\leq{\bf{1}}\; \forall i\in\mathbb N_m\}$
%
Therefore, if~$\mathcal A_\kappa\subset\mathbb N_m$ such that~$\abs{\mathcal A_\kappa}=d$ and $a_\kappa v_\kappa = t_{\kappa,j}$ defines a vertex for $\mathcal W(p_j)$, then $a_\kappa v_\kappa = \sum_f \lambda_f t_{\kappa,f}$ defines a vertex for $\mathcal W(p)$.

The proposed algorithm to determine parametric convexity of a given piecewise affine polyhedral description~$\mathcal W(p)$ as in~\eqref{eq:definition:PWA:polytopic:set:general} can therefore be summarised as follows:
%
Firstly, compute all vertices~$\bigcup_{i\in\mathbb N_m}\text{vert}(\epi(d_i))$.
%
Next, check whether the number of vertices is constant on $\mathcal D = \pi_d\left(\bigcup_{i\in\mathbb N_m}\text{vert}(\epi(d_i))\right)$, i.e. 
%
$$\abs{\text{vert}(\mathcal W(p))} = \text{const.}\quad \forall p\in\mathcal D$$.
%

\section*{References}

\bibliography{Bibliography}

\end{document}

### 2016-07-04 draft.tex
Major changes adding two examples, yet no intro.
what happened

[ticket: X]

@@
 
-\usepackage{lineno,hyperref}
+\usepackage{lineno}
+\usepackage[hidelinks]{hyperref}
 \modulolinenumbers[5]
@@
 }
+
+\usepackage{tikz}
+\usetikzlibrary{arrows,positioning,patterns,decorations.pathreplacing}
 
@@
 
+%
+Notation:~$\mathscr P(X)$ denotes the power set of $X$.
+%
 \section{Preliminaries}
+
+Throughout the paper we deal with set-valued maps, i.e.
+functions that map an element of a metric space~$Y$ to a subset of a metric space~$Z$: $f:Y\mapsto\mathscr P(Z), Y\ni y\rightarrow f(y)\subset Z$.
+%
+A detailed presentation on properties of set-valued maps is beyond the scope of this paper and we refer to~\cite{Aubin:2009}, here we only assume that the set-valued map is continuous in the sense that its \emph{graph}
+%
+\begin{equation}
+  \mathscr G(f) = \{(y,z)\in Y\times Z: z\in f(y)\}
+\end{equation}
+%
+has a continuous boundary, for every bounded point $(y,z)\in\partial\mathscr G(f)$ the boundary $\partial\mathscr G(f)$ is locally given by the graph of a continuous function.
+%
+We only consider set-valued maps with convex images, i.e. such maps for which $z_1,z_2\in f(y)\Rightarrow \lambda z_1+(1-\lambda)z_2\in f(y)$ for all $\lambda\in[0,1]$ holds for all $y\in Y$.
+
+An important subset of such set-valued maps are such that their realisations are polytopic, $f(y)$ is a polytope for all $y\in Y$, in particular we study maps which depend on the \emph{parameter} in a piecewise affine way.
+%
+The graph of such maps is given by a union of polytopes, they have been studied in~\cite{Finzel:2000}.
+%
+We will make statements about \emph{generic} such maps, that is properties which are structurally stable in the sense that if~$f(y)$ has a particular property than there exists an open neighbourhood $U\ni y$ such that $f(\tilde y)$ has the same property for all $\tilde y\in U$, furthermore the set of points for which the property does not hold is of measure zero.
+%
+In the course of this paper it will be self evident what the set of points is, where the property of interest fails, in particular a lower dimensional polyhedron and we therefore omit a measure theoretic treatment of our assumption.
+
+The particular property we require is \emph{simplicity}, for each $y\in Y$ the set $f(y)$ is a polytope and each of its vertices~$v(y)$ is supported by a minimal number of hyperplanes, i.e.
+there exists linear system defining the set~$f(y) = \{z:A(y)z\leq b(y)\}$ and each vertex $v(y)$ is defined by $dim(Z)$ hyperplanes $A_{\mathcal I}(y)v(y)=b_{\mathcal I}(y)$ and $A_{\bar{\mathcal I}}(y)v(y)<b_{\bar{\mathcal I}}(y)$.
+%
+It is easy to see, that if $A(\cdot)$ and $b(\cdot)$ are continuous in $y$, then $\mathcal I$ locally defines a vertex, i.e.
+the combinatorial structure of a simple polytope is structurally stable and therefore being simple is a generic property of a polytope.
+
+The induced graph~$G(P)$ of a polytope~$P$ is the graph for which the vertices and edges coincide with the vertices and edges of the polytope itself~\cite{Bondy:2008}.
+%
+In this paper we only use one property of induced graphs, namely the \emph{Perles' Conjecture}~\cite{Kalai:1988}:
+\emph{For a simple polytope~$P$ the graph~$G(P)$ determines the combinatorial structure of~$P$.}
 
@@
 
-In this section we define the property of \emph{parametric convexity} in the context of set valued maps (so called point-to-set maps, see e.g.~\cite{Hogan:1973}). This property is then used 
-to demonstrate the convexity of a generalised Pontryagin difference. 
+In this section we define the property of \emph{parametric convexity} in the context of set-valued maps. 
 %
-In this section we refer to sets $Y\subseteq\mathbb R^d$ and $Z\subseteq\mathbb R^n$, and we denote the power set of $Z$ as $\mathscr P(Z)$.
+This property is then used to demonstrate the convexity of a generalised Pontryagin difference (see e.g.~\cite{blanchini:2007}). 
+%
+In this section we refer to sets $Y\subseteq\mathbb R^d$ and $Z\subseteq\mathbb R^n$.
 %
 \begin{defi}[Parametric Convexity]\label{def:parametric:convexity}
-Let $\mathcal W:Y\rightarrow \mathscr P(Z)$, where $Y\ni p\mapsto \mathcal W(p) \subset Z$, be a continuous point-to-set map.
-The map $\mathcal W$ is called \emph{parametrically convex} if it satisfies
+Let $\mathcal W:Y\rightarrow \mathscr P(Z)$, where $Y\ni p\mapsto \mathcal W(p) \subset Z$, be a continuous set-valued map. The map $\mathcal W$ is called \emph{parametrically convex} if it satisfies
 %
@@
 Notice that Definition~\ref{def:parametric:convexity} does not require convexity of~$\mathcal W(p)$. 
-However, we will only consider maps~$\mathcal W$ for which $\mathcal W(p)$ is convex for all fixed $p\in Y$.
+%
+However, recall that we will only consider maps~$\mathcal W$ for which $\mathcal W(p)$ is convex for all fixed $p\in Y$.
 
@@
 We begin by introducing an equivalent characterisation of parametric convexity that provides an insight into the geometrical properties of 
-point-to-set maps satisfying~\eqref{eq:def:parametrically:convex}.
-This is based on a description of parametric convexity in terms of conditions on the graph of a point-to-set map.
+set-valued maps satisfying~\eqref{eq:def:parametrically:convex}.
+%
+This is based on a description of parametric convexity in terms of conditions on the graph~$\mathscr G(\mathcal W)$ of a set-valued map.
 %
 \begin{defi}\label{def:graph:of:map}
-Let $\mathcal W:Y\rightarrow \mathscr P(Z)$ be a continuous point-to-set map
+Let $\mathcal W:Y\rightarrow \mathscr P(Z)$ be a continuous set-valued map
 such that $\mathcal W(p)$ is convex for all $p\in Y$, then 
 %
-\[
-\mathscr G(\mathcal W) = \{(p,z) \in\mathbb R^{d+n}: z\in\mathcal W(p)\}
-\]
-%
-denotes the \emph{graph} of $\mathcal W$,
-%
 \begin{equation*}  
-\text{int}(\mathscr G(\mathcal W)) = \{(p,z) \in\mathbb R^{d+n} : \exists \epsilon>0, \, z+\epsilon \zeta\in \mathcal W(p) \forall \zeta\in\mathbb R^n\}
+\text{int}(\mathscr G(\mathcal W)) = \{(p,z) \in Y\times Z : \forall \zeta\in\mathbb R^n\exists \epsilon>0, \, z+\epsilon \zeta\in \mathcal W(p) \}
 \end{equation*}
 %
-is its \emph{interior}, and
+denotes the \emph{interior} of its graph and
 %
@@
 %
-denotes its \emph{boundary};
+its \emph{boundary};
 %
@@
 %
-Note that the orientation cone is defined in the space of the
-\emph{set variable} $z$ rather than \emph{graph variable} $(p,z)$.
+Note that the sets are defined in the space of the \emph{set variable} $z\in Y$ rather than \emph{graph variable} $(p,z)\in Y\times Z$.
 %
-Furthermore, the orientation cone contains all directions that 
-point out of the set $\mathcal W(p)$ and hence all linear combinations thereof.
+Furthermore, the orientation cone contains all directions that point out of the set $\mathcal W(p)$ and hence all linear combinations thereof.
 %
@@
 %
-It follows that $\mathcal W$ cannot be parametrically convex in this case.
+It follows that $\mathcal W$ cannot be parametrically convex.
 \end{proof}
@@
 %
-Let $\mathcal W(p):=\{z\in\mathbb R^n: r(p,z)\leq0\}$ define a point-to-set
+Let $\mathcal W(p):=\{z\in\mathbb R^n: r(p,z)\leq0\}$ define a set-valued
 map where 
@@
 %
-It is useful to be able to perform set certain set operations on point-to-set maps, therefore we define the parametric Pontryagin difference:
+It is useful to be able to perform set certain set operations on set-valued maps, therefore we define the parametric Pontryagin difference:
 %
 \begin{defi}[Parametric Pontryagin Difference]\label{def:parametric:pontryagin:difference}
-  Let $S\subseteq Z$ and let $\mathcal W:Z\to\mathscr P(Z)$ be a continuous point-to-set map such that
+  Let $S\subseteq Z$ and let $\mathcal W:Z\to\mathscr P(Z)$ be a continuous set-valued map such that
   $\mathcal W(p)$ is convex for all $p\in Z$, then the \emph{parametric Pontryagin difference} 
@@
 %
-By a slight abuse of notation, $\mathcal{W}(S)$ is used in~(\ref{eq:definition:parametric:pontryagin:difference}) to indicate that $\mathcal{W}$ is a point-to-set map and that $S\ominus\mathcal{W}(S)$ denotes the parametric Pontryagin difference, rather than a fixed set and the conventional Pontryagin difference.
+By a slight abuse of notation, $\mathcal{W}(S)$ is used in~(\ref{eq:definition:parametric:pontryagin:difference}) to indicate that $\mathcal{W}$ is a set-valued map and that $S\ominus\mathcal{W}(S)$ denotes the parametric Pontryagin difference, rather than a fixed set and the conventional Pontryagin difference.
 %
@@
 \begin{thm}\label{thm:convexity:of:pontryagin:difference}
-Let $\mathcal W: Z\rightarrow\mathscr P(Z)$ be a given point-to-set map, then the parametric Pontryagin difference $S \ominus \mathcal W(S)$ is convex for every convex $S\subseteq Z$ if and only if $\mathcal W$ is parametrically convex.
+Let $\mathcal W: Z\rightarrow\mathscr P(Z)$ be a given set-valued map, then the parametric Pontryagin difference $S \ominus \mathcal W(S)$ is convex for every convex $S\subseteq Z$ if and only if $\mathcal W$ is parametrically convex.
 \end{thm}
@@
 %
-(where the last inclusion results from the convexity of $\mathcal S$), and it follows that
+(where the last inclusion results from the convexity of $S$), and it follows that
 $\lambda z_1 + (1-\lambda) z_2 \in S^\prime$ for all $\lambda \in (0,1)$. 
@@
 Theorem~\ref{thm:convexity:of:pontryagin:difference} provides necessary and sufficient conditions for convexity of the parametric Pontryagin difference. 
-Later we will show that the parametric Pontryagin difference between a polyhedral set and a piecewise affine polytopic parametric set is itself polyhedral.
+%
+Later we will show that the parametric Pontryagin difference between a polyhedral set and a piecewise polytopic set-valued map is itself polyhedral.
 %
@@
 %
-In this section we discuss point-to-set maps~$\mathcal W$ for which every realisation~$\mathcal W(p)$ is polyhedral and in particular
-we study~$\mathcal W$ which depend on $p\in Y$ in a piecewise affine way. 
+In this section we discuss set-valued maps~$\mathcal W$ for which every realisation~$\mathcal W(p)$ is polyhedral and in particular we study~$\mathcal W$ which depend on $p\in Y$ in a piecewise affine way.
 %
-To the authors' best knowledge the the literature on piecewise polyhedral sets is limited, we refer to~\cite{Finzel:2000}, however properties of general set-valued maps are known and applicable, see e.g.~\cite{Aubin:1990}.
+To the authors' best knowledge the the literature on piecewise polyhedral sets is limited, we refer to~\cite{Finzel:2000}, however properties of general set-valued maps are known and applicable, see e.g.~\cite{Aubin:2009}.
 
@@
 %
+\begin{rem}
+%
+Recall that the graph $\mathscr G(\mathcal W)$ of a set-valued map can not be strictly convex anywhere in order for $\mathcal W$ to be parametrically convex. 
+%
+Therefore, Corollary~\ref{thm:polytopic:set:not:p:convex} is only a global statement.
+\end{rem}
+%
 \begin{cor}\label{thm:p:convexity:PWA:set:constant:num:verts}
-The generic piecewise affine polytopic parametric point-to-set valued map 
+The generic piecewise affine polytopic parametric set-valued valued map 
 %
@@
 Furthermore, since~$\mathcal W(p)$ is generic, only one element of ${\bf{k}}^\ast\vert_{\mathcal P_{j_1}}$
-and ${\bf{k}}^\ast\vert_{\mathcal P_{j_2}}$ differs, that is, there exists a single index $i\in\mathbb N_m$ such that $k_i^\ast\vert_{\mathcal P_{j_1}}\neq k_i^\ast\vert_{\mathcal P_{j_2}}$.
+and ${\bf{k}}^\ast\vert_{\mathcal P_{j_2}}$ for neighbouring $\mathcal P_{j_1}$ and $\mathcal P_{j_2}$ differs, that is, there exists a single index $i\in\mathbb N_m$ such that $k_i^\ast\vert_{\mathcal P_{j_1}}\neq k_i^\ast\vert_{\mathcal P_{j_2}}$.
 %
@@
 %
-The \emph{Perles' Conjecture}, which was proven e.g.
-in~\cite{Kalai:1988}, states that the combinatorial structure of a simple polytope is uniquely determined by its graph, that is, as long as the graph of~$\mathcal W(p)$ remains unchanged so does its combinatorial structure.
+The \emph{Perles' Conjecture}~\cite{Kalai:1988}, states that the combinatorial structure of a simple polytope is uniquely determined by its graph, that is, as long as the graph of~$\mathcal W(p)$ remains unchanged so does its combinatorial structure.
 %
-The graph of a polytope is given by the vertices and the edges of a polytope, since we have that the number of vertices remains unchanged throughout~$Y$ for $\mathcal W(p)$ the graph $G(\mathcal W(p))$ has to have a constant number of vertices.
+The induced graph of a polytope is given by the vertices and the edges of a polytope, since we have that the number of vertices remains unchanged throughout~$Y$ for $\mathcal W(p)$ the induced graph $G(\mathcal W(p))$ has to have a constant number of vertices.
 %
@@
 %
-This means in particular that we ignore the fact that locally $v_{\kappa_1}=v_{\kappa_2}$ and use a locally redundant representation $\mathcal W(p) = \conv_\kappa\{v_\kappa(p)\}$.
+This means in particular that we ignore the fact that locally $v_{\kappa_1}=v_{\kappa_2}$ and can
+ use a locally redundant representation $\mathcal W(p) = \conv_\kappa\{v_\kappa(p)\}$.
 \end{proof}
@@
 %
-In the previous sections we have derived that for the Pontryagin difference between any convex set $S$ and a point-to-set map~$\mathcal W$ to be convex itself we require the parametric convexity property for~$\mathcal W$.
+In the previous sections we have derived that for the Pontryagin difference between any convex set $S$ and a set-valued map~$\mathcal W$ to be convex itself we require the parametric convexity property for~$\mathcal W$.
 %
@@
 For notational convenience let $d_i(p) = \max_k\{b_{i,k}+c_{i,k}p\}$ denote the right hand side of~\eqref{eq:definition:PWA:polytopic:set:general}, i.e.
-$\mathcal W(p) = \{z\in\mathbb R^d: a_i z\leq d_i(p)\;\forall i\in\mathbb N_m\}$.
+$\mathcal W(p) = \{z\in\mathbb R^n: a_i z\leq d_i(p)\;\forall i\in\mathbb N_m\}$.
 %
@@
 $$
-	\epi(d_i) = \{(p,t)\in\mathbb R^{d+1}: d_i(p)\leq t\}
+	\epi(d_i) = \{(p,t)\in Y\times\mathbb R: d_i(p)\leq t\}
 $$
@@
 %
+A natural way to obtain a convex polyhedral complex is by projecting the facets of the set
+%
+\begin{equation}
+  E=\left\{(p,t_1,\dots,t_m)\in Y\times\mathbb R^{m}:d_i(p)\leq t_i\right\}
+\end{equation}
+%
+onto $\mathbb R^d$.
+%
 The set of vertices of elements in the complex coincides with the union of all vertices of $d$-dimensional faces of $\epi(d_i)$ for all $i\in\mathbb N_m$, i.e.
@@
 %
-It is now almost obvious that the graph $\mathscr G(\mathcal W\vert_P)$ on each $d$-dimensional element $P\in\mathcal C$ is entirely defined by the values of $\mathcal W(p_j)$ at the vertices $p_j\in\text{vert}(P)$.
+It is now almost obvious that the graph $\mathscr G(\mathcal W\vert_{\mathcal P_j})$ on each $d$-dimensional element $\mathcal P_j\in\mathcal C$ is entirely defined by the values of $\mathcal W(p_j)$ at the vertices $p_j\in\text{vert}(\mathcal P_j)$.
 %
-In each~$P$ we have $\mathcal W(p) = \{z: a_i z\leq \sum_f \lambda_f t_{i,j,f}, \sum_f\lambda_f p_{j,f}=p, \sum_f\lambda=1,{\bf{0}}\leq\lambda\leq{\bf{1}}\; \forall i\in\mathbb N_m\}$
+In each~$\mathcal P_j$ we have $\mathcal W(p) = \{z: a_i z\leq \sum_f \lambda_f t_{i,j,f}, \sum_f\lambda_f p_{j,f}=p, \sum_f\lambda=1,{\bf{0}}\leq\lambda\leq{\bf{1}}\; \forall i\in\mathbb N_m\}$
 %
@@
 %
-Firstly, compute all vertices~$\bigcup_{i\in\mathbb N_m}\text{vert}(\epi(d_i))$.
+Firstly, compute all vertices~$\text{vert}(E)$.
 %
-Next, check whether the number of vertices is constant on $\mathcal D = \pi_d\left(\bigcup_{i\in\mathbb N_m}\text{vert}(\epi(d_i))\right)$, i.e. 
+Next, check whether the number of vertices is constant on $\mathcal D = \pi_d\left(\text{vert}(E)\right)$, i.e. 
 %
@@
 %
+
+\section{Numerical Examples}
+\subsection{Norm bound sets}
+%
+Consider the set~$X = \{x\in\mathbb R^2: \abs{x_1}\leq 1\wedge \abs{x_2}\leq 1\}$ and the set-valued map $\mathcal W(x) = \{w\in\mathbb R^2: \norm{w}_P\leq\kappa\norm{x}_P\}$.
+%
+Where $\norm{\cdot}_P$ is a polytopic approximation to the euclidean norm~$\norm{\cdot}_2$, i.e.
+%
+$$
+c_1 \norm{x}_P\leq\norm{x}_2\leq c_2\norm{x}_P.
+$$
+%
+For the choice 
+%
+$$
+\norm{x}_P = \max_{k\leq n}\left\{\sin\left(\frac{2\pi}{n-1}k\right) x_1 + \cos\left(\frac{2\pi}{n-1}k\right) x_2\right\} = \max_{k\leq n}\{F_k x\}
+$$
+%
+we find $c_1 = \cos\left(\frac{\pi}{n-1}\right)$ and $c_2=1$.
+%
+This choice of~$\mathcal W(x)$ is a scaled approximation of an euclidean ball and therefore obviously parametrically convex with a fixed combinatorial structure.
+%
+In fact, we find the~$n$ vertices given by the solution to
+%
+$$
+  \left(\begin{array}{cc}
+  \sin\left(\frac{2\pi}{n-1}(k-1)\right) & \cos\left(\frac{2\pi}{n-1}(k-1)\right) \\
+  \sin\left(\frac{2\pi}{n-1}k\right) & \cos\left(\frac{2\pi}{n-1}k\right)
+  \end{array}
+  \right) w_k = {\bf{1}}\norm{x}_P
+$$
+%
+for $k=1,\dots,n$.
+
+Characterising the parametric Pontryagin difference~$X\ominus\mathcal W(X) = \{z\in\mathbb R^2:z+w\in X\;\forall w\in\mathcal W(x)\}$ is done by characterising its boundary.
+%
+This is done by finding points~$z$ which for some~$w\in\mathcal W(z)$ can be taken to the boundary of $X$.
+%
+For the face given by $P_i = \{x:\Lambda_i x=\lambda_i\wedge\Lambda_j x\leq \lambda_j,j\neq i\}$, we find the face(s) of $X\ominus\mathcal W(X)$ by finding extremal values of $w\in\mathcal W(P_i)$ defining it, i.e.
+the extremal values of
+%
+$$
+  \Lambda_i(z+w)=\lambda_i\; w\in\mathcal W(z)\wedge \Lambda_j(z+w)\leq\lambda_j,j\neq i.
+$$
+%
+To do this, we rewrite the problem as a maximisation
+%
+$$
+\begin{array}{rl}\max& \Lambda_i w \\ \text{s.t.}& w\in\mathcal W(z)\\ &\Lambda_i (z + w) = \lambda_i\\
+&\Lambda_j(z+w)\leq \lambda_j\end{array}
+$$
+%
+We now exploit the fact that we have a vertex description of the set-valued map $\mathcal W(x) = \bigl\{w:F w\leq{\bf{1}}\max_{k\leq n}\{F_kx\}\bigr\}$ and with the auxiliary variable~$\max_{k\leq n}\{F_k x\} = t$ we rewrite $\mathcal W(x) = \conv\{w_i(t(x))\}$ using the vertices
+%
+$$
+\begin{pmatrix}
+w_1\\ \vdots \\ w_n
+\end{pmatrix} = \begin{pmatrix}T_1\\\vdots\\T_n\end{pmatrix}{\bf{1}}t(x).
+$$
+%
+With this the set of points for which there exists a feasible $w\in\mathcal W$ reaching the face $P_i$ is given as the projection
+%
+$$
+\pi_2\left(\left\{(z,t,\tau): \begin{array}{rcl}\Lambda_i Tt &\leq& \tau\\ Fz&\leq& t\\ \Lambda_i(z+\tau)&=&\lambda_i\\ \Lambda_j(z+T_lt)&\leq&\lambda_j\end{array},j\neq i,l\in\{1,\dots,n\}\right\}\right)
+$$
+%
+This then gives us all points $z$ for which a feasible $w$ can be found such that $z+w\in P_i$, by combining all such projections we obtain the representation of $X\ominus\mathcal W(X)$.
+%
+Alternatively, the set~$X\ominus\mathcal W(X)$ can be obtained by a single projection of the higher dimensional set:
+$$
+\pi_2\left(\left\{(z,t,\tau_1,\dots,\tau_q):\begin{array}{rcl}
+\Lambda_i Tt & \leq &\tau_i\\
+Fz &\leq& t\\
+\Lambda_i(z+\tau_i)&\leq&\lambda_i
+\end{array},i\in\{1,\dots,q\}\right\}\right)
+$$
+%
+However, in practical application the increase in computation time of projecting a $d+q+1$ polyhedron onto $d$ instead of projecting a $d+2$ polyhedron onto $d$ $q$ times is usually prohibitively large.
+
+For the choice~$\kappa=0.2$ and~$n = 35$ the set~$X\ominus\mathcal W(X)$ is illustrated in Figure~\ref{fig:example:parametric:pontryagin:difference}.
+
+\begin{figure}
+\centering
+\includegraphics[width=.95\textwidth]{parametricPD.pdf}
+\caption{$X\ominus\mathcal W(X)$}
+\label{fig:example:parametric:pontryagin:difference}
+\end{figure}
+
+\subsection{Element wise bound sets}\label{exp:second:example}
+%
+For another example we take inspiration from a robust control scenario.
+%
+We want to approximate the maximal positive invariant set for a system of the type~$x^+=Ax + f(x)$ for $x\in\mathcal X$, i.e.
+the largest set of points~$\mathcal X^\infty\subseteq\mathcal X$ such that $x\in\mathcal X^\infty\Rightarrow x^+\in\mathcal X^\infty$, see e.g.~\cite{blanchini:2007}.
+%
+For general nonlinear systems~$x^+=Ax + f(x)$ the maximal positive invariant set can not be calculated, but assume we find piecewise affine bounds on the nonlinearity, i.e.
+$\min_{k\leq M_i}\{h_{i,k}^x x + h_{i,k}^c\}\leq f_i(x)\leq\max_{k\leq N_i}\{H_{i,k}^x x + H_{i,k}^c\}$ for all $x\in\mathcal X$ and all elements of~$f(x)$.
+%
+We can now study the system $x^+=Ax+w$ with $w\in\mathcal W(x) = \{w:\min_{k\leq M_i}\{h_{i,k}^x x + h_{i,k}^c\}\leq w_i\leq\max_{k\leq N_i}\{H_{i,k}^x x + H_{i,k}^c\}\,\forall i\in\{1,\dots,d\}\}$.
+%
+Instead of computing the maximal positive invariant set for the nonlinear system we compute the maximal robust positive invariant set for the perturbed linear system $x^+=Ax+w$, i.e.
+the set of states~$\mathscr X^\infty\subseteq\mathcal X$ such that $x\in\mathscr X^\infty$ implies $x^+\in\mathscr X^\infty$ for all possible $w\in\mathcal W(x)$.
+%
+The algorithm to determine the maximal robust positive invariant sets recursively intersects the current set iterate~$X_l$ with the set of all possible successor states starting from the current iterate $X_{l+1}=X_l\cap\left\{\bigcup_{x\in X_l,w\in\mathcal W(x)}\{Ax+w\}\right\}$, we will only present a single step.
+%
+Notice that for a constant set-valued map~$\mathcal W(x) = \mathcal W$ the iteration can be summarised as $X_{l+1} = X_l\cap A^{-1}(X_l\ominus\mathcal W)$, for a set valued map a similar compact notation also holds, however it is more confusing than helpful:~$X_{l+1}=X_l\cap(A^{-1}X_l\ominus A^{-1}\mathcal W(A^{-1}X_l))$.
+
+In order to illustrate the proposed treatment of the nonlinearities we use the two dimensional system~$x^+=x+f(x)$ where the nonlinearity is given by
+%
+\begin{subequations}
+\begin{equation}
+  f_1(x) = \frac{1}{10}\left(\frac{x_1}{2}+x_2\right)^3
+\end{equation}
+\begin{equation}
+  f_2(x) = \frac{1}{2}\arcsin\left(\sigma\left(x_1-\frac{x_2}{2}\right)\sqrt{\frac{x_1-\frac{x_2}{2}}{2}} + \sigma\left(-\left(x_1-\frac{x_2}{2}\right)\right)\frac{x_1-\frac{x_2}{2}}{2} \right)
+\end{equation}
+\end{subequations}
+%
+with the Heaviside function
+%
+$$
+  \sigma(t) = \left\{\begin{array}{crcl}1& t&\geq&0\\ 0 &t&<&0 \end{array}\right.
+$$
+%
+As the constraint set we use $X_l = \{x:\abs{x_1}+\abs{x_2}\leq 2\}$.
+%
+In order not to bore the reader with numerical values, we illustrate the approximation of $f_1(x)$ in Figure~\ref{fig:approximation:f1:p:diff} and~$f_2(x)$ in Figure~\ref{fig:approximation:f2:p:diff}, for both we obtain upper and lower bounds using secants and tangents.
+%
+Figure~\ref{fig:approximation:f2:p:diff} shows an obvious weakness of the approach:~$\max_k\{c_k x+b_k\}$ is always convex, therefore approximating non-convex functions introduces conservativeness.
+
+The actual computation of the set~$X_{l+1}$ is then done analogous to the previous example, again we use that 
+%
+$$
+  \mathcal W(x) = \conv\left\{\begin{pmatrix}t_1\\ t_3\end{pmatrix},\begin{pmatrix}t_1\\ t_4\end{pmatrix},
+  \begin{pmatrix} t_2\\ t_3\end{pmatrix},\begin{pmatrix}t_2\\ t_4\end{pmatrix}
+  \right\}
+$$
+%
+with $t_1=\max_k\{H_{1,k}^x x+H_{1,k}^c\},\; t_3=\max_k\{H_{2,k}^x x+H_{2,k}^c\},\; t_2=-\max_k\{-h_{1,k}^x x-h_{1,k}^c\}$ and $t_4=-\max_k\{-h_{1,k}^x x-h_{1,k}^c\}$.
+%
+Each facet~$P_i=\{x:\Lambda_i x=\lambda_i\wedge\Lambda_jx\leq\lambda_j,j\neq i\}$ of the current set iterate defines facets of the next set iterate satisfying
+%
+\begin{equation}
+\Lambda_i(Ax+w^\ast)=\lambda_i\quad \Lambda_j(Ax+w^\ast)\leq\lambda_j,j\neq i
+\end{equation}
+%
+where $w^\ast$ is the maximiser of the defining mpLP $\max_{w\in\mathcal W(x)}\Lambda_iw$, i.e. one of the aforementioned vertices with their representation
+%
+$$
+  \begin{pmatrix} w_1\\ \vdots \\ w_N\end{pmatrix}= Tt.
+$$
+%
+With this the collection of facets generated by~$P_i$ is given by the projection
+%
+\begin{equation}
+  \pi_d\left(\left\{(x,t,\tau)\in\mathbb R^{3d+1}:\begin{array}{rcl}
+  \Lambda_iAx+\tau&=&\lambda_i\\
+  \Lambda_i T_lt&\leq&\tau\\
+  \Lambda_j(Ax+T_lt)&\leq&\lambda_j\\
+  H_l^x x + H_l^c&\leq&t_{2l-1}\\
+  -h_l^x x - h_l^c&\leq&t_{2l}
+  \end{array}, \begin{array}{l}
+  j\neq i\\
+  l\in\{1,\dots,d\}\end{array}
+  \right\}\right)
+\end{equation}
+%
+Analogous to the previous example, instead of computing~$q$ projections from $3d+1$ onto $d$ we can perform a single projection with the same result:
+%
+\begin{equation}
+  \pi_d\left(\left\{(x,t,\tau)\in\mathbb R^{3d+q}:\begin{array}{rcl}
+  \Lambda_i T_lt&\leq&\tau_i\\
+  \Lambda_iAx+\tau_i&\leq&\lambda_i\\
+  H_l^x x + H_l^c&\leq&t_{2l-1}\\
+  -h_l^x x - h_l^c&\leq&t_{2l}
+  \end{array}, \begin{array}{l}
+  i\in\{1,\dots,q\},\\
+  l\in\{1,\dots,d\}\end{array}
+  \right\}\right)
+\end{equation}
+%
+The resulting set for our 2 dimensional example is illustrated in Figure~\ref{fig:second:example:resulting:set}.
+
+\begin{figure}
+\centering
+\begin{tikzpicture}[scale=2]
+\draw[-latex'] (-2.1,0) -- (2.1,0) node[above] {$t$};
+\draw[-latex'] (0,-.9) -- (0,.9) node[right,blue] {$f_1(t)$};
+\foreach \x in {-2,-1.5556,...,2} \draw (\x,0.05) -- (\x,-.05);
+\draw (-2,-.05) node[below] {$-2$};
+\draw (2,-.05) node[below] {$2$};
+\foreach \y in {-.8,-.4,...,.8} \draw (0.05,\y) -- (-.05,\y);
+\draw (.05,-.8) node[right] {$-0.8$};
+\draw (.05,-.4) node[right] {$-0.4$};
+\draw[scale=1,domain=-2:2,smooth,variable=\x,blue] plot ({\x},{\x*\x*\x/10});
+\draw (-2.0000, -0.8000) -- (-1.5556, -0.3764) -- (-1.1111, -0.1372) -- (-0.6667, -0.0296) -- (-0.2222, -0.0011) -- (0,0); 
+\draw (0,0) -- (0.2222, 0.0011) -- (0.6667, 0.0296) -- (1.1111, 0.1372) -- (1.5556, 0.3764) -- (2.0000, 0.8000);
+\fill[pattern = north east lines, opacity=.5] (-2.0000, -0.8000) -- (-1.5556, -0.3764) -- (-1.1111, -0.1372) -- (-0.6667, -0.0296) -- (-0.2222, -0.0011) -- (0,0) -- (-2,0) -- cycle; 
+\fill[pattern = north east lines, opacity=.5] (0,0) -- (0.2222, 0.0011) -- (0.6667, 0.0296) -- (1.1111, 0.1372) -- (1.5556, 0.3764) -- (2.0000, 0.8000) -- (2,0) -- cycle;
+\end{tikzpicture}
+\caption{$f_1(t=\frac{x_1}{2}+x_2)$ and its approximation by 9 secants used in Example~\ref{exp:second:example}.}
+\label{fig:approximation:f1:p:diff}
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{tikzpicture}[scale=2]
+\draw[-latex'] (-2.1,0) -- (2.1,0) node[above] {$t$};
+\draw[-latex'] (0,-.9) -- (0,.9) node[right,blue] {$f_2(t)$};
+\foreach \x in {-2,-1.5556,...,2} \draw (\x,0.05) -- (\x,-.05);
+\draw (-2,-.05) node[below] {$-2$};
+\draw (2,-.05) node[below] {$2$};
+\foreach \y in {-.8,-.4,...,.8} \draw (0.05,\y) -- (-.05,\y);
+\draw (.05,-.8) node[right] {$-0.8$};
+\draw (.05,-.4) node[right] {$-0.4$};
+\draw[blue] (-2.0000, -0.7854) -- (-1.9596, -0.6847) -- (-1.9192, -0.6428) -- (-1.8788, -0.6104) -- (-1.8384, -0.5830) -- (-1.7980, -0.5587) -- (-1.7576, -0.5367) -- (-1.7172, -0.5163) -- (-1.6768, -0.4972) -- (-1.6364, -0.4791) -- (-1.5960, -0.4620) -- (-1.5556, -0.4456) -- (-1.5152, -0.4298) -- (-1.4747, -0.4146) -- (-1.4343, -0.3999) -- (-1.3939, -0.3856) -- (-1.3535, -0.3717) -- (-1.3131, -0.3581) -- (-1.2727, -0.3449) -- (-1.2323, -0.3319) -- (-1.1919, -0.3192) -- (-1.1515, -0.3068) -- (-1.1111, -0.2945) -- (-1.0707, -0.2825) -- (-1.0303, -0.2706) -- (-0.9899, -0.2589) -- (-0.9495, -0.2473) -- (-0.9091, -0.2359) -- (-0.8687, -0.2247) -- (-0.8283, -0.2135) -- (-0.7879, -0.2025) -- (-0.7475, -0.1915) -- (-0.7071, -0.1807) -- (-0.6667, -0.1699) -- (-0.6263, -0.1592) -- (-0.5859, -0.1486) -- (-0.5455, -0.1381) -- (-0.5051, -0.1276) -- (-0.4646, -0.1172) -- (-0.4242, -0.1069) -- (-0.3838, -0.0966) -- (-0.3434, -0.0863) -- (-0.3030, -0.0761) -- (-0.2626, -0.0658) -- (-0.2222, -0.0557) -- (-0.1818, -0.0455) -- (-0.1414, -0.0354) -- (-0.1010, -0.0253) -- (-0.0606, -0.0152) -- (-0.0202, -0.0051) -- ( 0.0202,  0.0503) -- ( 0.0606,  0.0875) -- ( 0.1010,  0.1133) -- ( 0.1414,  0.1346) -- ( 0.1818,  0.1531) -- ( 0.2222,  0.1699) -- ( 0.2626,  0.1854) -- ( 0.3030,  0.1999) -- ( 0.3434,  0.2136) -- ( 0.3838,  0.2267) -- ( 0.4242,  0.2393) -- ( 0.4646,  0.2515) -- ( 0.5051,  0.2633) -- ( 0.5455,  0.2747) -- ( 0.5859,  0.2859) -- ( 0.6263,  0.2969) -- ( 0.6667,  0.3077) -- ( 0.7071,  0.3184) -- ( 0.7475,  0.3289) -- ( 0.7879,  0.3393) -- ( 0.8283,  0.3496) -- ( 0.8687,  0.3598) -- ( 0.9091,  0.3699) -- ( 0.9495,  0.3801) -- ( 0.9899,  0.3902) -- ( 1.0303,  0.4003) -- ( 1.0707,  0.4104) -- ( 1.1111,  0.4205) -- ( 1.1515,  0.4307) -- ( 1.1919,  0.4410) -- ( 1.2323,  0.4513) -- ( 1.2727,  0.4618) -- ( 1.3131,  0.4723) -- ( 1.3535,  0.4830) -- ( 1.3939,  0.4939) -- ( 1.4343,  0.5050) -- ( 1.4747,  0.5164) -- ( 1.5152,  0.5280) -- ( 1.5556,  0.5400) -- ( 1.5960,  0.5523) -- ( 1.6364,  0.5651) -- ( 1.6768,  0.5785) -- ( 1.7172,  0.5926) -- ( 1.7576,  0.6076) -- ( 1.7980,  0.6237) -- ( 1.8384,  0.6413) -- ( 1.8788,  0.6610) -- ( 1.9192,  0.6842) -- ( 1.9596,  0.7141) -- ( 2.0000,  0.7854);
+\draw (-2.0000, -0.7854) -- (-1.8000, -0.5599) -- (-1.5000, -0.4240) -- (0, 0);
+\fill[pattern = north east lines, opacity=.5] (-2.0000, -0.7854) -- (-1.8000, -0.5599) -- (-1.5000, -0.4240) -- (0, 0) -- (-2,0) -- cycle;
+\draw (-.5466,0) -- (0.7000, 0.3165) -- (1.0000, 0.3927) -- (1.5000, 0.5236) -- (1.7000, 0.5865) -- (2.0000, 0.7854);
+\fill[pattern = north east lines, opacity=.5] (-.5466,0) -- (0.7000, 0.3165) -- (1.0000, 0.3927) -- (1.5000, 0.5236) -- (1.7000, 0.5865) -- (2.0000, 0.7854) -- (2,0) -- cycle;
+\end{tikzpicture}
+\caption{$f_2(t=x_1-\frac{x_2}{2})$ and its approximation by 5 secants and 4 tangents as used in Example~\ref{exp:second:example}.}
+\label{fig:approximation:f2:p:diff}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=.95\textwidth]{complexPonDiff.pdf}
+\caption{In purple~$X_l$, outlined in blue~$X_{l+1}$, its vertices~$v_i$ marked by red crosses, yellow circles mark the vertices of $\{v_i\}\oplus\mathcal W(v_i)$, green crosses mark the actual value of $f(v_i)$ and dotted lines show the $x_1-\frac{x_2}{2}=0$ and $\frac{x_1}{2}+x_2=0$ planes.}
+\label{fig:second:example:resulting:set}
+\end{figure}
 

### 2016-07-07 draft.tex
Added introduction and citations.
what happened

[ticket: X]

@@
 \section{Introduction}
+%
+The Pontryagin difference was originally introduced as the Minkowski difference as a set theoretic tool in~\cite{Hadwiger:1950,Hadwiger:1957}, however in the years since the term Minkowski difference has often been used to refer to a different operation.
+%
+It was implicitly reintroduced in~\cite{Pontryagin:1966} for differential games to characterise safe sets for which strategies could be found which keep elements inside some second set for all possible adversary actions.
+%
+Since its introduction the usage of the Pontryagin difference has been extended beyond its application in differential games to various scenarios in which safe sets are required which withstand some perturbation.
+%
+See for example~\cite{blanchini:2007} for a its use as a robust control analysis tool in different contexts and under the name (set-)erosion it is used in morphological image analysis, e.g.~\cite{Haralick:1987}.
+%
+When the Pontryagin differnece has to be performed explicitly by numeric algorithms it is almost imperative that the respective sets are polytopic, since it is not possible to operate on general sets explicitly.
+%
+Algorithms to determine the Pontryagin difference between two polytopes are known and do not require more complex computation than the solving of linear programs~\cite{Kolmanovsky:1998,Kerrigan:2003}, as well as their analytical properties, see~\cite{blanchini:2007,Haralick:1987,Kolmanovsky:1998}.
+%
+The sets on which these operations can be performed are fixed predetermined polytopes, due to their physical interpretation safe sets, it can be desirable to extend the class of sets on which these operations can be performed.
+%
+For this purpose we propose the use of set-valued maps with polytopic realisation as the subtrahend.
 
+General set-valued maps have been studied analytically and various results are available in the literature, see e.g.~\cite{Aubin:2009}.
 %
-Notation:~$\mathscr P(X)$ denotes the power set of $X$.
+However, computational aspects of operations on set-valued maps are largely unknown, we refer to~\cite{Finzel:2000} for some results for polyhedral set-valued maps.
 %
-\section{Preliminaries}
+In this paper we present a particular class of set-valued maps for which the Pontryagin difference can be computed explicitly.
+%
+The set-valued maps we consider are parametrised polytopes with the so called \emph{parametric convexity} property which allows us to guarantee that the \emph{parametric Pontryagin difference} is convex for all convex minuend sets.
+%
+We provide the computational framework to allow us to perform parametric Pontryagin differences explicitly.
+
+The paper is structured as follows:
+%
+In Section~\ref{sec:preliminaries} we summarise preliminaries we require throughout the paper, in Section~\ref{sec:parametric:convexity} we introduce parametric convexity the essential ingredient for all subsequent analysis and provide analytic results for the set operations, which we refine and extend for set-valued maps with polyhedral realisations in Section~\ref{sec:polyhedral:maps}.
+%
+Section~\ref{sec:computational:methods} elaborates on how to determine whether a polyhedral map is in fact parametrically convex and how to perform operations on such set-valued maps, these concepts are then illustrated in Section~\ref{sec:numerical:examples} by two examples and finally we conclude the paper in Section~\ref{sec:conclusion}.
+
+Throughout this paper we refer to the the real $d$-dimensional parameter space as $Y\subseteq\mathbb R^d$, the $n$-dimensional realisation space as~$Z\subseteq\mathbb R^n$ and its power set~$\mathscr P(Z)$.
+%
+We denote index sets by $\mathcal A$ or $\mathcal I$, by $f\vert_\Omega$ we mean $f$ evaluated only on values in $\Omega$.
+%
+The standard Minkowski sum~\cite{Minkowski:1911} of the sets $X_1,X_2$ is denoted by $X_1\oplus X_2$
+%
+\section{Preliminaries}\label{sec:preliminaries}
 
@@
 The particular property we require is \emph{simplicity}, for each $y\in Y$ the set $f(y)$ is a polytope and each of its vertices~$v(y)$ is supported by a minimal number of hyperplanes, i.e.
-there exists linear system defining the set~$f(y) = \{z:A(y)z\leq b(y)\}$ and each vertex $v(y)$ is defined by $dim(Z)$ hyperplanes $A_{\mathcal I}(y)v(y)=b_{\mathcal I}(y)$ and $A_{\bar{\mathcal I}}(y)v(y)<b_{\bar{\mathcal I}}(y)$.
+there exists linear system defining the set~$f(y) = \{z:A(y)z\leq b(y)\}$ and each vertex $v(y)$ is defined by $n$ hyperplanes $A_{\mathcal I}(y)v(y)=b_{\mathcal I}(y)$ and $A_{\bar{\mathcal I}}(y)v(y)<b_{\bar{\mathcal I}}(y)$.
 %
@@
 
-\section{Parametric Convexity}
+\section{Parametric Convexity}\label{sec:parametric:convexity}
 
@@
 %
-This property is then used to demonstrate the convexity of a generalised Pontryagin difference (see e.g.~\cite{blanchini:2007}). 
+This property is then used to demonstrate the convexity of a generalised Pontryagin difference (see e.g.~\cite{Hadwiger:1950,blanchini:2007}). 
 %
-In this section we refer to sets $Y\subseteq\mathbb R^d$ and $Z\subseteq\mathbb R^n$.
+% In this section we refer to sets $Y\subseteq\mathbb R^d$ and $Z\subseteq\mathbb R^n$.
 %
@@
 However, recall that we will only consider maps~$\mathcal W$ for which $\mathcal W(p)$ is convex for all fixed $p\in Y$.
+%
+A similar definition was given in~\cite{Hadwiger:1957} for scalar families of sets ($d=1$), however the results presented are of no particular use for us here.
 
@@
 %
-\section{Polyhedral maps}
+\section{Polyhedral maps}\label{sec:polyhedral:maps}
 %
@@
 \begin{cor}\label{thm:polytopic:set:not:p:convex}
-The polytopic parametric set valued map $\mathcal W(p):=\{z: a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\}$
+The polytopic parametric set valued map $\mathcal W(p):=\{z: a_i z + b_i p\leq c_i \; \forall i\in\{1,\dots,m\}\}$
 is not parametrically convex for any non-zero matrix $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$.
@@
 \begin{equation*}
-	\mathscr G(\mathcal W) = \{(p,z):a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\} ,
+	\mathscr G(\mathcal W) = \{(p,z):a_i z + b_i p\leq c_i \; \forall i\in\{1,\dots,m\}\} ,
 \end{equation*}
@@
 \begin{equation}\label{eq:definition:PWA:polytopic:set:general}
-  \mathcal W(p) := \Bigl\{z\in\mathbb R^n: a_i z \leq \max_{k}\{b_{i,k} + c_{i,k}p\} \; \forall i\in\mathbb N_m \Bigr\}
+  \mathcal W(p) := \Bigl\{z\in\mathbb R^n: a_i z \leq \max_{k}\{b_{i,k} + c_{i,k}p\} \; \forall i\in\{1,\dots,m\} \Bigr\}
 \end{equation}
@@
 Notice that a vertex $v_\kappa(p)$ is defined by \emph{active} and \emph{inactive} inequalities, namely $\mathcal A_\kappa(p)$ and
-$\mathcal I_\kappa(p) = \mathbb N_m
+$\mathcal I_\kappa(p) = \{1,\dots,m\}
 %\{1,\dots,m\}
@@
 Furthermore, since~$\mathcal W(p)$ is generic, only one element of ${\bf{k}}^\ast\vert_{\mathcal P_{j_1}}$
-and ${\bf{k}}^\ast\vert_{\mathcal P_{j_2}}$ for neighbouring $\mathcal P_{j_1}$ and $\mathcal P_{j_2}$ differs, that is, there exists a single index $i\in\mathbb N_m$ such that $k_i^\ast\vert_{\mathcal P_{j_1}}\neq k_i^\ast\vert_{\mathcal P_{j_2}}$.
+and ${\bf{k}}^\ast\vert_{\mathcal P_{j_2}}$ for neighbouring $\mathcal P_{j_1}$ and $\mathcal P_{j_2}$ differs, that is, there exists a single index $i\in\{1,\dots,m\}$ such that $k_i^\ast\vert_{\mathcal P_{j_1}}\neq k_i^\ast\vert_{\mathcal P_{j_2}}$.
 %
@@
 %
-It is possible that there exist zero-measure sets (points, lines, $n-1$-hyperplanes) in~$Y$ where $\mathcal W$ becomes singular, meaning not simple
+It is possible that there exist zero-measure sets (points, lines, $d-1$-hyperplanes) in~$Y$ where $\mathcal W$ becomes singular, meaning not simple
 and vertices may merge, however due to the fact that for parameters outside such sets the combinatorial structure is fixed, we can find a  continuous selection through these sets, in any sense we like.
@@
 %
-This allows for efficient numerical treatment, since we know how the vertices are defined~$\mathcal A_\kappa = const.$.
+This allows for efficient numerical treatment, since we know how the vertices are defined~$\mathcal A_\kappa = const$.
+%
+We will illustrate how we exploit this property for our benefit in the Section~\ref{sec:computational:methods} and~\ref{sec:numerical:examples}.
+%
 
-In order to determine the Pontryagin difference between two sets one constructs the boundary of the Pontryagin difference. 
-%
-For this let $S = \{x\in\mathbb R^n:\Lambda_i x\leq \lambda_i,i\in\mathbb N_q\}$ and let $\mathcal W$ be defined by~\eqref{eq:definition:PWA:polytopic:set:general} satisfying Corollary~\ref{thm:p:convexity:PWA:set:constant:num:verts} and let $\mathcal W(x) = \conv_{i\in\mathbb N_v}\{v_i(x)\}\oplus\text{cone}_{i\in\mathbb N_r}\{r_i(x)\}$ be its V-representation.
-%
-Each inequality of $S$ must be satisfied for all admissible realisations $w\in\mathcal W(x)$ , that is:
-%
-\begin{equation*}\begin{split}
-	\Lambda_i(x+w) &\overset{!}{\leq}\lambda_i\; \forall i\in\mathbb N_q, w\in\mathcal W(x)\\
-	\Lambda_i x + \underbrace{\max_{w\in\mathcal W(x)} \Lambda_i w}_{(\dagger)} &\overset{!}{\leq} \lambda_i\; \forall i\in\mathbb N_q
-\end{split}\end{equation*}
-%
-The term~$(\dagger)$ is mpLP and its solution is attained on an extremal of~$\mathcal W(x)$, i.e. on one of the vertices or rays $v_i(x)$, $r_i(x)$.
-%
-Solving the mpLP is not necessary, due to Corollary~\ref{thm:combinatorical:equivalence:alternative} we know that every vertex and ray is generated by a fixed linear map~($a_i v_\kappa(x) = b_{i,k^\ast_i} + c_{i,k^\ast_i}x$ for~$i\in\mathcal A_\kappa$).
-%
-Therefore instead of solving~$(\dagger)$ we simply replace it with all possible vertices and rays and perform a regular inequality reduction:
-%
-\begin{equation*}
-	S\ominus\mathcal W(S) = \{x\in\mathbb R^n : \Lambda_i (x + v_j/r_j(x) ) \leq \lambda_i \; \forall i\in\mathbb N_q,j\in\mathbb N_{v/r}\}.
-\end{equation*}
-%
-Since~$v_j(x)$ and~$r_j(x)$ are piecewise affine in~$x$, the set~$S\ominus\mathcal W(S)$ is a polyhedral set and has the description H-representation $S\ominus\mathcal W(S)=\{x\in\mathbb R^n:\Gamma_i x\leq \gamma_i\;i\in\mathbb N_u\}$.
+% In order to determine the Pontryagin difference between two sets one constructs the boundary of the Pontryagin difference. 
+% %
+% For this let $S = \{x\in\mathbb R^n:\Lambda_i x\leq \lambda_i,i\in\mathbb N_q\}$ and let $\mathcal W$ be defined by~\eqref{eq:definition:PWA:polytopic:set:general} satisfying Corollary~\ref{thm:p:convexity:PWA:set:constant:num:verts} and let $\mathcal W(x) = \conv_{i\in\mathbb N_v}\{v_i(x)\}\oplus\text{cone}_{i\in\mathbb N_r}\{r_i(x)\}$ be its V-representation.
+% %
+% Each inequality of $S$ must be satisfied for all admissible realisations $w\in\mathcal W(x)$ , that is:
+% %
+% \begin{equation*}\begin{split}
+% 	\Lambda_i(x+w) &\overset{!}{\leq}\lambda_i\; \forall i\in\mathbb N_q, w\in\mathcal W(x)\\
+% 	\Lambda_i x + \underbrace{\max_{w\in\mathcal W(x)} \Lambda_i w}_{(\dagger)} &\overset{!}{\leq} \lambda_i\; \forall i\in\mathbb N_q
+% \end{split}\end{equation*}
+% %
+% The term~$(\dagger)$ is mpLP and its solution is attained on an extremal of~$\mathcal W(x)$, i.e. on one of the vertices or rays $v_i(x)$, $r_i(x)$.
+% %
+% Solving the mpLP is not necessary, due to Corollary~\ref{thm:combinatorical:equivalence:alternative} we know that every vertex and ray is generated by a fixed linear map~($a_i v_\kappa(x) = b_{i,k^\ast_i} + c_{i,k^\ast_i}x$ for~$i\in\mathcal A_\kappa$).
+% %
+% Therefore instead of solving~$(\dagger)$ we simply replace it with all possible vertices and rays and perform a regular inequality reduction:
+% %
+% \begin{equation*}
+% 	S\ominus\mathcal W(S) = \{x\in\mathbb R^n : \Lambda_i (x + v_j/r_j(x) ) \leq \lambda_i \; \forall i\in\mathbb N_q,j\in\mathbb N_{v/r}\}.
+% \end{equation*}
+% %
+% Since~$v_j(x)$ and~$r_j(x)$ are piecewise affine in~$x$, the set~$S\ominus\mathcal W(S)$ is a polyhedral set and has the description H-representation $S\ominus\mathcal W(S)=\{x\in\mathbb R^n:\Gamma_i x\leq \gamma_i\;i\in\mathbb N_u\}$.
 
-\section{Computational Methods}
+\section{Computational Methods}\label{sec:computational:methods}
 %
@@
 %
+\subsection{Determination of Parametric Convexity}
 In the previous sections we have derived that for the Pontryagin difference between any convex set $S$ and a set-valued map~$\mathcal W$ to be convex itself we require the parametric convexity property for~$\mathcal W$.
@@
 For notational convenience let $d_i(p) = \max_k\{b_{i,k}+c_{i,k}p\}$ denote the right hand side of~\eqref{eq:definition:PWA:polytopic:set:general}, i.e.
-$\mathcal W(p) = \{z\in\mathbb R^n: a_i z\leq d_i(p)\;\forall i\in\mathbb N_m\}$.
+$\mathcal W(p) = \{z\in\mathbb R^n: a_i z\leq d_i(p)\;\forall i\in\{1,\dots,m\}\}$.
 %
@@
 %
-In each~$\mathcal P_j$ we have $\mathcal W(p) = \{z: a_i z\leq \sum_f \lambda_f t_{i,j,f}, \sum_f\lambda_f p_{j,f}=p, \sum_f\lambda=1,{\bf{0}}\leq\lambda\leq{\bf{1}}\; \forall i\in\mathbb N_m\}$
+In each~$\mathcal P_j$ we have $\mathcal W(p) = \{z: a_i z\leq \sum_f \lambda_f t_{i,j,f}, \sum_f\lambda_f p_{j,f}=p, \sum_f\lambda=1,{\bf{0}}\leq\lambda\leq{\bf{1}}\; \forall i\in\{1,\dots,m\}\}$
 %
-Therefore, if~$\mathcal A_\kappa\subset\mathbb N_m$ such that~$\abs{\mathcal A_\kappa}=d$ and $a_\kappa v_\kappa = t_{\kappa,j}$ defines a vertex for $\mathcal W(p_j)$, then $a_\kappa v_\kappa = \sum_f \lambda_f t_{\kappa,f}$ defines a vertex for $\mathcal W(p)$.
+Therefore, if~$\mathcal A_\kappa\subset\{1,\dots,m\}$ such that~$\abs{\mathcal A_\kappa}=d$ and $a_\kappa v_\kappa = t_{\kappa,j}$ defines a vertex for $\mathcal W(p_j)$, then $a_\kappa v_\kappa = \sum_f \lambda_f t_{\kappa,f}$ defines a vertex for $\mathcal W(p)$.
 
@@
 %
+\subsection{Computing the Parametric Pontryagin Difference}\label{ssec:computation:p:pontryagin:difference}
+%
+%
+%
+The constancy of the active inequalities defining vertices of~$\mathcal W(p)$ is particularly useful when we compute the parametric Pontryagin difference $S\ominus\mathcal W(S)$:
+%
+For the set $S=\{p\in\mathbb R^d:\Lambda_i p\leq\lambda_i,i\in\{1,\dots,q\}\}$ each facet $P_i=\{p:\Lambda_i p=\lambda_i\wedge\Lambda_j p\leq\lambda_j,j\neq i\}$ defines facets of the set difference.
+%
+Namely each point~$p$ on the boundary of $S\ominus\mathcal W(S)$ is such that there exists an admissible $w^\ast$ such that $p+w^\ast$ lies on the boundary of $S$.
+%
+Computing the set $S\ominus\mathcal W(S)$ therefore reduces to computing points~$p$ for which an admissible $w^\ast$ exists to produce~$p+w^\ast\in P_i$ for some $i\in\{1,\dots,q\}$.
+%
+In order to find such points we use the inequality they have to satisfy:
+%
+\begin{equation}\begin{split}
+  \Lambda_i(p+w)\leq\lambda_i\forall w\in\mathcal W(p)\\
+  \Lambda_i p+\underbrace{\max_{w\in\mathcal W(p)}\Lambda_i w}_{(\dagger)}\leq\lambda_i
+\end{split}\end{equation}
+%
+The term~$(\dagger)$ is a multi parametric linear program (mpLP), we less interested in the objective value of~$(\dagger)$ but rather in the shape of its solution over~$p$ since it defines the shape of the set of points which can only just be taken to $P_i$ for an extremal value of $w\in\mathcal W(p)$.
+%
+We exploit the linearity of the objective function to argue that only vertices of~$\mathcal W(p)$ are candidates to be the maximiser in~$(\dagger)$.
+%
+According to Corollary~\ref{thm:combinatorical:equivalence:alternative} there exists a fixed map~$T$ such that 
+%
+\begin{equation}
+  \begin{pmatrix}w_1\\ \vdots\\ w_N\end{pmatrix} = \underbrace{\begin{pmatrix}T_1\\ \vdots\\ T_N\end{pmatrix}}_T t(p)
+\end{equation}
+%
+defines all vertices $\mathcal W(p) = \conv\{w_1(t(p)),\dots,w_N(t(p))\}$ for a element-wise convex piecewise affine function $t(p)$.
+%
+It is easy to see that the choice $t_i(p)=d_i(p)$ again leads us to the epigraph~$\epi(d_i)$ and therefore that the maximisation~$(\dagger)$ becomes
+%
+\begin{equation}\label{eq:rewriting:pontryagin:diff:without:facet:constraint}
+  \max_{w\in\mathcal W(p)}\Lambda_i w = \left\{\begin{array}{rl}
+  \min& \tau\\
+  \text{s.t.}& \Lambda_iT_jt\leq\tau\\
+  & B_i+C_ip\leq t_i\\
+  & j\in\{1,\dots,N\}
+  \end{array}\right.
+\end{equation}
+%
+further, the solution to~\eqref{eq:rewriting:pontryagin:diff:without:facet:constraint} is only relevant for such~$p$ that can be taken to~$P_i$ for some $i\in\{1,\dots,q\}$.
+%
+We can add that constraint to~\eqref{eq:rewriting:pontryagin:diff:without:facet:constraint} in order to obtain a linear program that is only feasible on the points which can be taken to $P_i$ for feasible $w$:
+%
+\begin{equation}\label{eq:rewriting:pontryagin:diff:with:facet:constraint}
+  \begin{array}{rl}
+  \min& \tau\\
+  \text{s.t.}& \Lambda_iT_jt\leq\tau\\
+  & B_j+C_j p\leq t_j\\
+  &\Lambda_i p + \tau=\lambda_i\\
+  &\Lambda_l(p + T_jt)\leq\lambda_l\\
+  &l\neq i, j\in\{1,\dots,N\}
+  \end{array}
+\end{equation}
+%
+Notice that we are only interested in the feasible~$p$ rather than the objective value of~\eqref{eq:rewriting:pontryagin:diff:with:facet:constraint}, i.e.
+$p$ such that there exist $t$ and $\tau$ such that
+%
+\begin{equation}
+  (p,t,\tau)\in\tilde P_i=\left\{(p,t,\tau):\begin{array}{rcl}
+  \Lambda_iT_jt&\leq&\tau\\
+  B_k+C_k p&\leq& t_k\\
+  \Lambda_i p + \tau&=&\lambda_i\\
+  \Lambda_l(p + T_jt)&\leq&\lambda_l\\
+  \end{array},\begin{array}{rcl}
+   l&\neq& i\\
+   j&\in&\{1,\dots,N\}\\k&\in&\{1,\dots,q\}\end{array}
+   \right\}
+\end{equation}
+%
+but this is the definition of the projection onto $\mathbb R^d$, $\pi_d(Q)$.
+%
+With this the boundary of $S\ominus \mathcal W(S)$ is given as the union of projections:
+%
+\begin{equation}\label{eq:boundary:S:ominus:WS}
+ \partial(S\ominus\mathcal W(S)) = \bigcup_{i\in\{1,\dots,q\}}\pi_d\left(
+\tilde P_i
+ \right)
+\end{equation}
+%
+The simplest way to use~\eqref{eq:boundary:S:ominus:WS} is to use a vertex description of $\tilde P_i$:
+%
+\begin{equation}\label{the:way:we:compute:p:pontryagin:differences}
+  \text{vert}(S\ominus\mathcal W(S)) = \bigcup_{i\in\{1,\dots,q\}}\pi_d(\text{vert}(\tilde P_i))
+\end{equation}
 
-\section{Numerical Examples}
+We further propose an alternative way of computing $S\ominus\mathcal W(S)$:
+%
+Instead of using~$\tilde P_i$ which are points~$p$ that can be taken to $P_i$ for a feasible $w\in\mathcal W(p)$ and the values of the~$d_i(p)$ and so on, we obtain all feasible~$p$ such that a feasible $w\in\mathcal W(p)$ exists such that $p+w$lies on the boundary of $S$.
+%
+\begin{equation}
+  L = \left\{(p,t,\tau):\begin{array}{rcl}
+  \Lambda_iT_jt&\leq&\tau_i\\
+  B_i+C_i p&\leq& t_i\\
+  \Lambda_i p + \tau_i&\leq&\lambda_i\\
+  \end{array},\begin{array}{rcl}
+  j&\in&\{1,\dots,N\}\\
+  i&\in&\{1,\dots,q\}\end{array}
+  \right\}
+\end{equation}
+%
+The set~$L$ contains all such $p$ for which there exists a feasible $w\in\mathcal W(p)$ such that $p+w\in S$ and hence the projection $\pi_d(L)=S\ominus\mathcal W(S)$, which does not require a vertex enumeration.
+%
+%
+%
+%
+%
+\section{Numerical Examples}\label{sec:numerical:examples}
 \subsection{Norm bound sets}
@@
 
-Characterising the parametric Pontryagin difference~$X\ominus\mathcal W(X) = \{z\in\mathbb R^2:z+w\in X\;\forall w\in\mathcal W(x)\}$ is done by characterising its boundary.
-%
-This is done by finding points~$z$ which for some~$w\in\mathcal W(z)$ can be taken to the boundary of $X$.
-%
-For the face given by $P_i = \{x:\Lambda_i x=\lambda_i\wedge\Lambda_j x\leq \lambda_j,j\neq i\}$, we find the face(s) of $X\ominus\mathcal W(X)$ by finding extremal values of $w\in\mathcal W(P_i)$ defining it, i.e.
-the extremal values of
-%
-$$
-  \Lambda_i(z+w)=\lambda_i\; w\in\mathcal W(z)\wedge \Lambda_j(z+w)\leq\lambda_j,j\neq i.
-$$
-%
-To do this, we rewrite the problem as a maximisation
-%
-$$
-\begin{array}{rl}\max& \Lambda_i w \\ \text{s.t.}& w\in\mathcal W(z)\\ &\Lambda_i (z + w) = \lambda_i\\
-&\Lambda_j(z+w)\leq \lambda_j\end{array}
-$$
-%
-We now exploit the fact that we have a vertex description of the set-valued map $\mathcal W(x) = \bigl\{w:F w\leq{\bf{1}}\max_{k\leq n}\{F_kx\}\bigr\}$ and with the auxiliary variable~$\max_{k\leq n}\{F_k x\} = t$ we rewrite $\mathcal W(x) = \conv\{w_i(t(x))\}$ using the vertices
+In order to apply the method described in Section~\ref{ssec:computation:p:pontryagin:difference} we a require map $T$ such that 
 %
@@
 %
-With this the set of points for which there exists a feasible $w\in\mathcal W$ reaching the face $P_i$ is given as the projection
+holds, but this becomes trivial as $t=\max_{k\leq n} \{F_kx\}$ is a scalar.
 % 
+The sets $\tilde P_i$ and $L$ are given by
+%
+% Characterising the parametric Pontryagin difference~$X\ominus\mathcal W(X) = \{z\in\mathbb R^2:z+w\in X\;\forall w\in\mathcal W(z)\}$ is done by characterising its boundary.
+% %
+% This is done by finding points~$z$ which for some~$w\in\mathcal W(z)$ can be taken to the boundary of $X$.
+% %
+% For the face given by $P_i = \{x:\Lambda_i x=\lambda_i\wedge\Lambda_j x\leq \lambda_j,j\neq i\}$, we find the face(s) of $X\ominus\mathcal W(X)$ by finding extremal values of $w\in\mathcal W(P_i)$ defining it, i.e.
+the extremal values of
+% %
+% $$
+%   \Lambda_i(z+w)=\lambda_i\; w\in\mathcal W(z)\wedge \Lambda_j(z+w)\leq\lambda_j,j\neq i.
+% $$
+% %
+% To do this, we rewrite the problem as a maximisation
+% %
+% $$
+% \begin{array}{rl}\max& \Lambda_i w \\ \text{s.t.}& w\in\mathcal W(z)\\ &\Lambda_i (z + w) = \lambda_i\\
+% &\Lambda_j(z+w)\leq \lambda_j\end{array}
+% $$
+% %
+% We now exploit the fact that we have a vertex description of the set-valued map $\mathcal W(x) = \bigl\{w:F w\leq{\bf{1}}\max_{k\leq n}\{F_kx\}\bigr\}$ and with the auxiliary variable~$\max_{k\leq n}\{F_k x\} = t$ we rewrite $\mathcal W(x) = \conv\{w_i(t(x))\}$ using the vertices
+% %
+% $$
+% \begin{pmatrix}
+% w_1\\ \vdots \\ w_n
+% \end{pmatrix} = \begin{pmatrix}T_1\\\vdots\\T_n\end{pmatrix}{\bf{1}}t(x).
+% $$
+% %
+% With this the set of points for which there exists a feasible $w\in\mathcal W$ reaching the face $P_i$ is given as the projection
+% %
 $$
-\pi_2\left(\left\{(z,t,\tau): \begin{array}{rcl}\Lambda_i Tt &\leq& \tau\\ Fz&\leq& t\\ \Lambda_i(z+\tau)&=&\lambda_i\\ \Lambda_j(z+T_lt)&\leq&\lambda_j\end{array},j\neq i,l\in\{1,\dots,n\}\right\}\right)
+\tilde P_i= \left\{(z,t,\tau): \begin{array}{rcl}\Lambda_i Tt &\leq& \tau\\ Fz&\leq& t\\ \Lambda_i(z+\tau)&=&\lambda_i\\ \Lambda_j(z+T_lt)&\leq&\lambda_j\end{array},j\neq i,l\in\{1,\dots,n\}\right\}
 $$
 %
-This then gives us all points $z$ for which a feasible $w$ can be found such that $z+w\in P_i$, by combining all such projections we obtain the representation of $X\ominus\mathcal W(X)$.
-%
-Alternatively, the set~$X\ominus\mathcal W(X)$ can be obtained by a single projection of the higher dimensional set:
+and
+% %
+% This then gives us all points $z$ for which a feasible $w$ can be found such that $z+w\in P_i$, by combining all such projections we obtain the representation of $X\ominus\mathcal W(X)$.
+% %
+% Alternatively, the set~$X\ominus\mathcal W(X)$ can be obtained by a single projection of the higher dimensional set:
 $$
-\pi_2\left(\left\{(z,t,\tau_1,\dots,\tau_q):\begin{array}{rcl}
+L = \left\{(z,t,\tau_1,\dots,\tau_q):\begin{array}{rcl}
 \Lambda_i Tt & \leq &\tau_i\\
@@
 \Lambda_i(z+\tau_i)&\leq&\lambda_i
-\end{array},i\in\{1,\dots,q\}\right\}\right)
+\end{array},i\in\{1,\dots,q\}\right\}
 $$
+% %
+% However, in practical application the increase in computation time of projecting a $d+q+1$ polyhedron onto $d$ instead of projecting a $d+2$ polyhedron onto $d$ $q$ times is usually prohibitively large.
 %
-However, in practical application the increase in computation time of projecting a $d+q+1$ polyhedron onto $d$ instead of projecting a $d+2$ polyhedron onto $d$ $q$ times is usually prohibitively large.
+respectively.
 
-For the choice~$\kappa=0.2$ and~$n = 35$ the set~$X\ominus\mathcal W(X)$ is illustrated in Figure~\ref{fig:example:parametric:pontryagin:difference}.
+For the choice~$\kappa=0.2$ and~$n = 35$ the set~$X\ominus\mathcal W(X)=\pi_2(L)=$\linebreak $\conv\{\cup_{i\in\{1,\dots,4\}}\pi_2(\text{vert}(\tilde P_i)\}$ is illustrated in Figure~\ref{fig:example:parametric:pontryagin:difference}.
 
@@
 \end{figure}
+%
+%
+%
+%
+%
+\section{Conclusion}\label{sec:conclusion}
+%
+%
+%
+In this paper we presented a way to extend the scope of the Pontryagin difference to a wider class of sets.
+%
+We introduced the framework of parametric convexity and some of its analysis, which proved to be essential to prove the convexity of the parametric Pontryagin difference.
+%
+Furthermore we provided the link required to make the parametric Pontryagin difference computationally accessible for polytopic sets, it relied fully on the combinatorial nature of the subtrahend set-valued map.
+%
+Using two simple examples we illustrated the potency of the proposed methodology.
+
+The parametric Pontryagin difference has been applied successfully in a robust control environment~\cite{Schaich:2015,Schaich:2015a} and will continue to extend its scope of application.
 

### 2016-07-26 draft.tex
Added Abstract and Highlights.
what happened

[ticket: X]

@@
-\documentclass[review]{elsarticle}
+\documentclass{elsarticle}
 
@@
 
-\title{Operations on Parametrised Polytopes\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
+\title{Explicit Operations on Parametrised Polytopes}
+% \tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
 
@@
 \begin{abstract}
-The abstract goes here.
+The Pontryagin set difference is a commonly used operation between two polytopes to calculate a set of safe operation.
+%
+We suggest to use a particular class of set-valued maps as the subtrahend, for this we introduce the property of parametric convexity and present some of its analytic framework.
+%
+In order to guarantee the convexity of the difference of a convex minuend and a set-valued map it proves necessary and sufficient to have the parametrically convexity property of the set-valued map.
+%
+For generic piecewise polyhedral set-valued maps we prove that parametric convexity is equivalent to a constant combinatorial structure of all its realisations.
+%
+We present a computational way of verifying parametric convexity of a piecewise polyhedral set-valued map as well as a way to calculate the parametric Pontryagin difference between a polyhedron and a piecewise polyhedral set-valued map.
+%
+Two examples are used to illustrate the presented methodology.
 \end{abstract}
@@
 \begin{keyword}
-keyword one \sep keyword two
+Parametric Convexity \sep Piecewise Affine Set-Valued Map \sep Pontryagin Difference
 \end{keyword}
@@
 
-\linenumbers
+% \linenumbers
 
@@
 %
-When the Pontryagin differnece has to be performed explicitly by numeric algorithms it is almost imperative that the respective sets are polytopic, since it is not possible to operate on general sets explicitly.
+When the Pontryagin difference has to be performed explicitly by numeric algorithms it is usually assumed that the respective sets are polytopic, since it is not possible to operate on general sets explicitly.
 %
@@
 %
-The sets on which these operations can be performed are fixed predetermined polytopes, due to their physical interpretation safe sets, it can be desirable to extend the class of sets on which these operations can be performed.
+The sets on which these operations can be performed are fixed predetermined polytopes but, due to their physical interpretation safe sets, it can be desirable to extend the class of sets on which these operations can be performed.
 %
@@
 %
-However, computational aspects of operations on set-valued maps are largely unknown, we refer to~\cite{Finzel:2000} for some results for polyhedral set-valued maps.
+However, computational aspects of operations on general set-valued maps are largely unknown, we refer to~\cite{Finzel:2000} for some results for polyhedral set-valued maps.
 %
@@
 %
-The set-valued maps we consider are parametrised polytopes with the so called \emph{parametric convexity} property which allows us to guarantee that the \emph{parametric Pontryagin difference} is convex for all convex minuend sets.
+The set-valued maps we consider are parametrised polytopes with a property we introduce as \emph{parametric convexity} which allows us to guarantee that the \emph{parametric Pontryagin difference} is convex for all convex minuend sets.
 %
@@
 %
-In Section~\ref{sec:preliminaries} we summarise preliminaries we require throughout the paper, in Section~\ref{sec:parametric:convexity} we introduce parametric convexity the essential ingredient for all subsequent analysis and provide analytic results for the set operations, which we refine and extend for set-valued maps with polyhedral realisations in Section~\ref{sec:polyhedral:maps}.
+In Section~\ref{sec:preliminaries} we summarise preliminaries we require throughout the paper, in Section~\ref{sec:parametric:convexity} we introduce parametric convexity, the essential ingredient for all subsequent analysis and provide analytic results for the set operations we refine and extend for set-valued maps with polyhedral realisations in Section~\ref{sec:polyhedral:maps}.
 %
@@
 %
-We denote index sets by $\mathcal A$ or $\mathcal I$, by $f\vert_\Omega$ we mean $f$ evaluated only on values in $\Omega$.
-%
-The standard Minkowski sum~\cite{Minkowski:1911} of the sets $X_1,X_2$ is denoted by $X_1\oplus X_2$
+We denote index sets by $\mathcal A,\,\mathcal J$ or $\mathcal I$, the complement of a subset of an index set $\mathcal I\subset\mathcal A$ is denoted by $\bar{\mathcal I}=\mathcal A\setminus\mathcal I$, the objects $a_{\mathcal I}$ and $b_{\mathcal I}$ denote the matrix and the column vector with rows given by the row vectors $a_i$ and the scalar values $b_i$ with $i\in\mathcal I$.
+%
+By $f\vert_\Omega$ we mean $f$ evaluated only $\Omega$, a ball centred around $c$ of radius $r$ is denoted by $B_r(z)=\{x:\norm{x-z}_2\leq\epsilon\}$ with the Euclidean norm $\norm{\cdot}_2$.
+%
+The Minkowski sum~\cite{Minkowski:1911} of the sets $X_1,X_2$ is denoted by $X_1\oplus X_2$, for a $d_2$ dimensional set $X$ the projection onto $\mathbb R^{d_1}$ with $d_1\leq d_2$ is denoted by $\pi_{d_1}(X) = \{x\in\mathbb R^{d_1}:\exists \tilde x\in\mathbb R^{d_2-d_1} (x,\tilde x)\in X\}$.
+%
+For a polytopic set $X$ the set of its vertices is denoted by $\text{vert}(X)$.
 %
@@
 Throughout the paper we deal with set-valued maps, i.e.
-functions that map an element of a metric space~$Y$ to a subset of a metric space~$Z$: $f:Y\mapsto\mathscr P(Z), Y\ni y\rightarrow f(y)\subset Z$.
+functions that map an element of a metric space~$Y$ to a subset of a metric space~$Z$, that is $f:Y\mapsto\mathscr P(Z), Y\ni y\rightarrow f(y)\subset Z$.
 %
@@
 %
-has a continuous boundary, for every bounded point $(y,z)\in\partial\mathscr G(f)$ the boundary $\partial\mathscr G(f)$ is locally given by the graph of a continuous function.
-%
-We only consider set-valued maps with convex images, i.e. such maps for which $z_1,z_2\in f(y)\Rightarrow \lambda z_1+(1-\lambda)z_2\in f(y)$ for all $\lambda\in[0,1]$ holds for all $y\in Y$.
-
-An important subset of such set-valued maps are such that their realisations are polytopic, $f(y)$ is a polytope for all $y\in Y$, in particular we study maps which depend on the \emph{parameter} in a piecewise affine way.
+has a continuous boundary, i.e. for every bounded point $(y,z)\in\partial\mathscr G(f)$ the boundary $\partial\mathscr G(f)$ is locally given by the graph of a continuous function.
+%
+We only consider set-valued maps with convex images, i.e. maps for which $z_1,z_2\in f(y)\Rightarrow \lambda z_1+(1-\lambda)z_2\in f(y)$ for all $\lambda\in[0,1]$ holds for all $y\in Y$.
+
+An important subset of such set-valued maps are such that their realisations are polytopic, i.e.
+$f(y)$ is a polytope for all $y\in Y$, in particular we study maps which depend on the \emph{parameter} in a piecewise affine way.
 %
@@
 The particular property we require is \emph{simplicity}, for each $y\in Y$ the set $f(y)$ is a polytope and each of its vertices~$v(y)$ is supported by a minimal number of hyperplanes, i.e.
-there exists linear system defining the set~$f(y) = \{z:A(y)z\leq b(y)\}$ and each vertex $v(y)$ is defined by $n$ hyperplanes $A_{\mathcal I}(y)v(y)=b_{\mathcal I}(y)$ and $A_{\bar{\mathcal I}}(y)v(y)<b_{\bar{\mathcal I}}(y)$.
+there exists a linear system defining the set~$f(y) = \{z:A(y)z\leq b(y)\}$ and each vertex $v(y)$ is defined by $n$ hyperplanes $A_{\mathcal I}(y)v(y)=b_{\mathcal I}(y)$ and $A_{\bar{\mathcal I}}(y)v(y)<b_{\bar{\mathcal I}}(y)$.
 %
@@
 
-The induced graph~$G(P)$ of a polytope~$P$ is the graph for which the vertices and edges coincide with the vertices and edges of the polytope itself~\cite{Bondy:2008}.
+The induced graph~$G(P)$ of a polytope~$P$ is the graph with vertices and edges that coincide with the vertices and edges of the polytope itself~\cite{Bondy:2008}.
 %
@@
 %
-This property is then used to demonstrate the convexity of a generalised Pontryagin difference (see e.g.~\cite{Hadwiger:1950,blanchini:2007}). 
+This property is then used to demonstrate the convexity of a generalised Pontryagin difference operation (see e.g.~\cite{Hadwiger:1950,blanchini:2007}). 
 %
@@
 %
-A similar definition was given in~\cite{Hadwiger:1957} for scalar families of sets ($d=1$), however the results presented are of no particular use for us here.
+A similar definition was given in~\cite{Hadwiger:1957} for scalar families of sets ($d=1$), however the results presented are not directly related.
 
@@
 \begin{equation*}  
-\text{int}(\mathscr G(\mathcal W)) = \{(p,z) \in Y\times Z : \forall \zeta\in\mathbb R^n\exists \epsilon>0, \, z+\epsilon \zeta\in \mathcal W(p) \}
+\text{int}(\mathscr G(\mathcal W)) = \{(p,z) \in Y\times Z : \forall \zeta\in\mathbb R^n\;\exists \epsilon>0, \, z+\epsilon \zeta\in \mathcal W(p) \}
 \end{equation*}
@@
 %
-Note that the sets are defined in the space of the \emph{set variable} $z\in Y$ rather than \emph{graph variable} $(p,z)\in Y\times Z$.
+Note that the sets in Definition~\ref{def:graph:of:map} are defined in the space of the \emph{set variable} $z\in Y$ rather than \emph{graph variable} $(p,z)\in Y\times Z$.
 %
@@
 %
+Furthermore, since $\lambda(p_1,z_1)+(1-\lambda)(p_2,z_2)\not\in \text{int}(\mathscr G(\mathcal W))$ and both $(p_1,z_1)$ and $(p_2,z_2)$ die on the boundary either $z_1-z_2$ or $z_2-z_1$ is outward facing for both $\mathcal W(p_1)$ and $\mathcal W(p_2)$, therefore either $z_1-z_2$ or $z_2-z_1$ is in $\mathcal N\mathcal W(p_1,z_1)$ and $\mathcal N\mathcal W(p_2,z_2)$ and hence in their intersection.
 
@@
 %
-\begin{cor}
+\begin{cor}\label{thm:inequalities:convex:concave}
 %
@@
 %
-To the authors' best knowledge the the literature on piecewise polyhedral sets is limited, we refer to~\cite{Finzel:2000}, however properties of general set-valued maps are known and applicable, see e.g.~\cite{Aubin:2009}.
-
+To the authors' best knowledge the literature on piecewise polyhedral sets is limited to~\cite{Finzel:2000}, however properties of general set-valued maps are known and applicable, see e.g.~\cite{Aubin:2009}.
+%
+\begin{rem}
+%
+Notice that the boundary of a polytope is locally convex, i.e. concave but not strictly concave, it is locally strictly convex only around lower dimensional faces (vertices, edges, etc.) .
+%
+This trivial but important fact is exploited throughout the following statements. 
+%
+As long as the boundary $\partial\mathscr G(\mathcal W)$ is locally affine in $p\in Y$ Corollary~\ref{thm:inequalities:convex:concave} applies. 
+%
+Conversely if the boundary $\partial\mathscr G(\mathcal W)$ is locally given by more than one affine function in $p\in Y$ (determined by linear inequalities), then it is locally strictly convex and can therefore not be parametrically convex.
+\end{rem}
+%
 \begin{cor}\label{thm:polytopic:set:not:p:convex}
-The polytopic parametric set valued map $\mathcal W(p):=\{z: a_i z + b_i p\leq c_i \; \forall i\in\{1,\dots,m\}\}$
+The polytopic parametric set-valued map $\mathcal W(p):=\{z: a_i z + b_i p\leq c_i \; \forall i\in\{1,\dots,m\}\}$
 is not parametrically convex for any non-zero matrix $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$.
@@
 %
-\begin{rem}
-%
-Recall that the graph $\mathscr G(\mathcal W)$ of a set-valued map can not be strictly convex anywhere in order for $\mathcal W$ to be parametrically convex. 
-%
-Therefore, Corollary~\ref{thm:polytopic:set:not:p:convex} is only a global statement.
-\end{rem}
+We now present the central theorem of this work, which holds for piecewise affine polytopic set-valued maps which are generic, which implies two things, their realisation is simple and further no more than one structural component changes at a time.
+%
+The second assumption will become clearer in the proof of the central statement for piecewise affine polytopic set-valued maps and makes the statement of Theorem~\ref{thm:p:convexity:graph} more specific.
 %
@@
 This means that there exists a finite partition of $Y\subseteq\mathbb R^d$ into convex polyhedra 
-$\mathcal P_j$ such that $\bigcup_{j\in\mathbb N_t} \mathcal P_j = Y$ and 
+$\mathcal P_j$ such that $\bigcup_{j\in\mathcal I} \mathcal P_j = Y$ and 
 ${\bf{k}}^\ast(p) = (k_1^\ast(p),\dots,k_m^\ast(p))$ is constant for all $p \in \mathcal P_j$.
@@
 \begin{equation*}
-  \mathscr G(\mathcal W) = \bigcup_{j\in\mathbb N_t} \left\{z\in\mathbb R^n: a_i z \leq b_{i,k_i^\ast} + c_{i,k_i^\ast}p \; \forall i \in\mathbb N_m \right\}\bigr\vert_{\mathcal P_{j}}
+  \mathscr G(\mathcal W) = \bigcup_{j\in\mathcal I} \left\{z\in\mathbb R^n: a_i z \leq b_{i,k_i^\ast} + c_{i,k_i^\ast}p \; \forall i \in\{1,\dots,m\} \right\}\bigr\vert_{\mathcal P_{j}}
 \end{equation*}
@@
 Notice that a vertex $v_\kappa(p)$ is defined by \emph{active} and \emph{inactive} inequalities, namely $\mathcal A_\kappa(p)$ and
-$\mathcal I_\kappa(p) = \{1,\dots,m\}
-%\{1,\dots,m\}
-\setminus\mathcal A_\kappa(p)$ respectively, where
+$\bar{\mathcal A}_\kappa(p)$ respectively, where
 %
@@
   a_i v_\kappa(p) &= b_{i,k_i^\ast} + c_{i,k_i^\ast} p \quad\forall i\in\mathcal A_\kappa(p)\\
-  a_i v_\kappa(p) &< b_{i,k_i^\ast} + c_{i,k_i^\ast} p \quad\forall i\in\mathcal I_\kappa(p) .
+  a_i v_\kappa(p) &< b_{i,k_i^\ast} + c_{i,k_i^\ast} p \quad\forall i\in\bar{\mathcal A}_\kappa(p) .
 \end{split}\end{equation*}
 %
-Since $\mathcal W(p)$ is assumed to be generic, it has to be generic for almost every~$p\in Y$, which means it is \emph{simple}, i.e.
-each vertex is defined by exactly $n$ active inequalities $\abs{\mathcal A_\kappa(p)}=n$ for all $p\in Y$ and all $\kappa$.
+Since $\mathcal W(p)$ is simple almost everywhere in~$Y$, i.e. each vertex is defined by exactly $n$ active inequalities $\abs{\mathcal A_\kappa(p)}=n$ for all $p\in Y$ and all $\kappa$.
 %
@@
 Hence on the hyperplane $fp=g$, both the maximising index ${\bf{k}}^\ast(p)$ and the active index sets $\mathcal A_{\kappa_1}(p)$ 
-and $\mathcal A_{\kappa_2}(p)$ must change, which implies that the problem is degenerate.
+and $\mathcal A_{\kappa_2}(p)$ must change, which implies that this problem is degenerate.
 %
@@
 \begin{align*}
-  \frac{d}{dp}\left(  {\bf{a}}_{\mathcal J\cup \{s\}} v_{\kappa_1}(p) - {\bf{b}}_{\mathcal J\cup \{s\}} - 
-  {\bf{c}}_{\mathcal J\cup \{s\},{\bf{k}}^\ast} p\right) &= 0\\
-  \frac{d}{dp}\left(  {\bf{a}}_{\mathcal J\cup \{u\}} v_{\kappa_2}(p) - {\bf{b}}_{\mathcal J\cup \{u\}} - 
-  {\bf{c}}_{\mathcal J\cup \{u\},{\bf{k}}^\ast} p\right) &= 0
+  \frac{d}{dp}\left(  a_{\mathcal J\cup \{s\}} v_{\kappa_1}(p) - b_{\mathcal J\cup \{s\}} - 
+  c_{\mathcal J\cup \{s\},{\bf{k}}^\ast} p\right) &= 0\\
+  \frac{d}{dp}\left(  a_{\mathcal J\cup \{u\}} v_{\kappa_2}(p) - b_{\mathcal J\cup \{u\}} - 
+  c_{\mathcal J\cup \{u\},{\bf{k}}^\ast} p\right) &= 0
 \end{align*}
 %
-implies
+which implies
 \begin{align*}
-  {\bf{a}}_{\mathcal J\cup \{s\}} \frac{dv_{\kappa}}{dp} &= {\bf{c}}_{\mathcal J\cup \{s\},{\bf{k}}^\ast}\\
-  {\bf{a}}_{\mathcal J\cup \{u\}} \frac{dv_{\kappa}}{dp} &= {\bf{c}}_{\mathcal J\cup \{u\},{\bf{k}}^\ast}
+  a_{\mathcal J\cup \{s\}} \frac{dv_{\kappa}}{dp} &= c_{\mathcal J\cup \{s\},{\bf{k}}^\ast}\\
+  a_{\mathcal J\cup \{u\}} \frac{dv_{\kappa}}{dp} &= c_{\mathcal J\cup \{u\},{\bf{k}}^\ast}
 \end{align*}
@@
 \begin{equation}\label{eq:derivative:condition:on:index:sets}
-  \frac{dv_\kappa}{dp} = {\bf{a}}_{\mathcal J\cup \{s\}}^{-1}{\bf{c}}_{\mathcal J\cup \{s\},{\bf{k}}^\ast} = 
-  {\bf{a}}_{\mathcal J\cup \{u\}}^{-1}{\bf{c}}_{\mathcal J\cup \{u\},{\bf{k}}^\ast}
+  \frac{dv_\kappa}{dp} = a_{\mathcal J\cup \{s\}}^{-1}c_{\mathcal J\cup \{s\},{\bf{k}}^\ast} = 
+  a_{\mathcal J\cup \{u\}}^{-1}c_{\mathcal J\cup \{u\},{\bf{k}}^\ast}
 \end{equation}
@@
 %
-It is worth pointing out that Corollary~\ref{thm:p:convexity:PWA:set:constant:num:verts} can be reformulated in a numerically helpful way:
+It is worth pointing out that Corollary~\ref{thm:p:convexity:PWA:set:constant:num:verts} can be reformulated in a numerically useful way:
 %
@@
 %
-It is clear that as long as all complexes $\mathcal A_\kappa(p)=\mathcal A_\kappa$ are constant all faces of $\mathcal W(p)$ are defined as intersections of the same set of half spaces.
-%
-Although the shape of~$\mathcal W(p)$ might change its combinatorial structure does not, furthermore the combinatorial structure of $\mathcal W(p)$ is not affected by changes of the right hand side.
-%
-The \emph{Perles' Conjecture}~\cite{Kalai:1988}, states that the combinatorial structure of a simple polytope is uniquely determined by its graph, that is, as long as the graph of~$\mathcal W(p)$ remains unchanged so does its combinatorial structure.
-%
-The induced graph of a polytope is given by the vertices and the edges of a polytope, since we have that the number of vertices remains unchanged throughout~$Y$ for $\mathcal W(p)$ the induced graph $G(\mathcal W(p))$ has to have a constant number of vertices.
+It is clear that as long as all complexes in proof~\ref{thm:p:convexity:PWA:set:constant:num:verts}, $\mathcal A_\kappa(p)=\mathcal A_\kappa$ are constant, all faces of $\mathcal W(p)$ are defined as intersections of the same set of half spaces.
+%
+Although the shape of~$\mathcal W(p)$ might change its, combinatorial structure does not, furthermore the combinatorial structure of $\mathcal W(p)$ is not affected by changes of the right hand side.
+%
+The \emph{Perles' Conjecture}~\cite{Kalai:1988}, states that the combinatorial structure of a simple polytope is uniquely determined by its graph, that is, as long as the induced graph of~$\mathcal W(p)$ remains unchanged so does its combinatorial structure.
+%
+The induced graph of a polytope is given by the vertices and the edges of a polytope, and since we have that the number of vertices remains unchanged throughout~$Y$ for $\mathcal W(p)$, the induced graph $G(\mathcal W(p))$ has to have a constant number of vertices.
 %
@@
 %
-This allows for efficient numerical treatment, since we know how the vertices are defined~$\mathcal A_\kappa = const$.
-%
-We will illustrate how we exploit this property for our benefit in the Section~\ref{sec:computational:methods} and~\ref{sec:numerical:examples}.
+This allows for efficient numerical treatment, since we know how the vertices are defined, i.e.~$\mathcal A_\kappa = const$.
+%
+We will illustrate how we exploit this property in Section~\ref{sec:computational:methods} and~\ref{sec:numerical:examples}.
 %
@@
 %
-We have also seen that set-valued maps with polyhedral realisations $\mathcal W(p)$ the number of vertices and rays must not change throughout the parameter space~$Y$.
+We have also seen that for set-valued maps with polyhedral realisations $\mathcal W(p)$, the number of vertices and rays must not change throughout the parameter space~$Y$ in order that $\mathcal W(p)$ is parametrically convex.
 %
@@
 %
-For notational convenience let $d_i(p) = \max_k\{b_{i,k}+c_{i,k}p\}$ denote the right hand side of~\eqref{eq:definition:PWA:polytopic:set:general}, i.e.
-$\mathcal W(p) = \{z\in\mathbb R^n: a_i z\leq d_i(p)\;\forall i\in\{1,\dots,m\}\}$.
-%
-It is equivalent to study~$d_i$ and its \emph{epigraph} 
-%
-$$
-	\epi(d_i) = \{(p,t)\in Y\times\mathbb R: d_i(p)\leq t\}
+For notational convenience let $\phi_i(p) = \max_k\{b_{i,k}+c_{i,k}p\}$ denote the right hand side of~\eqref{eq:definition:PWA:polytopic:set:general}, i.e.
+$\mathcal W(p) = \{z\in\mathbb R^n: a_i z\leq \phi_i(p)\;\forall i\in\{1,\dots,m\}\}$.
+%
+It is equivalent to study~$\phi_i$ and its \emph{epigraph} 
+%
+$$
+	\epi(\phi_i) = \{(p,t)\in Y\times\mathbb R: \phi_i(p)\leq t\}
 $$
@@
 %
-of $\epi(d_i)$ there exists a maximiser~$k_j$ such that~$d_i$ is defined by~$d_i(p)=b_{i,k_j}+c_{i,k_j}p$ for all $p\in\pi_d(F_j)$ or equivalently~$d_i(p)=\sum_{f}\lambda_f t_{j,f}$ with ${\bf{0}}\leq\lambda\leq{\bf{1}}$ such that $p=\sum_{f}\lambda_f p_{j,f}$.
+of $\epi(\phi_i)$ there exists a maximiser~$k_j$ such that~$\phi_i$ is defined by~$\phi_i(p)=b_{i,k_j}+c_{i,k_j}p$ for all $p\in\pi_d(F_j)$ or equivalently~$\phi_i(p)=\sum_{f}\lambda_f t_{j,f}$ with ${\bf{0}}\leq\lambda\leq{\bf{1}}$ such that $p=\sum_{f}\lambda_f p_{j,f}$.
 %
 Notice that if~\eqref{eq:conv:hull:facet:of:epigraph} is redundant, i.e.
-not all elements are vertices of $F_j$, the statement is still true, and we can write $d_i(p)$ as a convex combination of points.
+not all elements are vertices of $F_j$, then the statement is still true, and we can write $\phi_i(p)$ as a convex combination of points.
 
@@
 %
-It is worth pointing out that we only assume any such polyhedral complex, in particular we do not consider it to be minimal, since the minimal such complex could have non-convex elements, those elements can however be partitioned such that every element of the non-minimal $\mathcal C$ are convex polyhedra.
+It is worth pointing out that any such polyhedral complex is not assumed to be minimal, since the minimal such complex could have non-convex elements, those elements can however be partitioned such that every element of the non-minimal $\mathcal C$ are convex polyhedra.
 %
@@
 \begin{equation}
-  E=\left\{(p,t_1,\dots,t_m)\in Y\times\mathbb R^{m}:d_i(p)\leq t_i\right\}
+  E=\left\{(p,t_1,\dots,t_m)\in Y\times\mathbb R^{m}:\phi_i(p)\leq t_i\right\}
 \end{equation}
@@
 %
-The set of vertices of elements in the complex coincides with the union of all vertices of $d$-dimensional faces of $\epi(d_i)$ for all $i\in\mathbb N_m$, i.e.
-%
-$$
-	\bigcup_{P\in\mathcal C}\text{vert}(P) = \bigcup_{(\ast)} \text{vert}(\pi_d(F)) = \bigcup_{i\in\mathbb N_m}\pi_d(\text{vert}(\epi(d_i))),
-$$
-%
-with $(\ast) = \{F: d-\text{dimensional face of } \epi(d_i) \text{ for some } i\in\mathbb N_m\}$.
+The set of vertices of elements in the complex coincides with the union of all vertices of $d$-dimensional faces of $\epi(\phi_i)$ for all $i\in\{1,\dots,m\}$, i.e.
+%
+$$
+	\bigcup_{P\in\mathcal C}\text{vert}(P) = \bigcup_{(\ast)} \text{vert}(\pi_d(F)) = \bigcup_{i\in\{1,\dots,m\}}\pi_d(\text{vert}(\epi(\phi_i))),
+$$
+%
+with $(\ast) = \{F: d-\text{dimensional face of } \epi(d_i) \text{ for some } i\in\{1,\dots,m\}\}$.
 %
@@
 $$\abs{\text{vert}(\mathcal W(p))} = \text{const.}\quad \forall p\in\mathcal D$$.
+%
+then Corollary~\ref{thm:p:convexity:PWA:set:constant:num:verts} holds and $\mathcal W(p)$ is parametrically convex, furthermore enumerating the vertices of $\mathcal W(p)$ for any fixed $p\in Y$ yields all vertex defining index sets $\mathcal A_\kappa\subset\{1,\dots,m\}$ which remain unchanged for all $p\neq\tilde p\in Y$ according to Corollary~\ref{thm:combinatorical:equivalence:alternative}.
 %
@@
 %
-The term~$(\dagger)$ is a multi parametric linear program (mpLP), we less interested in the objective value of~$(\dagger)$ but rather in the shape of its solution over~$p$ since it defines the shape of the set of points which can only just be taken to $P_i$ for an extremal value of $w\in\mathcal W(p)$.
+The term~$(\dagger)$ is a mpLP, we are less interested in the objective value of~$(\dagger)$ but rather in the shape of its solution over~$p$ since it defines the shape of the set of points 
+which can only just be taken to $P_i$ for an extremal value of $w\in\mathcal W(p)$ and therefore form the boundary of $S\ominus \mathcal W(S)$.
 %
@@
 %
-defines all vertices $\mathcal W(p) = \conv\{w_1(t(p)),\dots,w_N(t(p))\}$ for a element-wise convex piecewise affine function $t(p)$.
-%
-It is easy to see that the choice $t_i(p)=d_i(p)$ again leads us to the epigraph~$\epi(d_i)$ and therefore that the maximisation~$(\dagger)$ becomes
+defines all vertices of $\mathcal W(p) = \conv\{w_1(t(p)),\dots,w_N(t(p))\}$ for a element-wise convex piecewise affine function $t(p)$.
+%
+It is easy to see that the choice $t_i(p)=\phi_i(p)$ again leads us to the epigraph~$\epi(\phi_i)$ and therefore that the maximisation~$(\dagger)$ becomes
 %
@@
 %
-but this is the definition of the projection onto $\mathbb R^d$, $\pi_d(Q)$.
+but this is the definition of the projection onto $\mathbb R^d$.
 %
@@
 %
-Instead of using~$\tilde P_i$ which are points~$p$ that can be taken to $P_i$ for a feasible $w\in\mathcal W(p)$ and the values of the~$d_i(p)$ and so on, we obtain all feasible~$p$ such that a feasible $w\in\mathcal W(p)$ exists such that $p+w$lies on the boundary of $S$.
+Instead of using~$\tilde P_i$ which are points~$p$ that can be taken to $P_i$ for a feasible $w\in\mathcal W(p)$ and the values of the~$\phi_i(p)$ and so on, we obtain all feasible~$p$ such that a feasible $w\in\mathcal W(p)$ exists such that $p+w$ lies on the boundary of $S$.
 %
@@
 %
-The set~$L$ contains all such $p$ for which there exists a feasible $w\in\mathcal W(p)$ such that $p+w\in S$ and hence the projection $\pi_d(L)=S\ominus\mathcal W(S)$, which does not require a vertex enumeration.
+The set~$L$ contains all such $p$ for which there exists a feasible $w\in\mathcal W(p)$ such that $p+w\in S$ and hence $\pi_d(L)=S\ominus\mathcal W(S)$, which does not require a vertex enumeration.
 %
@@
 \section{Numerical Examples}\label{sec:numerical:examples}
-\subsection{Norm bound sets}
+\subsection{Norm bound sets}\label{ssec:example:one}
 %
@@
 %
-For the choice 
-%
-$$
-\norm{x}_P = \max_{k\leq n}\left\{\sin\left(\frac{2\pi}{n-1}k\right) x_1 + \cos\left(\frac{2\pi}{n-1}k\right) x_2\right\} = \max_{k\leq n}\{F_k x\}
-$$
-%
-we find $c_1 = \cos\left(\frac{\pi}{n-1}\right)$ and $c_2=1$.
-%
-This choice of~$\mathcal W(x)$ is a scaled approximation of an euclidean ball and therefore obviously parametrically convex with a fixed combinatorial structure.
+For example
+%
+$$
+\norm{x}_P = \max_{k\leq n}\left\{\sin\left(\frac{2\pi}{n-1}k\right) x_1 + \cos\left(\frac{2\pi}{n-1}k\right) x_2\right\} = \max_{k\leq n}\{F_k x\}.
+$$
+%
+For this choice we find $c_1 = \cos\left(\frac{\pi}{n-1}\right)$ and $c_2=1$.
+%
+Here~$\mathcal W(x)$ is a scaled approximation of an euclidean ball and therefore obviously parametrically convex with a fixed combinatorial structure.
 %
@@
 \includegraphics[width=.95\textwidth]{parametricPD.pdf}
-\caption{$X\ominus\mathcal W(X)$}
+\caption{$X\ominus\mathcal W(X)$ for Example~\ref{ssec:example:one}.}
 \label{fig:example:parametric:pontryagin:difference}
@@
 %
-For general nonlinear systems~$x^+=Ax + f(x)$ the maximal positive invariant set can not be calculated, but assume we find piecewise affine bounds on the nonlinearity, i.e.
+For general nonlinear systems~$x^+=Ax + f(x)$ the maximal positive invariant set cannot be calculated, but assume we find piecewise affine bounds on the nonlinearity, i.e.
 $\min_{k\leq M_i}\{h_{i,k}^x x + h_{i,k}^c\}\leq f_i(x)\leq\max_{k\leq N_i}\{H_{i,k}^x x + H_{i,k}^c\}$ for all $x\in\mathcal X$ and all elements of~$f(x)$.
@@
 %
-Instead of computing the maximal positive invariant set for the nonlinear system we compute the maximal robust positive invariant set for the perturbed linear system $x^+=Ax+w$, i.e.
+To bound the maximal positive invariant set for the nonlinear system we compute the maximal robust positive invariant set for the perturbed linear system $x^+=Ax+w$, i.e.
 the set of states~$\mathscr X^\infty\subseteq\mathcal X$ such that $x\in\mathscr X^\infty$ implies $x^+\in\mathscr X^\infty$ for all possible $w\in\mathcal W(x)$.
 %
-The algorithm to determine the maximal robust positive invariant sets recursively intersects the current set iterate~$X_l$ with the set of all possible successor states starting from the current iterate $X_{l+1}=X_l\cap\left\{\bigcup_{x\in X_l,w\in\mathcal W(x)}\{Ax+w\}\right\}$, we will only present a single step.
+The algorithm to determine the maximal robust positive invariant sets recursively intersects the current set iterate~$X_l$ with the set of all possible successor states starting from the current iterate $X_{l+1}=X_l\cap\left\{\bigcup_{x\in X_l,w\in\mathcal W(x)}\{Ax+w\}\right\}$.
+%
+We will only present a single step of this procedure.
 %
@@
 %
-In order not to bore the reader with numerical values, we illustrate the approximation of $f_1(x)$ in Figure~\ref{fig:approximation:f1:p:diff} and~$f_2(x)$ in Figure~\ref{fig:approximation:f2:p:diff}, for both we obtain upper and lower bounds using secants and tangents.
-%
-Figure~\ref{fig:approximation:f2:p:diff} shows an obvious weakness of the approach:~$\max_k\{c_k x+b_k\}$ is always convex, therefore approximating non-convex functions introduces conservativeness.
-
-The actual computation of the set~$X_{l+1}$ is then done analogous to the previous example, again we use that 
+We use piecewise affine approximations of $f_1(x)$~(Figure~\ref{fig:approximation:f1:p:diff}) and~$f_2(x)$ (Figure~\ref{fig:approximation:f2:p:diff})
+% In order not to bore the reader with numerical values, we illustrate the approximation of $f_1(x)$ in Figure~\ref{fig:approximation:f1:p:diff} and~$f_2(x)$ in Figure~\ref{fig:approximation:f2:p:diff},
+for both we obtain upper and lower bounds using secants and tangents.
+%
+Figure~\ref{fig:approximation:f2:p:diff} shows an obvious weakness of the approach:~$\max_k\{c_k x+b_k\}$ is necessarily convex, therefore approximating non-convex functions introduces conservativeness.
+
+The computation of the set~$X_{l+1}$ is then done analogously to the previous example, again we use 
 %
@@
 %
-Analogous to the previous example, instead of computing~$q$ projections from $3d+1$ onto $d$ we can perform a single projection with the same result:
+Analogously to the previous example, instead of computing~$q$ projections from $3d+1$ onto $d$ we can perform a single projection with the same result:
 %
@@
 %
-The resulting set for our 2 dimensional example is illustrated in Figure~\ref{fig:second:example:resulting:set}.
+The resulting set for this 2 dimensional example is illustrated in Figure~\ref{fig:second:example:resulting:set}.
 
@@
 %
-In this paper we presented a way to extend the scope of the Pontryagin difference to a wider class of sets.
-%
-We introduced the framework of parametric convexity and some of its analysis, which proved to be essential to prove the convexity of the parametric Pontryagin difference.
-%
-Furthermore we provided the link required to make the parametric Pontryagin difference computationally accessible for polytopic sets, it relied fully on the combinatorial nature of the subtrahend set-valued map.
+In this paper we present a way to extend the scope of the Pontryagin difference to a wide class of sets.
+%
+We introduce the framework of parametric convexity and some of its analysis, which proves essential for the convexity of the parametric Pontryagin difference.
+%
+Furthermore we provide the link required to make the parametric Pontryagin difference computationally accessible for polytopic sets, this relies on the combinatorial nature of the subtrahend set-valued map.
 %
@@
 
-The parametric Pontryagin difference has been applied successfully in a robust control environment~\cite{Schaich:2015,Schaich:2015a} and will continue to extend its scope of application.
+The parametric Pontryagin difference has been applied successfully in a robust control environment~\cite{Schaich:2015,Schaich:2015a} and this work will further to extend its scope of application.
 

### 2016-07-26 draft.tex
edits to Abstract and Highlights.txt

@@
 \begin{abstract}
-The Pontryagin set difference is a commonly used operation between two polytopes to calculate a set of safe operation.
-%
-We suggest to use a particular class of set-valued maps as the subtrahend, for this we introduce the property of parametric convexity and present some of its analytic framework.
-%
-In order to guarantee the convexity of the difference of a convex minuend and a set-valued map it proves necessary and sufficient to have the parametrically convexity property of the set-valued map.
-%
-For generic piecewise polyhedral set-valued maps we prove that parametric convexity is equivalent to a constant combinatorial structure of all its realisations.
-%
-We present a computational way of verifying parametric convexity of a piecewise polyhedral set-valued map as well as a way to calculate the parametric Pontryagin difference between a polyhedron and a piecewise polyhedral set-valued map.
+The Pontryagin set difference is an operation between two polytopes that is used to calculate sets of safe operation in applications of game theory and robust control design.
+%
+We consider a particular class of set-valued maps as the subtrahend; for this we introduce the property of parametric convexity and present some of its analytic framework.
+%
+In order to guarantee the convexity of the difference of a convex minuend and a set-valued map it proves necessary and sufficient that the set-valued map is parametrically convex.
+%
+For generic piecewise polyhedral set-valued maps we show that parametric convexity is equivalent to a constant combinatorial structure of all its realisations.
+%
+We present a computational method for verifying parametric convexity of a piecewise polyhedral set-valued map as well as a way to calculate the parametric Pontryagin difference between a polyhedron and a piecewise polyhedral set-valued map.
 %
@@
 %
-Furthermore, since $\lambda(p_1,z_1)+(1-\lambda)(p_2,z_2)\not\in \text{int}(\mathscr G(\mathcal W))$ and both $(p_1,z_1)$ and $(p_2,z_2)$ die on the boundary either $z_1-z_2$ or $z_2-z_1$ is outward facing for both $\mathcal W(p_1)$ and $\mathcal W(p_2)$, therefore either $z_1-z_2$ or $z_2-z_1$ is in $\mathcal N\mathcal W(p_1,z_1)$ and $\mathcal N\mathcal W(p_2,z_2)$ and hence in their intersection.
+Furthermore, since $\lambda(p_1,z_1)+(1-\lambda)(p_2,z_2)\not\in \text{int}(\mathscr G(\mathcal W))$ and both $(p_1,z_1)$ and $(p_2,z_2)$ lie on the boundary, either $z_1-z_2$ or $z_2-z_1$ is outward facing for both $\mathcal W(p_1)$ and $\mathcal W(p_2)$; therefore either $z_1-z_2$ or $z_2-z_1$ lies in both $\mathcal N\mathcal W(p_1,z_1)$ and $\mathcal N\mathcal W(p_2,z_2)$ and hence also in their intersection.
 
@@
 \begin{cor}\label{thm:combinatorical:equivalence:alternative}
-The generic set~$\mathcal W(p)$ defined by~\eqref{eq:definition:PWA:polytopic:set:general} is parametrically convex if and only if, it is combinatorially equivalent for any $p_1,p_2\in Y\subseteq\mathbb R^d$ almost everywhere, i.e.
-$\mathcal W(p_1)\cong\mathcal W(p_2)$.
+The generic set~$\mathcal W(p)$ defined by~\eqref{eq:definition:PWA:polytopic:set:general} is parametrically convex if and only if it is combinatorially equivalent for any $p_1,p_2\in Y\subseteq\mathbb R^d$ almost everywhere, i.e.\ $\mathcal W(p_1)\cong\mathcal W(p_2)$.
 \end{cor}

### 2016-07-26 draft.tex
edited Remark 8

@@
-\documentclass{elsarticle}
+\documentclass[final]{elsarticle}
 
@@
 %% or include affiliations in footnotes:
-\author{Rainer M. Schaich}
+\author{Rainer M. Schaich\fnref{akn}}
 \ead{rainer.schaich@eng.ox.ac.uk}
-
-\author{Mark Cannon\corref{correspondingauthor}}
+\fntext[akn]{The author is funded by the EPSRC DTA and the Worcester College Martin Senior Scholarship.}
+
+\author{Mark Cannon}
 \ead{mark.cannon@eng.ox.ac.uk}
 
-\cortext[correspondingauthor]{Corresponding author}
-
 \address{Department of Engineering Science, University of Oxford, Parks Road, OX1 3PJ, Oxford}
@@
 \begin{abstract}
-The Pontryagin set difference is an operation between two polytopes that is used to calculate sets of safe operation in applications of game theory and robust control design.
+The Pontryagin set difference is an operation between two polytopes that is used to calculate sets of safe operation in diverse applications including game theory and robust control.
 %
@@
 \begin{keyword}
-Parametric Convexity \sep Piecewise Affine Set-Valued Map \sep Pontryagin Difference
+Parametric Convexity \sep Piecewise Affine Set-Valued Map \sep Pontryagin Difference \sep Parametrised Polytopes
 \end{keyword}
@@
 %
-Notice that the boundary of a polytope is locally convex, i.e. concave but not strictly concave, it is locally strictly convex only around lower dimensional faces (vertices, edges, etc.) .
+Notice that the boundary of a polytope is almost everywhere locally convex (i.e. concave but not strictly concave) and locally strictly convex around lower dimensional faces (vertices, edges, etc.).
 %
@@
 %
-As long as the boundary $\partial\mathscr G(\mathcal W)$ is locally affine in $p\in Y$ Corollary~\ref{thm:inequalities:convex:concave} applies. 
+As long as the boundary $\partial\mathscr G(\mathcal W)$ is locally affine in $p\in Y$, Corollary~\ref{thm:inequalities:convex:concave} applies. 
 %
@@
 $$
-\tilde P_i= \left\{(z,t,\tau): \begin{array}{rcl}\Lambda_i Tt &\leq& \tau\\ Fz&\leq& t\\ \Lambda_i(z+\tau)&=&\lambda_i\\ \Lambda_j(z+T_lt)&\leq&\lambda_j\end{array},j\neq i,l\in\{1,\dots,n\}\right\}
+\tilde P_i= \left\{(z,t,\tau): \begin{array}{rcl}\kappa\Lambda_i Tt &\leq& \tau\\ Fz&\leq& t\\ \Lambda_i(z+\tau)&=&\lambda_i\\ \Lambda_j(z+\kappa T_lt)&\leq&\lambda_j\end{array},j\neq i,l\in\{1,\dots,n\}\right\}
 $$
@@
 L = \left\{(z,t,\tau_1,\dots,\tau_q):\begin{array}{rcl}
-\Lambda_i Tt & \leq &\tau_i\\
+\kappa\Lambda_i Tt & \leq &\tau_i\\
 Fz &\leq& t\\

### 2016-07-26 draft.tex
Modification of draft

--- 2016-07-26 draft.tex
@@
 %% or include affiliations in footnotes:
-\author{Rainer M. Schaich}
+\author{Rainer M. Schaich\fnref{akn}}
 \ead{rainer.schaich@eng.ox.ac.uk}
-
-\author{Mark Cannon\corref{correspondingauthor}}
+\fntext[akn]{The author is funded by the EPSRC DTA and the Worcester College Martin Senior Scholarship.}
+
+\author{Mark Cannon}
 \ead{mark.cannon@eng.ox.ac.uk}
-
-\cortext[correspondingauthor]{Corresponding author}
 

### 2017-01-07 draft.tex
Modified tikzpicture.
what happened

[ticket: X]

@@
 \centering
-\includegraphics[width=.95\textwidth]{complexPonDiff.pdf}
-\caption{In purple~$X_l$, outlined in blue~$X_{l+1}$, its vertices~$v_i$ marked by red crosses, yellow circles mark the vertices of $\{v_i\}\oplus\mathcal W(v_i)$, green crosses mark the actual value of $f(v_i)$ and dotted lines show the $x_1-\frac{x_2}{2}=0$ and $\frac{x_1}{2}+x_2=0$ planes.}
+\begin{tikzpicture}[scale=3]
+\draw[step=.5,gray,very thin] (-2,-2) grid (2,2);
+\foreach \x in {-2,-1.5,...,2} \draw (\x,-2) node[below] {$\x$};
+\foreach \y in {-2,-1.5,...,2} \draw (-2,\y) node[left] {$\y$};
+\draw[-latex'] (-2,-2) -- (2.2,-2) node[below] {$x_1$};
+\draw[-latex'] (-2,-2) -- (-2,2.2) node[left] {$x_2$};
+\draw[blue,thick] ( -0.2333,   1.7667) -- ( -1.3333,   0.6667) -- ( -1.4807,   0.5182) -- ( -1.6815,   0.2968) -- ( -1.6720,   0.2560) -- ( -1.6039,   0.1353) -- ( -1.5073,  -0.0145) -- ( -1.0649,  -0.5786) -- ( -0.5663,  -1.1326) -- ( -0.1361,  -1.4875) -- (  0.2333,  -1.7667) -- (  1.3333,  -0.6667) -- (  1.4807,  -0.5182) -- (  1.6499,  -0.3316) -- (  1.5962,  -0.2075) -- (  1.5190,  -0.0928) -- (  1.4796,  -0.0407) -- (  1.1714,   0.3429) -- (  0.9224,   0.6499) -- (  0.1793,   1.4518) -- (  0.1361,   1.4875) -- ( -0.2333,   1.7667) -- cycle;
+\draw[red] (  2.0000,   0.0000) -- (  0.0000,   2.0000) -- ( -2.0000,  -0.0000) -- ( -0.0000,  -2.0000) -- (  2.0000,   0.0000) -- cycle;
+\foreach \x/\y in { -0.2333/  1.7667,  0.1361/  1.4875,  0.1793/  1.4518, -1.3333/  0.6667, -1.0649/ -0.5786, -1.5073/ -0.0145, -1.6039/  0.1353,  0.9224/  0.6499,  1.6499/ -0.3316,  1.4807/ -0.5182,  1.5962/ -0.2075,  1.4796/ -0.0407,  1.5190/ -0.0928,  1.3333/ -0.6667,  1.1714/  0.3429,  0.2333/ -1.7667, -0.1361/ -1.4875, -0.5663/ -1.1326, -1.6720/  0.2560, -1.6815/  0.2968, -1.4807/  0.5182} \draw[green!80!black] (\x,\y) circle (.75pt);
+\foreach \x/\y in {  0.2160/  1.4706,  0.5125/  1.3332,  0.5456/  1.3134, -1.3333/  0.1741, -1.2021/ -0.7778, -1.5526/ -0.4386, -1.6336/ -0.3595,  1.0596/  0.9390,  1.6619/  0.2996,  1.4818/  0.0827,  1.6168/  0.3790,  1.5138/  0.4829,  1.5486/  0.4501,  1.3333/ -0.0915,  1.2515/  0.7356, -0.2160/ -1.3448, -0.5125/ -1.1956, -0.8500/ -1.1326, -1.6915/ -0.3039, -1.6976/ -0.2809, -1.4818/ -0.0094} \draw[yshift=-.5pt,xshift=-.5pt,magenta] (\x,\y) rectangle ++(1pt,1pt);
+% \foreach \x/\y in {0.2333/  1.7667,  0.2333/  1.4511, -0.2333/  1.7667, -0.2333/  1.4511,  0.5125/  1.4875,  0.5125/  1.3157,  0.1361/  1.4875,  0.1361/  1.3157,  0.5482/  1.4518,  0.5482/  1.2973,  0.1793/  1.4518,  0.1793/  1.2973, -1.3333/  0.6667, -1.3333/  0.1672, -1.3333/  0.6667, -1.3333/  0.1672, -1.0649/ -0.5786, -1.0649/ -0.7979, -1.2021/ -0.5786, -1.2021/ -0.7979, -1.5073/ -0.0145, -1.5073/ -0.4386, -1.5614/ -0.0145, -1.5614/ -0.4386, -1.6039/  0.1353, -1.6039/ -0.3664, -1.6336/  0.1353, -1.6336/ -0.3664,  1.0596/  0.9404,  1.0596/  0.6499,  0.9224/  0.9404,  0.9224/  0.6499,  1.6684/  0.3316,  1.6684/ -0.3316,  1.6499/  0.3316,  1.6499/ -0.3316,  1.4818/  0.0948,  1.4818/ -0.5182,  1.4807/  0.0948,  1.4807/ -0.5182,  1.6210/  0.3790,  1.6210/ -0.2075,  1.5962/  0.3790,  1.5962/ -0.2075,  1.5171/  0.4829,  1.5171/ -0.0407,  1.4796/  0.4829,  1.4796/ -0.0407,  1.5486/  0.4514,  1.5486/ -0.0928,  1.5190/  0.4514,  1.5190/ -0.0928,  1.3333/ -0.0906,  1.3333/ -0.6667,  1.3333/ -0.0906,  1.3333/ -0.6667,  1.2644/  0.7356,  1.2644/  0.3429,  1.1714/  0.7356,  1.1714/  0.3429,  0.2333/ -1.3435,  0.2333/ -1.7667, -0.2333/ -1.3435, -0.2333/ -1.7667, -0.1361/ -1.1944, -0.1361/ -1.4875, -0.5125/ -1.1944, -0.5125/ -1.4875, -0.5663/ -0.9938, -0.5663/ -1.1326, -0.8674/ -0.9938, -0.8674/ -1.1326, -1.6720/  0.2560, -1.6720/ -0.3039, -1.6961/  0.2560, -1.6961/ -0.3039, -1.6815/  0.2968, -1.6815/ -0.2968, -1.7032/  0.2968, -1.7032/ -0.2968, -1.4807/  0.5182, -1.4807/ -0.0145, -1.4818/  0.5182, -1.4818/ -0.0145} {
+%   \draw[cyan] (\x-.02,\y-.02) -- (\x+.02,\y+.02); 
+%   \draw[cyan] (\x-.02,\y+.02) -- (\x+.02,\y-.02);
+%   }
+
+\draw[cyan] (  0.2333,  1.7667) -- (  0.2333,  1.4511) -- ( -0.2333,  1.4511) -- ( -0.2333,  1.7667) -- cycle;
+\draw[cyan] (  0.5125,  1.4875) -- (  0.5125,  1.3157) -- (  0.1361,  1.3157) -- (  0.1361,  1.4875) -- cycle;
+\draw[cyan] (  0.5482,  1.4518) -- (  0.5482,  1.2973) -- (  0.1793,  1.2973) -- (  0.1793,  1.4518) -- cycle;
+\draw[cyan] ( -1.3333,  0.6667) -- ( -1.3333,  0.1672) -- ( -1.3333,  0.1672) -- ( -1.3333,  0.6667) -- cycle;
+\draw[cyan] ( -1.0649, -0.5786) -- ( -1.0649, -0.7979) -- ( -1.2021, -0.7979) -- ( -1.2021, -0.5786) -- cycle;
+\draw[cyan] ( -1.5073, -0.0145) -- ( -1.5073, -0.4386) -- ( -1.5614, -0.4386) -- ( -1.5614, -0.0145) -- cycle;
+\draw[cyan] ( -1.6039,  0.1353) -- ( -1.6039, -0.3664) -- ( -1.6336, -0.3664) -- ( -1.6336,  0.1353) -- cycle;
+\draw[cyan] (  1.0596,  0.9404) -- (  1.0596,  0.6499) -- (  0.9224,  0.6499) -- (  0.9224,  0.9404) -- cycle;
+\draw[cyan] (  1.6684,  0.3316) -- (  1.6684, -0.3316) -- (  1.6499, -0.3316) -- (  1.6499,  0.3316) -- cycle;
+\draw[cyan] (  1.4818,  0.0948) -- (  1.4818, -0.5182) -- (  1.4807, -0.5182) -- (  1.4807,  0.0948) -- cycle;
+\draw[cyan] (  1.6210,  0.3790) -- (  1.6210, -0.2075) -- (  1.5962, -0.2075) -- (  1.5962,  0.3790) -- cycle;
+\draw[cyan] (  1.5171,  0.4829) -- (  1.5171, -0.0407) -- (  1.4796, -0.0407) -- (  1.4796,  0.4829) -- cycle;
+\draw[cyan] (  1.5486,  0.4514) -- (  1.5486, -0.0928) -- (  1.5190, -0.0928) -- (  1.5190,  0.4514) -- cycle;
+\draw[cyan] (  1.3333, -0.0906) -- (  1.3333, -0.6667) -- (  1.3333, -0.6667) -- (  1.3333, -0.0906) -- cycle;
+\draw[cyan] (  1.2644,  0.7356) -- (  1.2644,  0.3429) -- (  1.1714,  0.3429) -- (  1.1714,  0.7356) -- cycle;
+\draw[cyan] (  0.2333, -1.3435) -- (  0.2333, -1.7667) -- ( -0.2333, -1.7667) -- ( -0.2333, -1.3435) -- cycle;
+\draw[cyan] ( -0.1361, -1.1944) -- ( -0.1361, -1.4875) -- ( -0.5125, -1.4875) -- ( -0.5125, -1.1944) -- cycle;
+\draw[cyan] ( -0.5663, -0.9938) -- ( -0.5663, -1.1326) -- ( -0.8674, -1.1326) -- ( -0.8674, -0.9938) -- cycle;
+\draw[cyan] ( -1.6720,  0.2560) -- ( -1.6720, -0.3039) -- ( -1.6961, -0.3039) -- ( -1.6961,  0.2560) -- cycle;
+\draw[cyan] ( -1.6815,  0.2968) -- ( -1.6815, -0.2968) -- ( -1.7032, -0.2968) -- ( -1.7032,  0.2968) -- cycle;
+\draw[cyan] ( -1.4807,  0.5182) -- ( -1.4807, -0.0145) -- ( -1.4818, -0.0145) -- ( -1.4818,  0.5182) -- cycle;
+
+\draw[thin,dash dot,gray] (0.7778,1.5556) -- (-0.7778,-1.5556);
+\draw[thin,dash dot,gray] (-1.5556,0.7778) -- (1.5556,-0.7778);
+\end{tikzpicture}
+% \caption[The parametric Pontryagin difference of a parametrically convex PWA set-valued map.]{The resulting set~$\mathcal X\ominus\mathcal W(\mathcal X)$ for Example~\ref{example:most:complex:pontryagin:difference:ever} in \textcolor{blue}{blue}, its vertices~$v_i$ marked by \textcolor{green!80!black}{green} circles, in \textcolor{red}{red} the set~$\mathcal X$, \textcolor{cyan}{cyan} boxes outline $\{v_i\}\oplus\mathcal W(v_i)$, \textcolor{magenta}{magenta} rectangles mark the actual value of $f(v_i)$, notice that each~$f(v_i)\in\{v_i\}\oplus\mathcal W(v_i)$ as required, and dash-dotted lines show the $x_1-\frac{x_2}{2}=0$ and $\frac{x_1}{2}+x_2=0$ planes.}
+
+% \includegraphics[width=.95\textwidth]{complexPonDiff.pdf}
+\caption{In red~$X_l$, outlined in blue~$X_{l+1}$, its vertices~$v_i$ marked by green circles, in cyan we outline $\{v_i\}\oplus\mathcal W(v_i)$, the red squares mark the actual value of $f(v_i)$ and dotted lines show the $x_1-\frac{x_2}{2}=0$ and $\frac{x_1}{2}+x_2=0$ planes.}
 \label{fig:second:example:resulting:set}

### 2017-01-07 secondExample.m

@@ -120,9 +120,11 @@ D(:,:,4) = kron(eye(4),L(4,:))*T;
     for i = 1:size(VV,1)
         x = VV(i,:)';
         t = [max(M1*x+B1),max(M2*x+B2),max(M3*x+B3),max(M4*x+B4)]';
-        ValidateF(x,t)
+        ValidateF(x,t);
         dx = reshape(T*t,2,4)+repmat(x,1,4);
         vv((4*i-3):4*i,:) = dx';
+        fprintf('\\draw[cyan] (%8.4f,%8.4f) -- (%8.4f,%8.4f) -- (%8.4f,%8.4f) -- (%8.4f,%8.4f) -- cycle;\n',...
+            dx(1),dx(2),dx(3),dx(4),dx(7),dx(8),dx(5),dx(6));
         r = [1,-1/2]*x;
         dx = [([1/2,1]*x)^3/10;
             real(1/2*asin(heav(r).*sqrt(abs(r)/2) + heav(-r).*r/2))];
@@ -144,8 +146,11 @@ D(:,:,4) = kron(eye(4),L(4,:))*T;
 xlabel('$x_1$');
 ylabel('$x_2$');
 
-
-
+% fprintf('\n');
+% for i = 1:size(vv,1)
+%     fprintf('%8.4f/%8.4f,',vv(i,1),vv(i,2));
+% end
+% fprintf('\n');
 Vn = [];
 for i = 1:4
     IDX = false(4,1);

### 2017-01-09 draft.tex
Adapted after merge.
what happened

[ticket: X]
submission to CGTA
Updated and submitted to Computational Geometry: Theory and Applications

@@
 
-\journal{Journal of Combinatorial Theory, Series A}
+\journal{Computational Geometry: Theory and Applications}
 
@@
 \ead{rainer.schaich@eng.ox.ac.uk}
-\fntext[akn]{The author is funded by the EPSRC DTA and the Worcester College Martin Senior Scholarship.}
-
-\author{Mark Cannon}
+\fntext[akn]{Supported by the EPSRC DTA and the Worcester College Martin Senior Scholarship}
+
+\author{Mark Cannon\fnref{coa}}
 \ead{mark.cannon@eng.ox.ac.uk}
-
-\address{Department of Engineering Science, University of Oxford, Parks Road, OX1 3PJ, Oxford}
+\fntext[coa]{Corresponding author}
+
+\address{Department of Engineering Science, University of Oxford, Oxford,  OX1 3PJ, UK}
 
@@
 %
-In this paper we only use one property of induced graphs, namely the \emph{Perles' Conjecture}~\cite{Kalai:1988}:
+In this paper we only use one property of induced graphs, namely the \emph{Perles Conjecture}~\cite{Kalai:1988}:
 \emph{For a simple polytope~$P$ the graph~$G(P)$ determines the combinatorial structure of~$P$.}
@@
 %
-Since $\mathcal W(p)$ is simple almost everywhere in~$Y$, i.e. each vertex is defined by exactly $n$ active inequalities $\abs{\mathcal A_\kappa(p)}=n$ for all $p\in Y$ and all $\kappa$.
+Since $\mathcal W(p)$ is simple almost everywhere in~$Y$, i.e. each vertex is defined by exactly $n$ active inequalities, we have $\abs{\mathcal A_\kappa(p)}=n$ for all $p\in Y$ and all $\kappa$.
 %
@@
 %
-The \emph{Perles' Conjecture}~\cite{Kalai:1988}, states that the combinatorial structure of a simple polytope is uniquely determined by its graph, that is, as long as the induced graph of~$\mathcal W(p)$ remains unchanged so does its combinatorial structure.
+The Perles Conjecture~\cite{Kalai:1988} states that the combinatorial structure of a simple polytope is uniquely determined by its graph, that is, as long as the induced graph of~$\mathcal W(p)$ remains unchanged so does its combinatorial structure.
 %
@@
 %
-with $(\ast) = \{F: d-\text{dimensional face of } \epi(d_i) \text{ for some } i\in\{1,\dots,m\}\}$.
-%
-It is now almost obvious that the graph $\mathscr G(\mathcal W\vert_{\mathcal P_j})$ on each $d$-dimensional element $\mathcal P_j\in\mathcal C$ is entirely defined by the values of $\mathcal W(p_j)$ at the vertices $p_j\in\text{vert}(\mathcal P_j)$.
+with $(\ast) = \{F: F \text{ is a } d\text{-dimensional face of } \epi(d_i) \text{ for some } i\in\{1,\dots,m\}\}$.
+%
+It is now obvious that the graph $\mathscr G(\mathcal W\vert_{\mathcal P_j})$ on each $d$-dimensional element $\mathcal P_j\in\mathcal C$ is entirely defined by the values of $\mathcal W(p_j)$ at the vertices $p_j\in\text{vert}(\mathcal P_j)$.
 %
@@
 \centering
-\begin{tikzpicture}[scale=3]
+\begin{tikzpicture}[scale=2.5]
 \draw[step=.5,gray,very thin] (-2,-2) grid (2,2);

### 2017-02-01 jems-draft.tex
added JEMS version
JEMS = Journal of the European Mathematical Society

--- 2017-01-09 draft.tex
@@
-\documentclass[final]{elsarticle}
-
-\usepackage{lineno}
-\usepackage[hidelinks]{hyperref}
-\modulolinenumbers[5]
-
-\usepackage{amsmath,amsthm,amssymb,mathrsfs}
-
-\journal{Computational Geometry: Theory and Applications}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%% Elsevier bibliography styles
-%%%%%%%%%%%%%%%%%%%%%%%
-%% To change the style, put a % in front of the second line of the current style and
-%% remove the % from the second line of the style you would like to use.
-%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Numbered
-%\bibliographystyle{model1-num-names}
-
-%% Numbered without titles
-%\bibliographystyle{model1a-num-names}
-
-%% Harvard
-%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
-
-%% Vancouver numbered
-%\usepackage{numcompress}\bibliographystyle{model3-num-names}
-
-%% Vancouver name/year
-%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
-
-%% APA style
-%\bibliographystyle{model5-names}\biboptions{authoryear}
-
-%% AMA style
-%\usepackage{numcompress}\bibliographystyle{model6-num-names}
-
-%% `Elsevier LaTeX' style
-\bibliographystyle{elsarticle-num}
-%%%%%%%%%%%%%%%%%%%%%%%
+% Modif. April 30, 2010
+% Send comments to publ@impan.pl
+
+\documentclass[a4paper, 12pt, twoside]{article}
+\usepackage{amsmath,amsthm,amssymb}
+\usepackage{times}
+\usepackage{enumerate}
+
+\usepackage{mathrsfs}
+
+\pagestyle{myheadings}
+\def\titlerunning#1{\gdef\titrun{#1}}
+\makeatletter
+\def\author#1{\gdef\autrun{\def\and{\unskip, }#1}\gdef\@author{#1}}
+\def\address#1{{\def\and{\\\hspace*{18pt}}\renewcommand{\thefootnote}{}%
+\footnote {#1}}%
+\markboth{\autrun}{\titrun}}
+\makeatother
+\def\email#1{e-mail: #1}
+\def\subjclass#1{{\renewcommand{\thefootnote}{}%
+\footnote{\emph{Mathematics Subject Classification (2010):} #1}}}
+\def\keywords#1{\par\medskip
+\noindent\textbf{Keywords.} #1}
+
+%% Numbered objects of "theorem" style (text italicized).
+%% The optional parameters indicate that all objects are numbered together, and "by section".
+%% However, you are welcome to use any other numbering system of your choice.
+
+\newtheorem{thm}{Theorem}[section]
+\newtheorem{cor}[thm]{Corollary}
+\newtheorem{lem}[thm]{Lemma}
+\newtheorem{prob}[thm]{Problem}
+
+%% A numbered theorem with a fancy name:
+
+\newtheorem{mainthm}[thm]{Main Theorem}
+
+%% Numbered objects of "non-theorem" style (text roman):
+
+\theoremstyle{definition}
+\newtheorem{defn}[thm]{Definition}
+\newtheorem{rem}[thm]{Remark}
+\newtheorem{exa}[thm]{Example}
+
+%% An unnumbered remark:
+
+\newtheorem*{xrem}{Remark}
+
+%% Equations numbered by section:
+
+\numberwithin{equation}{section}
+
+%%%%%%%%%%% For JEMS
+\frenchspacing
+
+\textwidth=15cm
+\textheight=23cm
+\parindent=16pt
+\oddsidemargin=-0.5cm
+\evensidemargin=-0.5cm
+\topmargin=-0.5cm
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%% Put your macros here:
 
@@
 
-\newcounter{thmcount}
-\renewcommand{\thethmcount}{\arabic{thmcount}}
-\renewcommand{\theequation}{\arabic{section}.\arabic{equation}}
-\renewcommand{\thefigure}{\arabic{section}.\arabic{figure}}
-
-\newtheorem{thm}[thmcount]{Theorem}
-\newtheorem{cor}[thmcount]{Corollary}
-\newtheorem{prop}[thmcount]{Proposition}
-
-\theoremstyle{remark}
-\newtheorem{rem}[thmcount]{Remark}
-
-\theoremstyle{definition}
-\newtheorem{defi}[thmcount]{Definition}
-\newtheorem{alg}[thmcount]{Algorithm}
-
 \DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
@@
 
-\begin{frontmatter}
+%%%%% To ease editing, add:
+
+%\baselineskip=17pt
+
+%%%%%%%%%%%%%%%%
+
+%% In the running head, give an abbreviation of the title. 
+\titlerunning{Explicit Operations on Parametrised Polytopes}
 
 \title{Explicit Operations on Parametrised Polytopes}
-% \tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
-
-%% or include affiliations in footnotes:
-\author{Rainer M. Schaich\fnref{akn}}
-\ead{rainer.schaich@eng.ox.ac.uk}
-\fntext[akn]{Supported by the EPSRC DTA and the Worcester College Martin Senior Scholarship}
-
-\author{Mark Cannon\fnref{coa}}
-\ead{mark.cannon@eng.ox.ac.uk}
-\fntext[coa]{Corresponding author}
-
-\address{Department of Engineering Science, University of Oxford, Oxford,  OX1 3PJ, UK}
+
+\author{Rainer M. Schaich
+\and 
+Mark Cannon}
+
+\date{\today}
+
+\maketitle
+
+\address{R. M. Schaich: Department of Engineering Science,
+  University of Oxford, Oxford, OX1 3PJ, UK; \email{rainer.schaich@eng.ox.ac.uk}
+\and
+M. Cannon:  Department of Engineering Science,
+  University of Oxford, Oxford, OX1 3PJ, UK; \email{mark.cannon@eng.ox.ac.uk}}
+
+\subjclass{Primary 52A20, 52B55; Secondary 52B11, 52A41, 90C25}
+% 52A20 Convex sets in $n$ dimensions (including convex hypersurfaces)
+% 52B55 Computational aspects related to convexity
+% 52B11 $n$-dimensional polytopes
+% 52A41 Convex functions and convex programs
+% 52A30 Variants of convex sets (star-shaped, ($m, n$)-convex, etc.)
+% 90C25 Convex programming
+% 68U05 Computer graphics; computational geometry
+% 52C45 Combinatorial complexity of geometric structures
 
 \begin{abstract}
-The Pontryagin set difference is an operation between two polytopes that is used to calculate sets of safe operation in diverse applications including game theory and robust control.
-%
-We consider a particular class of set-valued maps as the subtrahend; for this we introduce the property of parametric convexity and present some of its analytic framework.
-%
-In order to guarantee the convexity of the difference of a convex minuend and a set-valued map it proves necessary and sufficient that the set-valued map is parametrically convex.
+The Pontryagin set difference is an operation between two sets that is used to calculate sets of safe operation in diverse applications including game theory and robust control.
+%
+We consider a particular class of set-valued maps; for this we introduce the property of parametric convexity and present some of its analytic framework.
+%
+In order to guarantee the convexity of the difference of a convex set and a set-valued map it proves necessary and sufficient that the set-valued map is parametrically convex.
 %
@@
 Two examples are used to illustrate the presented methodology.
+
+\keywords{Pontryagin difference, piecewise affine set-valued map,
+  parametrised polytopes, parametric convexity}
 \end{abstract}
 
-\begin{keyword}
-Parametric Convexity \sep Piecewise Affine Set-Valued Map \sep Pontryagin Difference \sep Parametrised Polytopes
-\end{keyword}
-
-\end{frontmatter}
-
 % \linenumbers
@@
 %
-The Pontryagin difference was originally introduced as the Minkowski difference as a set theoretic tool in~\cite{Hadwiger:1950,Hadwiger:1957}, however in the years since the term Minkowski difference has often been used to refer to a different operation.
-%
-It was implicitly reintroduced in~\cite{Pontryagin:1966} for differential games to characterise safe sets for which strategies could be found which keep elements inside some second set for all possible adversary actions.
-%
-Since its introduction the usage of the Pontryagin difference has been extended beyond its application in differential games to various scenarios in which safe sets are required which withstand some perturbation.
-%
-See for example~\cite{blanchini:2007} for a its use as a robust control analysis tool in different contexts and under the name (set-)erosion it is used in morphological image analysis, e.g.~\cite{Haralick:1987}.
-%
-When the Pontryagin difference has to be performed explicitly by numeric algorithms it is usually assumed that the respective sets are polytopic, since it is not possible to operate on general sets explicitly.
-%
-Algorithms to determine the Pontryagin difference between two polytopes are known and do not require more complex computation than the solving of linear programs~\cite{Kolmanovsky:1998,Kerrigan:2003}, as well as their analytical properties, see~\cite{blanchini:2007,Haralick:1987,Kolmanovsky:1998}.
-%
-The sets on which these operations can be performed are fixed predetermined polytopes but, due to their physical interpretation safe sets, it can be desirable to extend the class of sets on which these operations can be performed.
-%
-For this purpose we propose the use of set-valued maps with polytopic realisation as the subtrahend.
+The Pontryagin difference was originally introduced (under the 
+name Minkowski difference) as a set theoretic tool
+in~\cite{Hadwiger:1950,Hadwiger:1957}. 
+%However in the years since the term Minkowski difference has often been used to refer to a different operation.
+%
+It was implicitly reintroduced in the context of
+differential games in~\cite{Pontryagin:1966}, where it was used to characterise safe sets for which strategies could be found which keep elements inside some second set for all possible adversary actions.
+%
+Since its introduction, the usage of the Pontryagin difference has been extended beyond applications in differential games to various scenarios in which safe sets are needed that withstand some perturbation.
+%
+See for example~\cite{blanchini:2007} for a its use as a robust
+control analysis tool in several different contexts and under the name
+(set-)erosion. It has also found use in morphological image analysis, e.g.~\cite{Haralick:1987}.
+%
+
+When the Pontryagin difference has to be performed explicitly by numerical algorithms, it is usually assumed that the respective sets are polytopic, since it is not possible to operate on general sets explicitly.
+%
+Algorithms to determine the Pontryagin difference between two
+polytopes do not require more complex computation than the solving of
+linear programs~\cite{Kolmanovsky:1998,Kerrigan:2003}, and their
+analytical properties are well-known, see e.g.~\cite{blanchini:2007,Haralick:1987,Kolmanovsky:1998}.
+%
+The sets on which these operations can be performed are fixed
+predetermined polytopes but, due to their physical interpretation in
+terms of safe sets, it can be desirable to extend the class of sets on which these operations can be performed.
+%
+For this purpose we consider the case in which the subtrahend is a
+set-valued map with a polytopic realisation.
 
@@
 %
-However, computational aspects of operations on general set-valued maps are largely unknown, we refer to~\cite{Finzel:2000} for some results for polyhedral set-valued maps.
-%
-In this paper we present a particular class of set-valued maps for which the Pontryagin difference can be computed explicitly.
+However, computational aspects of operations on general set-valued
+maps are largely unknown. We refer to~\cite{Finzel:2000} for some results for polyhedral set-valued maps.
+%
+In this paper we present a particular class of set-valued map for which the Pontryagin difference can be computed explicitly.
 %
@@
 %
-In Section~\ref{sec:preliminaries} we summarise preliminaries we require throughout the paper, in Section~\ref{sec:parametric:convexity} we introduce parametric convexity, the essential ingredient for all subsequent analysis and provide analytic results for the set operations we refine and extend for set-valued maps with polyhedral realisations in Section~\ref{sec:polyhedral:maps}.
+In Section~\ref{sec:preliminaries} we summarise preliminaries that are
+required throughout the paper. In
+Section~\ref{sec:parametric:convexity} we introduce parametric
+convexity, which is the essential ingredient for all subsequent
+analysis, and provide analytic results for set operations. 
+We refine and extend these results for the case of set-valued maps with polyhedral realisations in Section~\ref{sec:polyhedral:maps}.
 %
@@
 %
-We denote index sets by $\mathcal A,\,\mathcal J$ or $\mathcal I$, the complement of a subset of an index set $\mathcal I\subset\mathcal A$ is denoted by $\bar{\mathcal I}=\mathcal A\setminus\mathcal I$, the objects $a_{\mathcal I}$ and $b_{\mathcal I}$ denote the matrix and the column vector with rows given by the row vectors $a_i$ and the scalar values $b_i$ with $i\in\mathcal I$.
+We denote the integer range~$\{1,\dots,m\}$ by~$\mathbb N_m$ and index sets by $\mathcal A,\,\mathcal J$ or $\mathcal I$, the complement of a subset of an index set $\mathcal I\subset\mathcal A$ is denoted by $\bar{\mathcal I}=\mathcal A\setminus\mathcal I$, the objects $a_{\mathcal I}$ and $b_{\mathcal I}$ denote the matrix and the column vector with rows given by the row vectors $a_i$ and the scalar values $b_i$ with $i\in\mathcal I$.
 %
@@
 %
-\begin{defi}[Parametric Convexity]\label{def:parametric:convexity}
+\begin{defn}[Parametric Convexity]\label{def:parametric:convexity}
 Let $\mathcal W:Y\rightarrow \mathscr P(Z)$, where $Y\ni p\mapsto \mathcal W(p) \subset Z$, be a continuous set-valued map. The map $\mathcal W$ is called \emph{parametrically convex} if it satisfies
@@
   for all $p_1,p_2\in Y$ and $\lambda\in (0,1)$.
-\end{defi}
+\end{defn}
 %
@@
 %
-\begin{defi}\label{def:graph:of:map}
+\begin{defn}\label{def:graph:of:map}
 Let $\mathcal W:Y\rightarrow \mathscr P(Z)$ be a continuous set-valued map
@@
 %
-\begin{equation*}  
-\text{int}(\mathscr G(\mathcal W)) = \{(p,z) \in Y\times Z : \forall \zeta\in\mathbb R^n\;\exists \epsilon>0, \, z+\epsilon \zeta\in \mathcal W(p) \}
-\end{equation*}
+\begin{equation*}\begin{aligned}
+\text{int}(\mathscr G(\mathcal W)) = \{(p,z) \in Y\times Z : \forall \zeta\in\mathbb R^n\;\exists \epsilon>0,\\ \, z+\epsilon \zeta\in \mathcal W(p) \}
+\end{aligned}\end{equation*}
 %
@@
 %
-\end{defi}
+\end{defn}
 %
@@
 %
-\begin{defi}[Parametric Pontryagin Difference]\label{def:parametric:pontryagin:difference}
+\begin{defn}[Parametric Pontryagin Difference]\label{def:parametric:pontryagin:difference}
   Let $S\subseteq Z$ and let $\mathcal W:Z\to\mathscr P(Z)$ be a continuous set-valued map such that
@@
 \begin{align*}
-  \{ \lambda z_1 + (1-&\lambda)z_2
+  \{ \lambda z_1 + &(1-\lambda)z_2
   \}\oplus \mathcal W\left( \lambda z_1 + (1-\lambda)z_2\right)\\
@@
 \begin{cor}\label{thm:polytopic:set:not:p:convex}
-The polytopic parametric set-valued map $\mathcal W(p):=\{z: a_i z + b_i p\leq c_i \; \forall i\in\{1,\dots,m\}\}$
+The polytopic parametric set-valued map $\mathcal W(p):=\{z: a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\}$
 is not parametrically convex for any non-zero matrix $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$.
@@
 \begin{equation*}
-	\mathscr G(\mathcal W) = \{(p,z):a_i z + b_i p\leq c_i \; \forall i\in\{1,\dots,m\}\} ,
+	\mathscr G(\mathcal W) = \{(p,z):a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\} ,
 \end{equation*}
@@
 \begin{equation}\label{eq:definition:PWA:polytopic:set:general}
-  \mathcal W(p) := \Bigl\{z\in\mathbb R^n: a_i z \leq \max_{k}\{b_{i,k} + c_{i,k}p\} \; \forall i\in\{1,\dots,m\} \Bigr\}
+  \mathcal W(p) := \Bigl\{z\in\mathbb R^n: a_i z \leq \max_{k}\{b_{i,k} + c_{i,k}p\} \; \forall i\in\mathbb N_m \Bigr\}
 \end{equation}
@@
 \begin{equation*}
-  \mathscr G(\mathcal W) = \bigcup_{j\in\mathcal I} \left\{z\in\mathbb R^n: a_i z \leq b_{i,k_i^\ast} + c_{i,k_i^\ast}p \; \forall i \in\{1,\dots,m\} \right\}\bigr\vert_{\mathcal P_{j}}
+  \mathscr G(\mathcal W) = \bigcup_{j\in\mathcal I} \left\{z: a_i z \leq b_{i,k_i^\ast} + c_{i,k_i^\ast}p \; \forall i \in\mathbb N_m \right\}\bigr\vert_{\mathcal P_{j}}
 \end{equation*}
@@
 Furthermore, since~$\mathcal W(p)$ is generic, only one element of ${\bf{k}}^\ast\vert_{\mathcal P_{j_1}}$
-and ${\bf{k}}^\ast\vert_{\mathcal P_{j_2}}$ for neighbouring $\mathcal P_{j_1}$ and $\mathcal P_{j_2}$ differs, that is, there exists a single index $i\in\{1,\dots,m\}$ such that $k_i^\ast\vert_{\mathcal P_{j_1}}\neq k_i^\ast\vert_{\mathcal P_{j_2}}$.
+and ${\bf{k}}^\ast\vert_{\mathcal P_{j_2}}$ for neighbouring $\mathcal P_{j_1}$ and $\mathcal P_{j_2}$ differs, that is, there exists a single index $i\in\mathbb N_m$ such that $k_i^\ast\vert_{\mathcal P_{j_1}}\neq k_i^\ast\vert_{\mathcal P_{j_2}}$.
 %
@@
 For notational convenience let $\phi_i(p) = \max_k\{b_{i,k}+c_{i,k}p\}$ denote the right hand side of~\eqref{eq:definition:PWA:polytopic:set:general}, i.e.
-$\mathcal W(p) = \{z\in\mathbb R^n: a_i z\leq \phi_i(p)\;\forall i\in\{1,\dots,m\}\}$.
+$\mathcal W(p) = \{z\in\mathbb R^n: a_i z\leq \phi_i(p)\;\forall i\in\mathbb N_m\}$.
 %
@@
 %
-The set of vertices of elements in the complex coincides with the union of all vertices of $d$-dimensional faces of $\epi(\phi_i)$ for all $i\in\{1,\dots,m\}$, i.e.
-%
-$$
-	\bigcup_{P\in\mathcal C}\text{vert}(P) = \bigcup_{(\ast)} \text{vert}(\pi_d(F)) = \bigcup_{i\in\{1,\dots,m\}}\pi_d(\text{vert}(\epi(\phi_i))),
-$$
-%
-with $(\ast) = \{F: F \text{ is a } d\text{-dimensional face of } \epi(d_i) \text{ for some } i\in\{1,\dots,m\}\}$.
+The set of vertices of elements in the complex coincides with the union of all vertices of $d$-dimensional faces of $\epi(\phi_i)$ for all $i\in\mathbb N_m$, i.e.
+%
+$$\begin{aligned}
+	\bigcup_{P\in\mathcal C}\text{vert}(P) = \bigcup_{(\ast)} \text{vert}(\pi_d(F))\\ = \bigcup_{i\in\mathbb N_m}\pi_d(\text{vert}(\epi(\phi_i))),
+\end{aligned}$$
+%
+with $(\ast) = \{F: F $ is a $d$-dimensional face of $\epi(d_i)$ for some $i\in\mathbb N_m\}$.
 %
@@
 %
-In each~$\mathcal P_j$ we have $\mathcal W(p) = \{z: a_i z\leq \sum_f \lambda_f t_{i,j,f}, \sum_f\lambda_f p_{j,f}=p, \sum_f\lambda=1,{\bf{0}}\leq\lambda\leq{\bf{1}}\; \forall i\in\{1,\dots,m\}\}$
-%
-Therefore, if~$\mathcal A_\kappa\subset\{1,\dots,m\}$ such that~$\abs{\mathcal A_\kappa}=d$ and $a_\kappa v_\kappa = t_{\kappa,j}$ defines a vertex for $\mathcal W(p_j)$, then $a_\kappa v_\kappa = \sum_f \lambda_f t_{\kappa,f}$ defines a vertex for $\mathcal W(p)$.
+In each~$\mathcal P_j$ we have $\mathcal W(p) = \{z: a_i z\leq \sum_f \lambda_f t_{i,j,f}, \sum_f\lambda_f p_{j,f}=p, \sum_f\lambda=1,{\bf{0}}\leq\lambda\leq{\bf{1}}\; \forall i\in\mathbb N_m\}$
+%
+Therefore, if~$\mathcal A_\kappa\subset\mathbb N_m$ such that~$\abs{\mathcal A_\kappa}=d$ and $a_\kappa v_\kappa = t_{\kappa,j}$ defines a vertex for $\mathcal W(p_j)$, then $a_\kappa v_\kappa = \sum_f \lambda_f t_{\kappa,f}$ defines a vertex for $\mathcal W(p)$.
 
@@
 %
-then Corollary~\ref{thm:p:convexity:PWA:set:constant:num:verts} holds and $\mathcal W(p)$ is parametrically convex, furthermore enumerating the vertices of $\mathcal W(p)$ for any fixed $p\in Y$ yields all vertex defining index sets $\mathcal A_\kappa\subset\{1,\dots,m\}$ which remain unchanged for all $p\neq\tilde p\in Y$ according to Corollary~\ref{thm:combinatorical:equivalence:alternative}.
+then Corollary~\ref{thm:p:convexity:PWA:set:constant:num:verts} holds and $\mathcal W(p)$ is parametrically convex, furthermore enumerating the vertices of $\mathcal W(p)$ for any fixed $p\in Y$ yields all vertex defining index sets $\mathcal A_\kappa\subset\mathbb N_m$ which remain unchanged for all $p\neq\tilde p\in Y$ according to Corollary~\ref{thm:combinatorical:equivalence:alternative}.
 %
@@
 %
-For the set $S=\{p\in\mathbb R^d:\Lambda_i p\leq\lambda_i,i\in\{1,\dots,q\}\}$ each facet $P_i=\{p:\Lambda_i p=\lambda_i\wedge\Lambda_j p\leq\lambda_j,j\neq i\}$ defines facets of the set difference.
+For the set $S=\{p\in\mathbb R^d:\Lambda_i p\leq\lambda_i,i\in\mathbb N_q\}$ each facet $P_i=\{p:\Lambda_i p=\lambda_i\wedge\Lambda_j p\leq\lambda_j,j\neq i\}$ defines facets of the set difference.
 %
@@
 %
-Computing the set $S\ominus\mathcal W(S)$ therefore reduces to computing points~$p$ for which an admissible $w^\ast$ exists to produce~$p+w^\ast\in P_i$ for some $i\in\{1,\dots,q\}$.
+Computing the set $S\ominus\mathcal W(S)$ therefore reduces to computing points~$p$ for which an admissible $w^\ast$ exists to produce~$p+w^\ast\in P_i$ for some $i\in\mathbb N_q$.
 %
@@
   & B_i+C_ip\leq t_i\\
-  & j\in\{1,\dots,N\}
+  & j\in\mathbb N_N
   \end{array}\right.
@@
 %
-further, the solution to~\eqref{eq:rewriting:pontryagin:diff:without:facet:constraint} is only relevant for such~$p$ that can be taken to~$P_i$ for some $i\in\{1,\dots,q\}$.
+further, the solution to~\eqref{eq:rewriting:pontryagin:diff:without:facet:constraint} is only relevant for such~$p$ that can be taken to~$P_i$ for some $i\in\mathbb N_q$.
 %
@@
   &\Lambda_l(p + T_jt)\leq\lambda_l\\
-  &l\neq i, j\in\{1,\dots,N\}
+  &l\neq i, j\in\mathbb N_N
   \end{array}
@@
   \Lambda_l(p + T_jt)&\leq&\lambda_l\\
-  \end{array},\begin{array}{rcl}
-   l&\neq& i\\
-   j&\in&\{1,\dots,N\}\\k&\in&\{1,\dots,q\}\end{array}
+  \end{array},\begin{array}{l}
+   l\neq i\\
+   j\in\mathbb N_N\\
+   k\in\mathbb N_q
+   \end{array}
    \right\}
@@
   \end{array},\begin{array}{rcl}
-  j&\in&\{1,\dots,N\}\\
-  i&\in&\{1,\dots,q\}\end{array}
+  j&\in&\mathbb N_N\\
+  i&\in&\mathbb N_q\end{array}
   \right\}
@@
 %
-$$
-\norm{x}_P = \max_{k\leq n}\left\{\sin\left(\frac{2\pi}{n-1}k\right) x_1 + \cos\left(\frac{2\pi}{n-1}k\right) x_2\right\} = \max_{k\leq n}\{F_k x\}.
-$$
+$$\begin{aligned}
+\norm{x}_P &= \max_{k\leq n}\left\{\sin\left(\frac{2\pi}{n-1}k\right) x_1 + \cos\left(\frac{2\pi}{n-1}k\right) x_2\right\}\\
+ &= \max_{k\leq n}\{F_k x\}.
+\end{aligned}$$
 %
@@
 $$
-\tilde P_i= \left\{(z,t,\tau): \begin{array}{rcl}\kappa\Lambda_i Tt &\leq& \tau\\ Fz&\leq& t\\ \Lambda_i(z+\tau)&=&\lambda_i\\ \Lambda_j(z+\kappa T_lt)&\leq&\lambda_j\end{array},j\neq i,l\in\{1,\dots,n\}\right\}
+\tilde P_i= \left\{(z,t,\tau): \begin{array}{rcl}\kappa\Lambda_i Tt &\leq& \tau\\ Fz&\leq& t\\ \Lambda_i(z+\tau)&=&\lambda_i\\ \Lambda_j(z+\kappa T_lt)&\leq&\lambda_j\end{array},j\neq i,l\in\mathbb N_n\right\}
 $$
@@
 \Lambda_i(z+\tau_i)&\leq&\lambda_i
-\end{array},i\in\{1,\dots,q\}\right\}
+\end{array},i\in\mathbb N_q\right\}
 $$
@@
 \centering
-\includegraphics[width=.95\textwidth]{parametricPD.pdf}
+% \includegraphics[width=.95\columnwidth]{parametricPD.pdf}
+\begin{tikzpicture}[scale=3]
+\draw[step=.25,gray,very thin] ( -1,  -1) grid (  1,   1);
+\foreach \x in {-1,-0.5,...,1} \draw (\x,-1) node[below] {$\x$};
+\foreach \y in {-1,-0.5,...,1} \draw (-1,\y) node[left] {$\y$};
+\draw[thick,blue] (  0.0772,   0.8327) -- ( -0.0772,   0.8327) -- ( -0.2355,   0.8279) -- ( -0.4070,   0.8174) -- ( -0.6038,   0.7996) -- ( -0.7790,   0.7790) -- ( -0.7870,   0.7175) -- ( -0.8096,   0.5013) -- ( -0.8234,   0.3190) -- ( -0.8309,   0.1553) -- ( -0.8333,   0.0000) -- ( -0.8309,  -0.1553) -- ( -0.8234,  -0.3190) -- ( -0.8096,  -0.5013) -- ( -0.7870,  -0.7175) -- ( -0.7790,  -0.7790) -- ( -0.6038,  -0.7996) -- ( -0.4070,  -0.8174) -- ( -0.2355,  -0.8279) -- ( -0.0772,  -0.8327) -- (  0.0772,  -0.8327) -- (  0.2355,  -0.8279) -- (  0.4070,  -0.8174) -- (  0.6038,  -0.7996) -- (  0.7790,  -0.7790) -- (  0.7870,  -0.7175) -- (  0.8096,  -0.5013) -- (  0.8234,  -0.3190) -- (  0.8309,  -0.1553) -- (  0.8333,   0.0000) -- (  0.8309,   0.1553) -- (  0.8234,   0.3190) -- (  0.8096,   0.5013) -- (  0.7870,   0.7175) -- (  0.7790,   0.7790) -- (  0.6038,   0.7996) -- (  0.4070,   0.8174) -- (  0.2355,   0.8279) -- (  0.0772,   0.8327) -- cycle;
+\draw[-latex'] (-1,-1) -- (1.1,-1) node[above] {\small{$z_1$}};
+\draw[-latex'] (-1,-1) -- (-1,1.1) node[right] {\small{$z_2$}};
+\end{tikzpicture}
 \caption{$X\ominus\mathcal W(X)$ for Example~\ref{ssec:example:one}.}
@@
 %
-We can now study the system $x^+=Ax+w$ with $w\in\mathcal W(x) = \{w:\min_{k\leq M_i}\{h_{i,k}^x x + h_{i,k}^c\}\leq w_i\leq\max_{k\leq N_i}\{H_{i,k}^x x + H_{i,k}^c\}\,\forall i\in\{1,\dots,d\}\}$.
+We can now study the system $x^+=Ax+w$ with $w\in\mathcal W(x) = \{w:\min_{k\leq M_i}\{h_{i,k}^x x + h_{i,k}^c\}\leq w_i\leq\max_{k\leq N_i}\{H_{i,k}^x x + H_{i,k}^c\}\,\forall i\in\mathbb N_d\}$.
 %
@@
 \begin{equation}
-  f_2(x) = \frac{1}{2}\arcsin\left(\sigma\left(x_1-\frac{x_2}{2}\right)\sqrt{\frac{x_1-\frac{x_2}{2}}{2}} + \sigma\left(-\left(x_1-\frac{x_2}{2}\right)\right)\frac{x_1-\frac{x_2}{2}}{2} \right)
+  f_2(x) = \frac{1}{2}\arcsin\left(g_1\left(x_1-\frac{x_2}{2}\right)+g_2\left(x_1-\frac{x_2}{2}\right) \right)
 \end{equation}
@@
 %
-with the Heaviside function
-%
+with $g_1(t)=\sigma(t)\sqrt{\frac{t}{2}}$, $g_2(t)=\sigma(-t)\frac{t}{2}$ where $\sigma(t)$ denotes the Heaviside function
+%\sigma\left(x_1-\frac{x_2}{2}\right)\sqrt{\frac{x_1-\frac{x_2}{2}}{2}} + \sigma\left(-\left(x_1-\frac{x_2}{2}\right)\right)\frac{x_1-\frac{x_2}{2}}{2}
 $$
@@
 \begin{equation}
-  \pi_d\left(\left\{(x,t,\tau)\in\mathbb R^{3d+1}:\begin{array}{rcl}
+  \pi_d\left(\left\{(x,t,\tau):\begin{array}{rcl}
   \Lambda_iAx+\tau&=&\lambda_i\\
@@
   j\neq i\\
-  l\in\{1,\dots,d\}\end{array}
+  l\in\mathbb N_d\end{array}
   \right\}\right)
@@
 \begin{equation}
-  \pi_d\left(\left\{(x,t,\tau)\in\mathbb R^{3d+q}:\begin{array}{rcl}
+  \pi_d\left(\left\{(x,t,\tau):\begin{array}{rcl}
   \Lambda_i T_lt&\leq&\tau_i\\
@@
   \end{array}, \begin{array}{l}
-  i\in\{1,\dots,q\},\\
-  l\in\{1,\dots,d\}\end{array}
+  i\in\mathbb N_q,\\
+  l\in\mathbb N_d\end{array}
   \right\}\right)
@@
 \centering
-\begin{tikzpicture}[scale=2]
+\begin{tikzpicture}[scale=1.8]
 \draw[-latex'] (-2.1,0) -- (2.1,0) node[above] {$t$};
@@
 \centering
-\begin{tikzpicture}[scale=2.5]
+\begin{tikzpicture}[scale=1.8]
 \draw[step=.5,gray,very thin] (-2,-2) grid (2,2);
@@
 \foreach \y in {-2,-1.5,...,2} \draw (-2,\y) node[left] {$\y$};
-\draw[-latex'] (-2,-2) -- (2.2,-2) node[below] {$x_1$};
-\draw[-latex'] (-2,-2) -- (-2,2.2) node[left] {$x_2$};
+\draw[-latex'] (-2,-2) -- (2.2,-2) node[above] {$x_1$};
+\draw[-latex'] (-2,-2) -- (-2,2.2) node[right] {$x_2$};
 \draw[blue,thick] ( -0.2333,   1.7667) -- ( -1.3333,   0.6667) -- ( -1.4807,   0.5182) -- ( -1.6815,   0.2968) -- ( -1.6720,   0.2560) -- ( -1.6039,   0.1353) -- ( -1.5073,  -0.0145) -- ( -1.0649,  -0.5786) -- ( -0.5663,  -1.1326) -- ( -0.1361,  -1.4875) -- (  0.2333,  -1.7667) -- (  1.3333,  -0.6667) -- (  1.4807,  -0.5182) -- (  1.6499,  -0.3316) -- (  1.5962,  -0.2075) -- (  1.5190,  -0.0928) -- (  1.4796,  -0.0407) -- (  1.1714,   0.3429) -- (  0.9224,   0.6499) -- (  0.1793,   1.4518) -- (  0.1361,   1.4875) -- ( -0.2333,   1.7667) -- cycle;
@@
 
-\section*{References}
-
 \bibliography{Bibliography}
+\bibliographystyle{plain}
 

### 2017-02-01 jems-draft.tex
minor edits
Edited the abstract, introduction, conclusions and references.
Also changed (5.5)-(5.10) so that they are equivalent to eqns in Sect.
5.2 of thesis, and changed the end of Section 5.
Changed captions of Fig 1 and 2.

@@
 %
-Two examples are used to illustrate the presented methodology.
+Two examples are given to illustrate the presented methodology.
 
@@
 \subsection{Determination of Parametric Convexity}
-In the previous sections we have derived that for the Pontryagin difference between any convex set $S$ and a set-valued map~$\mathcal W$ to be convex itself we require the parametric convexity property for~$\mathcal W$.
-%
-We have also seen that for set-valued maps with polyhedral realisations $\mathcal W(p)$, the number of vertices and rays must not change throughout the parameter space~$Y$ in order that $\mathcal W(p)$ is parametrically convex.
-%
-This might seem like a computationally challenging endeavour, however we will see that it suffices to solve a finite number of calculations.
+%In the previous sections it was demonstrated that a set-valued
+%map~$\mathcal W$ must be parametrically convex in order that the
+%Pontryagin difference between any convex set $S$ and $\mathcal W$ is convex.
+%
+In Section~3 it was demonstrated that, in order for the
+Pontryagin difference between any convex set $S$ and a set-valued
+map~$\mathcal W$ to be convex, $\mathcal W$ must be parametrically
+convex.
+%
+We have also seen that for a set-valued map with polyhedral realisations $\mathcal W(p)$, the number of vertices and rays must not change throughout the parameter space~$Y$ in order that $\mathcal W(p)$ is parametrically convex.
+%
+Checking this condition may seem computationally challenging, however
+we show in this section that it suffices to perform a finite number of calculations.
 %
@@
 %
-$$\abs{\text{vert}(\mathcal W(p))} = \text{const.}\quad \forall p\in\mathcal D$$.
-%
-then Corollary~\ref{thm:p:convexity:PWA:set:constant:num:verts} holds and $\mathcal W(p)$ is parametrically convex, furthermore enumerating the vertices of $\mathcal W(p)$ for any fixed $p\in Y$ yields all vertex defining index sets $\mathcal A_\kappa\subset\mathbb N_m$ which remain unchanged for all $p\neq\tilde p\in Y$ according to Corollary~\ref{thm:combinatorical:equivalence:alternative}.
+$$\abs{\text{vert}(\mathcal W(p))} = c_{\mathcal D} \quad \forall p\in\mathcal D$$
+%
+for some constant $c_{\mathcal D}$. If this is the case, then
+Corollary~\ref{thm:p:convexity:PWA:set:constant:num:verts} holds and
+$\mathcal W(p)$ is parametrically convex.
+Furthermore enumerating the vertices of $\mathcal W(p)$ for any fixed $p\in Y$ yields all vertices defining index sets $\mathcal A_\kappa\subset\mathbb N_m$ which remain unchanged for all $p\neq\tilde p\in Y$ according to Corollary~\ref{thm:combinatorical:equivalence:alternative}.
 %
@@
 %
-The constancy of the active inequalities defining vertices of~$\mathcal W(p)$ is particularly useful when we compute the parametric Pontryagin difference $S\ominus\mathcal W(S)$:
-%
-For the set $S=\{p\in\mathbb R^d:\Lambda_i p\leq\lambda_i,i\in\mathbb N_q\}$ each facet $P_i=\{p:\Lambda_i p=\lambda_i\wedge\Lambda_j p\leq\lambda_j,j\neq i\}$ defines facets of the set difference.
+The constancy of the active inequalities defining vertices of~$\mathcal W(p)$ is particularly useful when we compute the parametric Pontryagin difference $S\ominus\mathcal W(S)$.
+%
+In particular for the set $S=\{p\in\mathbb R^d:\Lambda_i p\leq\lambda_i,i\in\mathbb N_q\}$ each facet $P_i=\{p:\Lambda_i p=\lambda_i\wedge\Lambda_j p\leq\lambda_j,j\neq i\}$ defines facets of the set difference.
 %
@@
 %
-The term~$(\dagger)$ is a mpLP, we are less interested in the objective value of~$(\dagger)$ but rather in the shape of its solution over~$p$ since it defines the shape of the set of points 
-which can only just be taken to $P_i$ for an extremal value of $w\in\mathcal W(p)$ and therefore form the boundary of $S\ominus \mathcal W(S)$.
+The term~$(\dagger)$ is a mpLP, however we are less interested in the
+objective value of~$(\dagger)$ than the shape of its solution
+over~$p$, since this defines the shape of the set of points 
+that can only just be taken to $P_i$ for an extremal value of $w\in\mathcal W(p)$ and hence form the boundary of $S\ominus \mathcal W(S)$.
 %
@@
   \text{s.t.}& \Lambda_iT_jt\leq\tau\\
-  & B_i+C_ip\leq t_i\\
-  & j\in\mathbb N_N
+  & B_k+C_k p \leq t_k\\
+  & j\in\mathbb N_N, \ k\in\mathbb N_m 
   \end{array}\right.
@@
 %
-further, the solution to~\eqref{eq:rewriting:pontryagin:diff:without:facet:constraint} is only relevant for such~$p$ that can be taken to~$P_i$ for some $i\in\mathbb N_q$.
-%
-We can add that constraint to~\eqref{eq:rewriting:pontryagin:diff:without:facet:constraint} in order to obtain a linear program that is only feasible on the points which can be taken to $P_i$ for feasible $w$:
+Furthermore the solution to~\eqref{eq:rewriting:pontryagin:diff:without:facet:constraint} is only relevant for such~$p$ that can be taken to~$P_i$ for some $i\in\mathbb N_q$.
+%
+By including this constraint in~\eqref{eq:rewriting:pontryagin:diff:without:facet:constraint}, we obtain a linear program that is only feasible on the points which can be taken to $P_i$ for feasible $w$:
 %
@@
   \text{s.t.}& \Lambda_iT_jt\leq\tau\\
-  & B_j+C_j p\leq t_j\\
+  & B_k+C_k p\leq t_k\\
   &\Lambda_i p + \tau=\lambda_i\\
   &\Lambda_l(p + T_jt)\leq\lambda_l\\
-  &l\neq i, j\in\mathbb N_N
+  &l\neq i, \ j\in\mathbb N_N, \ k\in\mathbb N_m 
   \end{array}
@@
    j\in\mathbb N_N\\
-   k\in\mathbb N_q
+   k\in\mathbb N_m
    \end{array}
@@
 %
-but this is the definition of the projection onto $\mathbb R^d$.
-%
-With this the boundary of $S\ominus \mathcal W(S)$ is given as the union of projections:
+%but this is the definition of the projection onto $\mathbb R^d$.
+%
+Therefore the boundary of $S\ominus \mathcal W(S)$ can be expressed as the union of projections:
 %
@@
 \begin{equation}\label{the:way:we:compute:p:pontryagin:differences}
-  \text{vert}(S\ominus\mathcal W(S)) = \bigcup_{i\in\{1,\dots,q\}}\pi_d(\text{vert}(\tilde P_i))
-\end{equation}
-
-We further propose an alternative way of computing $S\ominus\mathcal W(S)$:
-%
-Instead of using~$\tilde P_i$ which are points~$p$ that can be taken to $P_i$ for a feasible $w\in\mathcal W(p)$ and the values of the~$\phi_i(p)$ and so on, we obtain all feasible~$p$ such that a feasible $w\in\mathcal W(p)$ exists such that $p+w$ lies on the boundary of $S$.
+  \text{vert}(S\ominus\mathcal W(S)) =
+  \bigcup_{i\in\{1,\dots,q\}}\pi_d(\text{vert}(\tilde P_i)) .
+\end{equation}
+
+We conclude this section by proposing an alternative way of computing $S\ominus\mathcal W(S)$.
+%
+%Instead of using~$\tilde P_i$, which consists of points~$p$ that can be taken
+%to $P_i$ for a feasible $w\in\mathcal W(p)$, and the values of
+%$\phi_i(p)$, 
+%we obtain all feasible~$p$ such that a feasible $w\in\mathcal W(p)$
+%exists such that $p+w$ lies on the boundary of $S$.
+%
+%To directly obtain all feasible~$p$ such that a feasible $w\in\mathcal W(p)$
+%exists such that $p+w$ lies on the boundary of $S$, c
+Consider the set
 %
@@
   \Lambda_iT_jt&\leq&\tau_i\\
-  B_i+C_i p&\leq& t_i\\
+  B_k+C_k p&\leq& t_k\\
   \Lambda_i p + \tau_i&\leq&\lambda_i\\
-  \end{array},\begin{array}{rcl}
-  j&\in&\mathbb N_N\\
-  i&\in&\mathbb N_q\end{array}
-  \right\}
-\end{equation}
-%
-The set~$L$ contains all such $p$ for which there exists a feasible $w\in\mathcal W(p)$ such that $p+w\in S$ and hence $\pi_d(L)=S\ominus\mathcal W(S)$, which does not require a vertex enumeration.
-%
+  \end{array},\begin{array}{l}
+  j\in\mathbb N_N\\
+  k\in\mathbb N_m\\
+  i\in\mathbb N_q\end{array}
+  \right\} .
+\end{equation}
+%
+The set~$L$ contains all points $p$ for which there exists a feasible $w\in\mathcal W(p)$ such that $p+w\in S$ and hence $\pi_d(L)=S\ominus\mathcal W(S)$, which does not require a vertex enumeration.
+%
+Notice that although both of the methods described in this section
+provide the same result, the first method requires the vertex
+enumeration of $q$ $(d + m + 1)$-dimensional polyhedrons, whereas the
+latter requires the projection of a $(d + m + q)$-dimensional polyhedron
+onto $\mathbb R^d$. Depending on the complexity of $S$, the appropriate method may be chosen.
 %
@@
 
-\subsection{Element wise bound sets}\label{exp:second:example}
+\subsection{Elementwise bound sets}\label{exp:second:example}
 %
@@
 \end{tikzpicture}
-\caption{$f_1(t=\frac{x_1}{2}+x_2)$ and its approximation by 9 secants used in Example~\ref{exp:second:example}.}
+\caption{$f_1(t)$, for $t=\frac{x_1}{2}+x_2$, and its approximation by 9 secants used in Example~\ref{exp:second:example}.}
 \label{fig:approximation:f1:p:diff}
@@
 \end{tikzpicture}
-\caption{$f_2(t=x_1-\frac{x_2}{2})$ and its approximation by 5 secants and 4 tangents as used in Example~\ref{exp:second:example}.}
+\caption{$f_2(t)$, for $t=x_1-\frac{x_2}{2}$, and its approximation by 5 secants and 4 tangents as used in Example~\ref{exp:second:example}.}
 \label{fig:approximation:f2:p:diff}
@@
 %
-In this paper we present a way to extend the scope of the Pontryagin difference to a wide class of sets.
-%
-We introduce the framework of parametric convexity and some of its analysis, which proves essential for the convexity of the parametric Pontryagin difference.
+In this paper we present a way to extend the scope of the Pontryagin
+difference operation to a wide class of sets and set-valued maps.
+%
+We introduce the framework of parametric convexity and related analysis, which proves essential for the convexity of the parametric Pontryagin difference.
 %

### 2017-02-01 dcg-draft.tex
reformatted as dcg-draft.tex
Reformatted for the Discrete and Computational Geometry journal
Main file: dcg-draft.tex

--- 2017-02-01 jems-draft.tex
@@
-% Modif. April 30, 2010
-% Send comments to publ@impan.pl
-
-\documentclass[a4paper, 12pt, twoside]{article}
-\usepackage{amsmath,amsthm,amssymb}
+%\documentclass{svjour3}                     % onecolumn (standard format)
+%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
+\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+%\documentclass[twocolumn]{svjour3}          % twocolumn
+%
+\smartqed  % flush right qed marks, e.g. at end of proof
+%
+\usepackage{graphicx}
+%
+\usepackage{amsmath,amssymb}
 \usepackage{times}
@@
 \usepackage{mathrsfs}
-
-\pagestyle{myheadings}
-\def\titlerunning#1{\gdef\titrun{#1}}
-\makeatletter
-\def\author#1{\gdef\autrun{\def\and{\unskip, }#1}\gdef\@author{#1}}
-\def\address#1{{\def\and{\\\hspace*{18pt}}\renewcommand{\thefootnote}{}%
-\footnote {#1}}%
-\markboth{\autrun}{\titrun}}
-\makeatother
-\def\email#1{e-mail: #1}
-\def\subjclass#1{{\renewcommand{\thefootnote}{}%
-\footnote{\emph{Mathematics Subject Classification (2010):} #1}}}
-\def\keywords#1{\par\medskip
-\noindent\textbf{Keywords.} #1}
-
-%% Numbered objects of "theorem" style (text italicized).
-%% The optional parameters indicate that all objects are numbered together, and "by section".
-%% However, you are welcome to use any other numbering system of your choice.
-
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{cor}[thm]{Corollary}
-\newtheorem{lem}[thm]{Lemma}
-\newtheorem{prob}[thm]{Problem}
-
-%% A numbered theorem with a fancy name:
-
-\newtheorem{mainthm}[thm]{Main Theorem}
-
-%% Numbered objects of "non-theorem" style (text roman):
-
-\theoremstyle{definition}
-\newtheorem{defn}[thm]{Definition}
-\newtheorem{rem}[thm]{Remark}
-\newtheorem{exa}[thm]{Example}
-
-%% An unnumbered remark:
-
-\newtheorem*{xrem}{Remark}
+% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
+%
+% insert here the call for the packages your document requires
+%\usepackage{latexsym}
+% etc.
+%
+% please place your own definitions here and don't use \def but
+% \newcommand{}{}
+%
+
+% \newtheorem{thm}{Theorem}[section]
+% \newtheorem{cor}[thm]{Corollary}
+% \newtheorem{lem}[thm]{Lemma}
+% \newtheorem{prob}[thm]{Problem}
+
+% %% Numbered objects of "non-theorem" style (text roman):
+% \theoremstyle{definition}
+% \newtheorem{defn}[thm]{Definition}
+% \newtheorem{rem}[thm]{Remark}
+% \newtheorem{exa}[thm]{Example}
 
@@
 \numberwithin{equation}{section}
-
-%%%%%%%%%%% For JEMS
-\frenchspacing
-
-\textwidth=15cm
-\textheight=23cm
-\parindent=16pt
-\oddsidemargin=-0.5cm
-\evensidemargin=-0.5cm
-\topmargin=-0.5cm
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+% Insert the name of "your journal" with
+% \journalname{myjournal}
+%
 \begin{document}
 
-%%%%% To ease editing, add:
-
-%\baselineskip=17pt
-
-%%%%%%%%%%%%%%%%
-
-%% In the running head, give an abbreviation of the title. 
-\titlerunning{Explicit Operations on Parametrised Polytopes}
-
-\title{Explicit Operations on Parametrised Polytopes}
+\title{Explicit Operations on Parametrised Polytopes}%\thanks{Grants or other notes
+%about the article that should go on the front page should be
+%placed here. General acknowledgments should be placed at the end of the article.}
+%\subtitle{Do you have a subtitle?\\ If so, write it here}
+
+%\titlerunning{Short form of title}        % if too long for running head
 
@@
 
-\date{\today}
-
-\maketitle
-
-\address{R. M. Schaich: Department of Engineering Science,
+%\authorrunning{Short form of author list} % if too long for running head
+
+\institute{R. M. Schaich: Department of Engineering Science,
   University of Oxford, Oxford, OX1 3PJ, UK; \email{rainer.schaich@eng.ox.ac.uk}
@@
 
-\subjclass{Primary 52A20, 52B55; Secondary 52B11, 52A41, 90C25}
+\date{\today}
+
+\maketitle
+
+\begin{abstract}
+The Pontryagin set difference is an operation between two sets that is used to calculate sets of safe operation in diverse applications including game theory and robust control.
+%
+We consider a particular class of set-valued maps; for this we introduce the property of parametric convexity and present some of its analytic framework.
+%
+In order to guarantee the convexity of the difference of a convex set and a set-valued map it proves necessary and sufficient that the set-valued map is parametrically convex.
+%
+For generic piecewise polyhedral set-valued maps we show that parametric convexity is equivalent to a constant combinatorial structure of all its realisations.
+%
+We present a computational method for verifying parametric convexity of a piecewise polyhedral set-valued map as well as a way to calculate the parametric Pontryagin difference between a polyhedron and a piecewise polyhedral set-valued map.
+%
+Two examples are given to illustrate the presented methodology.
+
+\keywords{Parametric convexity \and Piecewise affine set-valued map \and Pontryagin difference \and Parametrised polytopes}
+
+\subclass{52B55 \and 52A41 \and 90C25}
 % 52A20 Convex sets in $n$ dimensions (including convex hypersurfaces)
@@
 % 52C45 Combinatorial complexity of geometric structures
-
-\begin{abstract}
-The Pontryagin set difference is an operation between two sets that is used to calculate sets of safe operation in diverse applications including game theory and robust control.
-%
-We consider a particular class of set-valued maps; for this we introduce the property of parametric convexity and present some of its analytic framework.
-%
-In order to guarantee the convexity of the difference of a convex set and a set-valued map it proves necessary and sufficient that the set-valued map is parametrically convex.
-%
-For generic piecewise polyhedral set-valued maps we show that parametric convexity is equivalent to a constant combinatorial structure of all its realisations.
-%
-We present a computational method for verifying parametric convexity of a piecewise polyhedral set-valued map as well as a way to calculate the parametric Pontryagin difference between a polyhedron and a piecewise polyhedral set-valued map.
-%
-Two examples are given to illustrate the presented methodology.
-
-\keywords{Pontryagin difference, piecewise affine set-valued map,
-  parametrised polytopes, parametric convexity}
 \end{abstract}
@@
 %
-\begin{defn}[Parametric Convexity]\label{def:parametric:convexity}
+\begin{definition}[Parametric Convexity]\label{def:parametric:convexity}
 Let $\mathcal W:Y\rightarrow \mathscr P(Z)$, where $Y\ni p\mapsto \mathcal W(p) \subset Z$, be a continuous set-valued map. The map $\mathcal W$ is called \emph{parametrically convex} if it satisfies
@@
   for all $p_1,p_2\in Y$ and $\lambda\in (0,1)$.
-\end{defn}
+\end{definition}
 %
@@
 %
-\begin{defn}\label{def:graph:of:map}
+\begin{definition}\label{def:graph:of:map}
 Let $\mathcal W:Y\rightarrow \mathscr P(Z)$ be a continuous set-valued map
@@
 \begin{equation*}\begin{aligned}
-\text{int}(\mathscr G(\mathcal W)) = \{(p,z) \in Y\times Z : \forall \zeta\in\mathbb R^n\;\exists \epsilon>0,\\ \, z+\epsilon \zeta\in \mathcal W(p) \}
+\text{int}(\mathscr G(\mathcal W)) = \{(p,z) \in Y\times Z : \forall \zeta\in\mathbb R^n\;\exists \epsilon>0, \, z+\epsilon \zeta\in \mathcal W(p) \}
 \end{aligned}\end{equation*}
@@
 %
-\end{defn}
-%
-\begin{rem}
+\end{definition}
+%
+\begin{remark}
 %
@@
 %
-\end{rem}
+\end{remark}
 %
@@
 %
-\begin{thm}\label{thm:p:convexity:graph}
+\begin{theorem}\label{thm:p:convexity:graph}
 The map $\mathcal W$ is parametrically convex iff for all $(p_1,z_1), (p_2,z_2)\in\partial\mathscr G(\mathcal W)$
@@
 %
-\end{thm}
+\end{theorem}
 %
@@
 \begin{split}
-  \lambda \mathcal W(p_1)\oplus (1-\lambda)\mathcal W(p_2) = \{&z : z=\lambda z_1 + (1-\lambda) z_2,\\ &z_1\in\mathcal  W(p_1),\, z_2\in\mathcal W(p_2)\}
+  \lambda \mathcal W(p_1)\oplus (1-\lambda)\mathcal W(p_2) = \{z : z=\lambda z_1 + (1-\lambda) z_2, z_1\in\mathcal  W(p_1),\, z_2\in\mathcal W(p_2)\}
 \end{split}
@@
 %
-\begin{cor}\label{thm:inequalities:convex:concave}
+\begin{corollary}\label{thm:inequalities:convex:concave}
 %
@@
 %
-\end{cor}
+\end{corollary}
 %
@@
 %
-\begin{defn}[Parametric Pontryagin Difference]\label{def:parametric:pontryagin:difference}
+\begin{definition}[Parametric Pontryagin Difference]\label{def:parametric:pontryagin:difference}
   Let $S\subseteq Z$ and let $\mathcal W:Z\to\mathscr P(Z)$ be a continuous set-valued map such that
@@
 %
-\end{defn}
+\end{definition}
 %
@@
 %
-\begin{thm}\label{thm:convexity:of:pontryagin:difference}
+\begin{theorem}\label{thm:convexity:of:pontryagin:difference}
 Let $\mathcal W: Z\rightarrow\mathscr P(Z)$ be a given set-valued map, then the parametric Pontryagin difference $S \ominus \mathcal W(S)$ is convex for every convex $S\subseteq Z$ if and only if $\mathcal W$ is parametrically convex.
-\end{thm}
-% \begin{thm}\label{thm:convexity:of:pontryagin:difference}
+\end{theorem}
+% \begin{theorem}\label{thm:convexity:of:pontryagin:difference}
 %   Let $S\subseteq X$ be a convex set and let $\mathcal W:X\rightarrow\mathscr P(X)$ be a parametrically convex point-to-set
 %   map such that $\mathcal W(p)$ is convex for all $p\in X$, then $S\ominus \mathcal W(S)$ is convex.
-% \end{thm}
+% \end{theorem}
 %
@@
 %
-\begin{rem}
+\begin{remark}
 %
@@
 Conversely if the boundary $\partial\mathscr G(\mathcal W)$ is locally given by more than one affine function in $p\in Y$ (determined by linear inequalities), then it is locally strictly convex and can therefore not be parametrically convex.
-\end{rem}
-%
-\begin{cor}\label{thm:polytopic:set:not:p:convex}
+\end{remark}
+%
+\begin{corollary}\label{thm:polytopic:set:not:p:convex}
 The polytopic parametric set-valued map $\mathcal W(p):=\{z: a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\}$
 is not parametrically convex for any non-zero matrix $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$.
-\end{cor}
+\end{corollary}
 %
@@
 %
-\begin{cor}\label{thm:p:convexity:PWA:set:constant:num:verts}
+\begin{corollary}\label{thm:p:convexity:PWA:set:constant:num:verts}
 The generic piecewise affine polytopic parametric set-valued valued map 
@@
 is parametrically convex iff the number of vertices, $v_\kappa(p)$, and rays, $r_\eta(p)$, of~$\mathcal W(p)$ is constant for almost all $p\in Y$.
-\end{cor}
+\end{corollary}
 %
@@
 %
-\begin{cor}\label{thm:combinatorical:equivalence:alternative}
+\begin{corollary}\label{thm:combinatorical:equivalence:alternative}
 The generic set~$\mathcal W(p)$ defined by~\eqref{eq:definition:PWA:polytopic:set:general} is parametrically convex if and only if it is combinatorially equivalent for any $p_1,p_2\in Y\subseteq\mathbb R^d$ almost everywhere, i.e.\ $\mathcal W(p_1)\cong\mathcal W(p_2)$.
-\end{cor}
+\end{corollary}
 %
@@
 $$\begin{aligned}
-	\bigcup_{P\in\mathcal C}\text{vert}(P) = \bigcup_{(\ast)} \text{vert}(\pi_d(F))\\ = \bigcup_{i\in\mathbb N_m}\pi_d(\text{vert}(\epi(\phi_i))),
+	\bigcup_{P\in\mathcal C}\text{vert}(P) = \bigcup_{(\ast)} \text{vert}(\pi_d(F)) = \bigcup_{i\in\mathbb N_m}\pi_d(\text{vert}(\epi(\phi_i))),
 \end{aligned}$$
@@
 $$\begin{aligned}
-\norm{x}_P &= \max_{k\leq n}\left\{\sin\left(\frac{2\pi}{n-1}k\right) x_1 + \cos\left(\frac{2\pi}{n-1}k\right) x_2\right\}\\
- &= \max_{k\leq n}\{F_k x\}.
+\norm{x}_P &= \max_{k\leq n}\left\{\sin\left(\frac{2\pi}{n-1}k\right) x_1 + \cos\left(\frac{2\pi}{n-1}k\right) x_2\right\} = \max_{k\leq n}\{F_k x\}.
 \end{aligned}$$
@@
 
-\begin{figure}
+\begin{figure}[h]
 \centering
@@
 
+\bibliographystyle{plain}
 \bibliography{Bibliography}
-\bibliographystyle{plain}
 

### 2018-01-06 dcg-draft.tex
version submitted
Changed definition 2 (orientation cone -> normal cone) and theorem 2 and its proof

@@
   \begin{equation}\label{eq:def:parametrically:convex}
-  \mathcal W(\lambda p_1 + (1-\lambda)p_2)\subseteq\lambda \mathcal W(p_1) \oplus (1-\lambda) \mathcal W(p_2)
-  \end{equation}
-%
+  \mathcal W(\lambda p_1 + (1-\lambda)p_2)\subseteq\lambda \mathcal W(p_1) \oplus (1-\lambda) \mathcal W(p_2).
+\end{equation}
 for all $p_1,p_2\in Y$ and $\lambda\in (0,1)$.
@@
 %
-furthermore for any $(p,z)\in\partial\mathscr G(\mathcal W)$ the \emph{orientation cone} is defined as 
+furthermore for any $(p,z)\in\partial\mathscr G(\mathcal W)$ the \emph{normal cone} is defined as 
 %
 \[
-  \mathcal N\mathcal W(p,z) = \{\zeta \in\mathbb R^n: z+\epsilon \zeta \not\in \mathcal W(p)\; \forall \epsilon>0\} .
+  \mathcal N_{\mathcal W} (p,z) = \{\zeta \in\mathbb R^n: \zeta^T (y - z) \leq 0, \;  \forall y\in \mathcal W(p) \} .
 \]
@@
 %
-Note that the sets in Definition~\ref{def:graph:of:map} are defined in the space of the \emph{set variable} $z\in Y$ rather than \emph{graph variable} $(p,z)\in Y\times Z$.
-%
-Furthermore, the orientation cone contains all directions that point out of the set $\mathcal W(p)$ and hence all linear combinations thereof.
+Note that the normal cone in Definition~\ref{def:graph:of:map} is defined in the space of the \emph{set variable} $z\in Y$ rather than \emph{graph variable} $(p,z)\in Y\times Z$.
+%
+Furthermore, the normal cone $\mathcal N_{\mathcal W} (p,z)$ is the set of normals to all hyperplanes that contain $z$ but no other points in $\mathcal W(p)$.
 %
@@
 \begin{theorem}\label{thm:p:convexity:graph}
-The map $\mathcal W$ is parametrically convex iff for all $(p_1,z_1), (p_2,z_2)\in\partial\mathscr G(\mathcal W)$
-with $p_1\neq p_2$ and $\mathcal N\mathcal W(p_1,z_1)\cap\mathcal N\mathcal W(p_2,z_2)\neq\emptyset$,
+  A map $\mathcal W$ such that $\mathcal W(p)\ni 0$ for all $p\in Y$
+  is parametrically convex iff for all $(p_1,z_1), (p_2,z_2)\in\partial\mathscr G(\mathcal W)$
+  with
+  %$p_1\neq p_2$ and
+  $\mathcal N_{\mathcal W}(p_1,z_1)\cap\mathcal N_{\mathcal W}(p_2,z_2)\neq\emptyset$,
 %
@@
   %
-Assume~\eqref{eq:graph:def:p:convexity} holds for $(p_1,z_1),(p_2,z_2)\in\partial\mathscr G(\mathcal W)$.
-%
-Then the extension of the definition of the Minkowski functional (see e.g.~\cite{Rudin:91}) to the graph $\mathscr G(\mathcal W)$,
+  Consider the set $S$, defined for given $\lambda\in (0,1)$ and $p_1,p_2\in Y$ by
   \[
-\mu_{\mathscr G(\mathcal W)} \bigl(
-\mathcal W(p), z \bigr)
-:= \min_\mu \{\mu \geq 0 : z \in \mu \mathcal W(p)\},
+    S = \lambda \mathcal{W}(p_1) \oplus (1-\lambda) \mathcal{W}(p_2) 
+      = \bigl\{ z : \lambda z_1 + (1 - \lambda) z_2, \ z_1 \in\mathcal W(p_1), \ z_2 \in\mathcal W(p_2) \bigr\} .
   \]
-yields $\mu_{\mathscr G(\mathcal W)}\left(\mathcal W(\lambda p_1 + (1-\lambda)p_2),\lambda z_1+(1-\lambda)z_2\right)\geq1$ for all $\lambda\in(0,1)$. Therefore $\lambda z_1 + (1-\lambda) z_2$
-lies either outside the set $\mathcal W(\lambda p_1+(1-\lambda)p_2)$ or on its boundary for all $\lambda\in(0,1)$, and hence the set of all possible interpolation points 
-%
-\[
-\begin{split}
-  \lambda \mathcal W(p_1)\oplus (1-\lambda)\mathcal W(p_2) = \{z : z=\lambda z_1 + (1-\lambda) z_2, z_1\in\mathcal  W(p_1),\, z_2\in\mathcal W(p_2)\}
-\end{split}
-\]
-%
-contains the set $\mathcal W(\lambda p_1 + (1-\lambda)p_2)$ for all $\lambda\in(0,1)$.
-%
-Furthermore, since $\lambda(p_1,z_1)+(1-\lambda)(p_2,z_2)\not\in \text{int}(\mathscr G(\mathcal W))$ and both $(p_1,z_1)$ and $(p_2,z_2)$ lie on the boundary, either $z_1-z_2$ or $z_2-z_1$ is outward facing for both $\mathcal W(p_1)$ and $\mathcal W(p_2)$; therefore either $z_1-z_2$ or $z_2-z_1$ lies in both $\mathcal N\mathcal W(p_1,z_1)$ and $\mathcal N\mathcal W(p_2,z_2)$ and hence also in their intersection.
-
-Now suppose that $\mathcal W$ is parametrically convex and that~\eqref{eq:graph:def:p:convexity} is not satisfied for 
-some $(p_1,z_1),(p_2,z_2)\in\partial\mathscr G(\mathcal W)$ with $\mathcal N\mathcal W(p_1,z_1)\cap\mathcal 
-N\mathcal W(p_2,z_2)\neq\emptyset$, 
-%
-i.e.~that there exists $\epsilon>0$ such that the ball
-$B_\epsilon(\lambda z_1 + (1-\lambda)z_2 )$
-is contained in $\mathcal W(\lambda p_1 + (1-\lambda)p_2)$ for some $\lambda \in (0,1)$.
-%
-But this implies that $\lambda z_1 + (1-\lambda) z_2 + \epsilon\zeta \in \mathcal W(\lambda p_1+(1-\lambda)p_2)$  for all $\zeta\in\mathbb R^n$ such that $\|\zeta\| = 1$, whereas
-$\mathcal N\mathcal W(p_1,z_1)\cap\mathcal N\mathcal W(p_2,z_2)\neq\emptyset$ implies that there exists 
-$\zeta \in\mathcal N\mathcal W(p_1,z_1)\cap\mathcal N\mathcal W(p_2,z_2)$ which cannot be represented as
-$\zeta =\lambda \zeta_1+
-(1-\lambda)\zeta_2$
-with $z_1 + \epsilon \zeta_1\in\mathcal W(p_1)$ and $z_2  + \epsilon \zeta_2\in\mathcal W(p_2)$.
-%
-It follows that $\mathcal W$ cannot be parametrically convex.
+  % \begin{align*}
+  %   S &= \lambda \mathcal{W}(p_1) \oplus (1-\lambda) \mathcal{W}(p_2) \\
+  %     &= \bigl\{ z : \lambda z_1 + (1 - \lambda) z_2, \ z_1 \in\mathcal W(p_1), \ z_2 \in\mathcal W(p_2) \bigr\} .
+  % \end{align*}
+  We first show that $z\in \partial S = S \setminus \textup{int}(S)$ if and only if
+  % \begin{equation}\label{eq:Scond}
+  %   z = \lambda z_1 + (1 - \lambda) z_2
+  %   \quad \text{and} \quad
+  %   \mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset 
+  % \end{equation}
+  $z = \lambda z_1 + (1 - \lambda) z_2$ for some $z_1\in\partial \mathcal W(p_1)$ and $z_2\in\partial \mathcal W(p_2)$ such that $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$.
+  %
+
+  Specifically, if $z\in \partial S$ then $z\in S$ and there exists $\zeta\in\mathbb R^n$ such that $z + \epsilon \zeta \notin S$ for all $\epsilon > 0$.
+  %
+  From this it follows that $z = \lambda z_1 + (1-\lambda ) z_2$ for $z_1\in\partial \mathcal W(p_1)$ and $z_2\in\partial \mathcal W(p_2)$ and there exists $n\in \mathbb R^n$ such that for all $\mu \in [0,1]$ we have
+  \begin{equation}\label{eq:normal_cone_cond}
+    n^T \bigl( \mu \zeta_1 + (1-\mu) \zeta_2 \bigr) \leq 0 
+  \end{equation}
+  for all $\zeta_1$and $\zeta_2$ such that $n_1^T\zeta_1 \leq 0$ and $n_2^T\zeta_2 \leq 0$ for all $n_1\in\mathcal N_{\mathcal W}(p_1)$ and $n_2\in\mathcal N_{\mathcal W}(p_2)$.
+Note that these conditions are equivalent to the requirement that the normal cone to $S$ at $z$ is non-empty.
+  %
+  Clearly $n\in \mathcal N_{\mathcal W}(p_1)$ (since $\mu = 1$ in (\ref{eq:normal_cone_cond}) gives $n^T\zeta_1 \leq 0$) and similarly $n\in \mathcal N_{\mathcal W}(p_2)$ (since $\mu = 0$ in (\ref{eq:normal_cone_cond}) gives $n^T\zeta_2 \leq 0$), and hence $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$ is necessary for $z\in\partial S$.
+  %
+  Furthermore $n\in \mathcal N_{\mathcal W}(p_1)\cap \mathcal N_{\mathcal W}(p_2)$ is also sufficient for (\ref{eq:normal_cone_cond}) and hence also $z\in\partial S$.
+  %
+
+  The proof is completed by noting that, if $\lambda z_1 + (1-\lambda ) z_2 \in\partial S$, then  (\ref{eq:graph:def:p:convexity}) is equivalent to $\mathcal W\bigl(\lambda p_1 + (1-\lambda) p_2 \bigr) \subseteq S$, and by applying the preceding argument for all $\lambda\in (0,1)$ and all $p_1,p_2 \in Y$.
+  \qed
+% %
+% Assume~\eqref{eq:graph:def:p:convexity} holds for $(p_1,z_1),(p_2,z_2)\in\partial\mathscr G(\mathcal W)$.
+% %
+% Then the extension of the definition of the Minkowski functional (see e.g.~\cite{Rudin:91}) to the graph $\mathscr G(\mathcal W)$,
+% \[
+% \mu_{\mathscr G(\mathcal W)} \bigl(
+% \mathcal W(p), z \bigr)
+% := \min_\mu \{\mu \geq 0 : z \in \mu \mathcal W(p)\},
+% \]
+% yields $\mu_{\mathscr G(\mathcal W)}\left(\mathcal W(\lambda p_1 + (1-\lambda)p_2),\lambda z_1+(1-\lambda)z_2\right)\geq1$ for all $\lambda\in(0,1)$. Therefore $\lambda z_1 + (1-\lambda) z_2$
+% lies either outside the set $\mathcal W(\lambda p_1+(1-\lambda)p_2)$ or on its boundary for all $\lambda\in(0,1)$, and hence the set of all possible interpolation points 
+% %
+% \[
+% \begin{split}
+%   \lambda \mathcal W(p_1)\oplus (1-\lambda)\mathcal W(p_2) = \{z : z=\lambda z_1 + (1-\lambda) z_2, z_1\in\mathcal  W(p_1),\, z_2\in\mathcal W(p_2)\}
+% \end{split}
+% \]
+% %
+% contains the set $\mathcal W(\lambda p_1 + (1-\lambda)p_2)$ for all $\lambda\in(0,1)$.
+% %
+% Furthermore, since $\lambda(p_1,z_1)+(1-\lambda)(p_2,z_2)\not\in \text{int}(\mathscr G(\mathcal W))$ and both $(p_1,z_1)$ and $(p_2,z_2)$ lie on the boundary, either $z_1-z_2$ or $z_2-z_1$ is outward facing for both $\mathcal W(p_1)$ and $\mathcal W(p_2)$; therefore either $z_1-z_2$ or $z_2-z_1$ lies in both $\mathcal N_{\mathcal W}(p_1,z_1)$ and $\mathcal N_{\mathcal W}(p_2,z_2)$ and hence also in their intersection.
+
+% Now suppose that $\mathcal W$ is parametrically convex and that~\eqref{eq:graph:def:p:convexity} is not satisfied for 
+% some $(p_1,z_1),(p_2,z_2)\in\partial\mathscr G(\mathcal W)$ with $\mathcal N_{\mathcal W}(p_1,z_1)\cap\mathcal N_{\mathcal W}(p_2,z_2)\neq\emptyset$, 
+% %
+% i.e.~that there exists $\epsilon>0$ such that the ball
+% $B_\epsilon(\lambda z_1 + (1-\lambda)z_2 )$
+% is contained in $\mathcal W(\lambda p_1 + (1-\lambda)p_2)$ for some $\lambda \in (0,1)$.
+% %
+% But this implies that $\lambda z_1 + (1-\lambda) z_2 + \epsilon\zeta \in \mathcal W(\lambda p_1+(1-\lambda)p_2)$  for all $\zeta\in\mathbb R^n$ such that $\|\zeta\| = 1$, whereas
+% $\mathcal N_{\mathcal W}(p_1,z_1)\cap\mathcal N_{\mathcal W}(p_2,z_2)\neq\emptyset$ implies that there exists 
+% $\zeta \in\mathcal N_{\mathcal W}(p_1,z_1)\cap\mathcal N_{\mathcal W}(p_2,z_2)$ which cannot be represented as
+% $\zeta =\lambda \zeta_1+
+% (1-\lambda)\zeta_2$
+% with $z_1 + \epsilon \zeta_1\in\mathcal W(p_1)$ and $z_2  + \epsilon \zeta_2\in\mathcal W(p_2)$.
+% %
+% It follows that $\mathcal W$ cannot be parametrically convex.
+% \qed
 \end{proof}
@@
 Conversely, if $r(p,z)$ is concave in $p$ for all $p\in\mathbb R^d$, then the conditions of Theorem~\ref{thm:p:convexity:graph} necessarily hold.
+\qed
 \end{proof}
@@
 Therefore if $S$ is a convex polyhedron constructed so that $\{z_1\}\oplus\mathcal W(z_1)$ and $\{z_2\}\oplus\mathcal W(z_2)$ contain points lying on the same facet of $S$ (this is always possible if $S^\prime=S\ominus \mathcal W(S)$ has a non-empty interior), then there exists $\lambda \in (0,1)$ such that $\lambda z_1 + (1-\lambda) z_2 \notin S^\prime$.
-%
+\qed
 \end{proof}
@@
 is convex and violates the conditions of Theorem~\ref{thm:p:convexity:graph}.
+\qed
 \end{proof}
@@
 \begin{proof}
-For clarity this proof is divided in 3 parts:
+For clarity this proof is divided into three parts:
 \begin{enumerate}
@@
 To complete the proof we note that~\eqref{eq:derivative:condition:on:index:sets} is a degenerate condition, in the sense that an arbitrarily small perturbation will result in $v_{\kappa_1}(p) \neq v_{\kappa_2}(p)$, and we therefore disregard this possibility.
+\qed
 \end{enumerate}
-\vskip-1.15\baselineskip
 \end{proof}
@@
  use a locally redundant representation $\mathcal W(p) = \conv_\kappa\{v_\kappa(p)\}$.
+\qed
 \end{proof}

### 2018-01-06 dcg-draft.tex
minor change to the proof of Theorem 1

@@
 
-  The proof is completed by noting that, if $\lambda z_1 + (1-\lambda ) z_2 \in\partial S$, then  (\ref{eq:graph:def:p:convexity}) is equivalent to $\mathcal W\bigl(\lambda p_1 + (1-\lambda) p_2 \bigr) \subseteq S$, and by applying the preceding argument for all $\lambda\in (0,1)$ and all $p_1,p_2 \in Y$.
+  If $\lambda z_1 + (1-\lambda ) z_2 \in\partial S$, then (\ref{eq:graph:def:p:convexity}) is equivalent to $\mathcal W\bigl(\lambda p_1 + (1-\lambda) p_2 \bigr) \subseteq S$, and so proof is completed by applying the preceding argument for all $(p_1,z_1) \in\partial\mathscr G(\mathcal W)$ and $(p_2,z_2)\in\partial\mathscr G(\mathcal W)$, and all $\lambda\in (0,1)$.
   \qed

### 2018-01-06 dcg-draft.tex
corrected typo

@@
   \end{equation}
-  for all $\zeta_1$and $\zeta_2$ such that $n_1^T\zeta_1 \leq 0$ and $n_2^T\zeta_2 \leq 0$ for all $n_1\in\mathcal N_{\mathcal W}(p_1)$ and $n_2\in\mathcal N_{\mathcal W}(p_2)$.
+  for all $\zeta_1$ and $\zeta_2$ such that $n_1^T\zeta_1 \leq 0$ and $n_2^T\zeta_2 \leq 0$ for all $n_1\in\mathcal N_{\mathcal W}(p_1)$ and $n_2\in\mathcal N_{\mathcal W}(p_2)$.
 Note that these conditions are equivalent to the requirement that the normal cone to $S$ at $z$ is non-empty.

### 2018-01-06 dcg-draft.tex
corrected more typos in Theorem 1

--- 2018-01-06 dcg-draft.tex
@@
 \begin{theorem}\label{thm:p:convexity:graph}
-  A map $\mathcal W$ such that $\mathcal W(p)\ni 0$ for all $p\in Y$
-  is parametrically convex iff for all $(p_1,z_1), (p_2,z_2)\in\partial\mathscr G(\mathcal W)$
-  with
-  %$p_1\neq p_2$ and
-  $\mathcal N_{\mathcal W}(p_1,z_1)\cap\mathcal N_{\mathcal W}(p_2,z_2)\neq\emptyset$,
+  A set-valued map $\mathcal W$ satisfying $\mathcal W(p)\ni 0$ for all $p\in Y$
+  is parametrically convex iff
 %
@@
 %
-holds for all $\lambda\in(0,1)$.
+holds for all $\lambda\in(0,1)$ and all $(p_1,z_1), (p_2,z_2)\in\partial\mathscr G(\mathcal W)$ such that  $\mathcal N_{\mathcal W}(p_1,z_1)\cap\mathcal N_{\mathcal W}(p_2,z_2)\neq\emptyset$.
 %
@@
   %
-  From this it follows that $z = \lambda z_1 + (1-\lambda ) z_2$ for $z_1\in\partial \mathcal W(p_1)$ and $z_2\in\partial \mathcal W(p_2)$ and there exists $n\in \mathbb R^n$ such that for all $\mu \in [0,1]$ we have
+  From this it follows that $z = \lambda z_1 + (1-\lambda ) z_2$ for $z_1\in\partial \mathcal W(p_1)$ and $z_2\in\partial \mathcal W(p_2)$ and there exists $\nu\in \mathbb R^n$ such that for all $\mu \in [0,1]$ we have
   \begin{equation}\label{eq:normal_cone_cond}
-    n^T \bigl( \mu \zeta_1 + (1-\mu) \zeta_2 \bigr) \leq 0 
-  \end{equation}
-  for all $\zeta_1$and $\zeta_2$ such that $n_1^T\zeta_1 \leq 0$ and $n_2^T\zeta_2 \leq 0$ for all $n_1\in\mathcal N_{\mathcal W}(p_1)$ and $n_2\in\mathcal N_{\mathcal W}(p_2)$.
+    \nu^T \bigl( \mu \zeta_1 + (1-\mu) \zeta_2 \bigr) \leq 0 
+  \end{equation}
+  for all $\zeta_1$ and $\zeta_2$ such that $\nu_1^T\zeta_1 \leq 0$ and $\nu_2^T\zeta_2 \leq 0$ for all $\nu_1\in\mathcal N_{\mathcal W}(p_1)$ and $\nu_2\in\mathcal N_{\mathcal W}(p_2)$.
 Note that these conditions are equivalent to the requirement that the normal cone to $S$ at $z$ is non-empty.
   %
-  Clearly $n\in \mathcal N_{\mathcal W}(p_1)$ (since $\mu = 1$ in (\ref{eq:normal_cone_cond}) gives $n^T\zeta_1 \leq 0$) and similarly $n\in \mathcal N_{\mathcal W}(p_2)$ (since $\mu = 0$ in (\ref{eq:normal_cone_cond}) gives $n^T\zeta_2 \leq 0$), and hence $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$ is necessary for $z\in\partial S$.
-  %
-  Furthermore $n\in \mathcal N_{\mathcal W}(p_1)\cap \mathcal N_{\mathcal W}(p_2)$ is also sufficient for (\ref{eq:normal_cone_cond}) and hence also $z\in\partial S$.
-  %
-
-  The proof is completed by noting that, if $\lambda z_1 + (1-\lambda ) z_2 \in\partial S$, then  (\ref{eq:graph:def:p:convexity}) is equivalent to $\mathcal W\bigl(\lambda p_1 + (1-\lambda) p_2 \bigr) \subseteq S$, and by applying the preceding argument for all $\lambda\in (0,1)$ and all $p_1,p_2 \in Y$.
+
+  Clearly we must have $\nu\in \mathcal N_{\mathcal W}(p_1)$ (since $\mu = 1$ in (\ref{eq:normal_cone_cond}) gives $\nu^T\zeta_1 \leq 0$) and similarly $\nu\in \mathcal N_{\mathcal W}(p_2)$ (since $\mu = 0$ in (\ref{eq:normal_cone_cond}) gives $\nu^T\zeta_2 \leq 0$), and hence $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$ is necessary for $z\in\partial S$.
+  %
+  Furthermore $\nu\in \mathcal N_{\mathcal W}(p_1)\cap \mathcal N_{\mathcal W}(p_2)$ is also sufficient to ensure (\ref{eq:normal_cone_cond}) and hence also sufficient for $z\in\partial S$.
+  %
+
+  If $\lambda z_1 + (1-\lambda ) z_2 \in\partial S$, then (\ref{eq:graph:def:p:convexity}) is equivalent to $\mathcal W\bigl(\lambda p_1 + (1-\lambda) p_2 \bigr) \subseteq S$, and the proof is therefore completed by applying the preceding argument for all $(p_1,z_1) \in\partial\mathscr G(\mathcal W)$ and $(p_2,z_2)\in\partial\mathscr G(\mathcal W)$, and all $\lambda\in (0,1)$.
   \qed

### 2018-01-07 dcg-draft.tex
Fixed corollary 2

@@
 The polytopic parametric set-valued map $\mathcal W(p):=\{z: a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\}$
-is not parametrically convex for any non-zero matrix $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$.
+is not parametrically convex for any $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$ with $\text{rank}(B)>1$.
 \end{corollary}
@@
 \begin{proof}
-If $B\neq 0$, then the graph
+First, assume $\text{rank}(B)=0$, in this case the graph $\mathscr G(\mathcal W)$ is constant for all $p$
 %
 \begin{equation*}
-	\mathscr G(\mathcal W) = \{(p,z):a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\} ,
+	\mathscr G(\mathcal W) = \{(p,z):a_i z\leq c_i \; \forall i\in\mathbb N_m\},
 \end{equation*}
 %
-is convex and violates the conditions of Theorem~\ref{thm:p:convexity:graph}.
+which satisfies Theorem~\ref{thm:p:convexity:graph}.
+%
+Next assume $\text{rank}(B)=1$, this implies that the image of $B$ $\text{rg}(B)$ is one dimensional, in particular there exists $\gamma\in\mathbb{R}^m$ such that $\text{rg}(B) = \{\gamma t: t\in\mathbb R\}$.
+%
+This implies that the graph $\mathscr G(\mathcal W)$ is given by
+%
+\begin{equation*}
+  \mathscr G(\mathcal W) = \{(t,z)\in\mathbb R^{1+n}:a_i z\leq c_i-\gamma_i t \; \forall i\in\mathbb N_m\}
+\end{equation*}
+%
+which is empty for all $t>t^\ast$ for some $t^\ast$ and is a non-uniformly scaled version of $\{Az\leq c\}$ otherwise, and again satisfies Theorem~\ref{thm:p:convexity:graph}.
+%
+Now consider $\text{rank}(B)=r>1$, i.e.
+the image $\text{rg}(B)$ is higher-dimensional, i.e.
+we find $\gamma_1,\gamma_2,...$ such that $\text{rg}(B) = \{\gamma_1t_1+\gamma_2t_2+\dots:t_i\in \mathbb R\}$.
+%
+This implies that the elements of $\sum_i\gamma_i t_i$ which define the right hand side of $\mathscr{G}(\mathcal W)$
+%
+\begin{equation*}
+  \mathscr G(\mathcal W) = \{(t,z)\in\mathbb R^{r+n}:a_i z\leq c_i-\sum_j(\gamma_j)_i t_j \; \forall i\in\mathbb N_m\}
+\end{equation*}
+%
+will vary with $t$, in other words: 
+%
+For $\text{rank}(B)>2$ the graph $\mathscr G(\mathcal W)$ is given by a convex polyhedron with vertices in the parameter space, which implies that the graph is locally strictly convex and $\mathcal W(p)$ therefore violates Theorem~\ref{thm:p:convexity:graph}.
 \qed

### 2018-01-07 dcg-draft.tex
Highlighted revisions in blue text and made it clearer that the choice of a convex polyhedral S is one possible choice to demonstrate necessity in Theorem 2

--- 2018-01-06 dcg-draft.tex
@@
 
-% \newcommand{\todo}[1]{\textcolor{blue}{#1}}
+\newcommand{\revision}[1]{\textcolor{blue}{#1}}
 \newcommand{\highlight}[1]{\textcolor{red}{#1}}
@@
 %
-furthermore for any $(p,z)\in\partial\mathscr G(\mathcal W)$ the \emph{normal cone} is defined as 
+\revision{furthermore for any $(p,z)\in\partial\mathscr G(\mathcal W)$ the \emph{normal cone} is defined as}
 %
 \[
-  \mathcal N_{\mathcal W} (p,z) = \{\zeta \in\mathbb R^n: \zeta^T (y - z) \leq 0, \;  \forall y\in \mathcal W(p) \} .
+  \revision{\mathcal N_{\mathcal W} (p,z) = \{\zeta \in\mathbb R^n: \zeta^T (y - z) \leq 0, \;  \forall y\in \mathcal W(p) \} .}
 \]
@@
 %
-Note that the normal cone in Definition~\ref{def:graph:of:map} is defined in the space of the \emph{set variable} $z\in Y$ rather than \emph{graph variable} $(p,z)\in Y\times Z$.
-%
-Furthermore, the normal cone $\mathcal N_{\mathcal W} (p,z)$ is the set of normals to all hyperplanes that contain $z$ but no other points in $\mathcal W(p)$.
+\revision{Note that the normal cone in Definition~\ref{def:graph:of:map} is defined in the space of the \emph{set variable} $z\in Y$ rather than \emph{graph variable} $(p,z)\in Y\times Z$.
+%
+Furthermore, the normal cone $\mathcal N_{\mathcal W} (p,z)$ is the set of normals to all hyperplanes that contain $z$ but no other points in $\mathcal W(p)$.}
 %
@@
 \begin{theorem}\label{thm:p:convexity:graph}
-  A set-valued map $\mathcal W$ satisfying $\mathcal W(p)\ni 0$ for all $p\in Y$
+  \revision{A set-valued map $\mathcal W$ satisfying $\mathcal W(p)\ni 0$ for all $p\in Y$
   is parametrically convex iff
@@
 %
-holds for all $\lambda\in(0,1)$ and all $(p_1,z_1), (p_2,z_2)\in\partial\mathscr G(\mathcal W)$ such that  $\mathcal N_{\mathcal W}(p_1,z_1)\cap\mathcal N_{\mathcal W}(p_2,z_2)\neq\emptyset$.
+holds for all $\lambda\in(0,1)$ and all $(p_1,z_1), (p_2,z_2)\in\partial\mathscr G(\mathcal W)$ such that  $\mathcal N_{\mathcal W}(p_1,z_1)\cap\mathcal N_{\mathcal W}(p_2,z_2)\neq\emptyset$.}
 %
@@
   %
-  Consider the set $S$, defined for given $\lambda\in (0,1)$ and $p_1,p_2\in Y$ by
+  \revision{Consider the set $S$, defined for given $\lambda\in (0,1)$ and $p_1,p_2\in Y$ by
   \[
@@
   % \end{equation}
-  $z = \lambda z_1 + (1 - \lambda) z_2$ for some $z_1\in\partial \mathcal W(p_1)$ and $z_2\in\partial \mathcal W(p_2)$ such that $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$.
-  %
-
-  Specifically, if $z\in \partial S$ then $z\in S$ and there exists $\zeta\in\mathbb R^n$ such that $z + \epsilon \zeta \notin S$ for all $\epsilon > 0$.
+  $z = \lambda z_1 + (1 - \lambda) z_2$ for some $z_1\in\partial \mathcal W(p_1)$ and $z_2\in\partial \mathcal W(p_2)$ such that $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$.}
+
+  \revision{Specifically, if $z\in \partial S$ then $z\in S$ and there exists $\zeta\in\mathbb R^n$ such that $z + \epsilon \zeta \notin S$ for all $\epsilon > 0$.
   %
@@
   for all $\zeta_1$ and $\zeta_2$ such that $\nu_1^T\zeta_1 \leq 0$ and $\nu_2^T\zeta_2 \leq 0$ for all $\nu_1\in\mathcal N_{\mathcal W}(p_1)$ and $\nu_2\in\mathcal N_{\mathcal W}(p_2)$.
-Note that these conditions are equivalent to the requirement that the normal cone to $S$ at $z$ is non-empty.
-  %
-
-  Clearly we must have $\nu\in \mathcal N_{\mathcal W}(p_1)$ (since $\mu = 1$ in (\ref{eq:normal_cone_cond}) gives $\nu^T\zeta_1 \leq 0$) and similarly $\nu\in \mathcal N_{\mathcal W}(p_2)$ (since $\mu = 0$ in (\ref{eq:normal_cone_cond}) gives $\nu^T\zeta_2 \leq 0$), and hence $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$ is necessary for $z\in\partial S$.
-  %
-  Furthermore $\nu\in \mathcal N_{\mathcal W}(p_1)\cap \mathcal N_{\mathcal W}(p_2)$ is also sufficient to ensure (\ref{eq:normal_cone_cond}) and hence also sufficient for $z\in\partial S$.
-  %
-
-  If $\lambda z_1 + (1-\lambda ) z_2 \in\partial S$, then (\ref{eq:graph:def:p:convexity}) is equivalent to $\mathcal W\bigl(\lambda p_1 + (1-\lambda) p_2 \bigr) \subseteq S$, and the proof is therefore completed by applying the preceding argument for all $(p_1,z_1) \in\partial\mathscr G(\mathcal W)$ and $(p_2,z_2)\in\partial\mathscr G(\mathcal W)$, and all $\lambda\in (0,1)$.
+Note that these conditions are equivalent to the requirement that the normal cone to $S$ at $z$ is non-empty.}
+
+\revision{Clearly we must have $\nu\in \mathcal N_{\mathcal W}(p_1)$ (since $\mu = 1$ in (\ref{eq:normal_cone_cond}) gives $\nu^T\zeta_1 \leq 0$) and similarly $\nu\in \mathcal N_{\mathcal W}(p_2)$ (since $\mu = 0$ in (\ref{eq:normal_cone_cond}) gives $\nu^T\zeta_2 \leq 0$), and hence $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$ is necessary for $z\in\partial S$.
+  %
+  Furthermore $\nu\in \mathcal N_{\mathcal W}(p_1)\cap \mathcal N_{\mathcal W}(p_2)$ is also sufficient to ensure (\ref{eq:normal_cone_cond}) for all $\mu\in[0,1]$, and hence also sufficient for $z\in\partial S$.}
+  %
+
+  \revision{If $\lambda z_1 + (1-\lambda ) z_2 \in\partial S$, then (\ref{eq:graph:def:p:convexity}) is equivalent to $\mathcal W\bigl(\lambda p_1 + (1-\lambda) p_2 \bigr) \subseteq S$, and the proof is therefore completed by applying the preceding argument for all $(p_1,z_1) \in\partial\mathscr G(\mathcal W)$ and $(p_2,z_2)\in\partial\mathscr G(\mathcal W)$, and all $\lambda\in (0,1)$.}
   \qed
@@
 
-To demonstrate that parametric convexity of $\mathcal W$ is necessary for convexity of $S\ominus \mathcal W(S)$, suppose that condition~(\ref{eq:def:parametrically:convex}) does not hold and choose $z_1,z_2$ so that $\mathcal W(\lambda z_1 + (1-\lambda) z_2) \not\subseteq \lambda \mathcal W(z_1) \oplus (1-\lambda) \mathcal W (z_2)$ for some $\lambda \in (0,1)$.
+To demonstrate that parametric convexity of $\mathcal W$ is necessary for convexity of $S\ominus \mathcal W(S)$ \revision{for all convex $S$}, suppose that condition~(\ref{eq:def:parametrically:convex}) does not hold and choose $z_1,z_2$ so that $\mathcal W(\lambda z_1 + (1-\lambda) z_2) \not\subseteq \lambda \mathcal W(z_1) \oplus (1-\lambda) \mathcal W (z_2)$ for some $\lambda \in (0,1)$.
 Then there exists a value of $\lambda\in(0,1)$ such that
@@
 \end{align*}
-Therefore if $S$ is a convex polyhedron constructed so that $\{z_1\}\oplus\mathcal W(z_1)$ and $\{z_2\}\oplus\mathcal W(z_2)$ contain points lying on the same facet of $S$ (this is always possible if $S^\prime=S\ominus \mathcal W(S)$ has a non-empty interior), then there exists $\lambda \in (0,1)$ such that $\lambda z_1 + (1-\lambda) z_2 \notin S^\prime$.
+Therefore \revision{if, for example, $S$ is a convex polyhedron such that} $\{z_1\}\oplus\mathcal W(z_1)$ and $\{z_2\}\oplus\mathcal W(z_2)$ contain points lying on the same facet of $S$ (this is always possible if $S^\prime=S\ominus \mathcal W(S)$ has a non-empty interior), then there exists $\lambda \in (0,1)$ such that $\lambda z_1 + (1-\lambda) z_2 \notin S^\prime$.
 \qed

### 2018-01-07 dcg-draft.tex
Highlighted revision of Corollary 2

@@
 \begin{corollary}\label{thm:polytopic:set:not:p:convex}
-The polytopic parametric set-valued map $\mathcal W(p):=\{z: a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\}$
-is not parametrically convex for any $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$ with $\text{rank}(B)>1$.
+\revision{The polytopic parametric set-valued map $\mathcal W(p):=\{z: a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\}$
+is not parametrically convex for any $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$ with $\text{rank}(B)>1$.}
 \end{corollary}
@@
 \begin{proof}
-First, assume $\text{rank}(B)=0$, in this case the graph $\mathscr G(\mathcal W)$ is constant for all $p$
+\revision{First, assume $\text{rank}(B)=0$, in this case the graph $\mathscr G(\mathcal W)$ is constant for all $p$
 %
@@
 %
-For $\text{rank}(B)>2$ the graph $\mathscr G(\mathcal W)$ is given by a convex polyhedron with vertices in the parameter space, which implies that the graph is locally strictly convex and $\mathcal W(p)$ therefore violates Theorem~\ref{thm:p:convexity:graph}.
+For $\text{rank}(B)>2$ the graph $\mathscr G(\mathcal W)$ is given by a convex polyhedron with vertices in the parameter space, which implies that the graph is locally strictly convex and $\mathcal W(p)$ therefore violates Theorem~\ref{thm:p:convexity:graph}.}
 \qed

### 2018-01-07 dcg-draft.tex
Made some further changes to the proof of Corollary 2

--- 2018-01-07 dcg-draft.tex
@@
 \providecommand{\rk}[1]{\text{rank}\left(#1\right)}
+\DeclareMathOperator{\rank}{rank}
+\DeclareMathOperator{\interior}{int}
+\DeclareMathOperator{\image}{im}
 
@@
 \begin{equation*}\begin{aligned}
-\text{int}(\mathscr G(\mathcal W)) = \{(p,z) \in Y\times Z : \forall \zeta\in\mathbb R^n\;\exists \epsilon>0, \, z+\epsilon \zeta\in \mathcal W(p) \}
+\interior(\mathscr G(\mathcal W)) = \{(p,z) \in Y\times Z : \forall \zeta\in\mathbb R^n\;\exists \epsilon>0, \, z+\epsilon \zeta\in \mathcal W(p) \}
 \end{aligned}\end{equation*}
@@
 \[
-  \partial \mathscr G(\mathcal W) = \mathscr G(\mathcal W)\setminus \textup{int}(\mathscr G(\mathcal W))
+  \partial \mathscr G(\mathcal W) = \mathscr G(\mathcal W)\setminus \interior(\mathscr G(\mathcal W))
 \]
@@
 \begin{equation}\label{eq:graph:def:p:convexity}
-\lambda (p_1,z_1) + (1-\lambda) (p_2,z_2) \not\in\textup{int} (\mathscr G(\mathcal W))
+\lambda (p_1,z_1) + (1-\lambda) (p_2,z_2) \not\in \interior (\mathscr G(\mathcal W))
 \end{equation}
@@
   % \end{align*}
-  We first show that $z\in \partial S = S \setminus \textup{int}(S)$ if and only if
+  We first show that $z\in \partial S = S \setminus \interior(S)$ if and only if
   % \begin{equation}\label{eq:Scond}
@@
 Furthermore, for any $(p_1,z_1),(p_2,z_2)\in \partial\mathscr G(\mathcal W)\vert_{\mathcal C}$ we have
-$\lambda (p_1,z_1) + (1-\lambda) (p_2,z_2) \in\mathrm{int} (\mathscr G(\mathcal W))\vert_{\mathcal C}$ for all $\lambda\in(0,1)$ since
+$\lambda (p_1,z_1) + (1-\lambda) (p_2,z_2) \in\interior (\mathscr G(\mathcal W))\vert_{\mathcal C}$ for all $\lambda\in(0,1)$ since
 $\mathscr G(\mathcal W)\vert_{\mathcal C}$ is strictly convex in $p$.
@@
 \begin{corollary}\label{thm:polytopic:set:not:p:convex}
-The polytopic parametric set-valued map $\mathcal W(p):=\{z: a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\}$
-is not parametrically convex for any non-zero matrix $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$.
+  \revision{The polytopic parametric set-valued map $\mathcal W(p):=\{z: a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\}$
+    is  parametrically convex if and only if the matrix $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$ is such that $\rank(B) \leq 1$.}
+%is not parametrically convex for any $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$ such that $\rank (B) >1$.}
 \end{corollary}
@@
 \begin{proof}
-If $B\neq 0$, then the graph
+\revision{First assume that $B=0$. In this case the graph $\mathscr G(\mathcal W)$ is constant for all $p$, i.e.
 %
 \begin{equation*}
-	\mathscr G(\mathcal W) = \{(p,z):a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\} ,
+	\mathscr G(\mathcal W) = \{(p,z):a_i z\leq c_i \; \forall i\in\mathbb N_m\},
 \end{equation*}
 %
-is convex and violates the conditions of Theorem~\ref{thm:p:convexity:graph}.
+which clearly satisfies the  conditions of Theorem~\ref{thm:p:convexity:graph} for parametric convexity.
+%
+Next assume $\rank(B)=1$.
+This implies that the image,  $\image(B)$, of $B$ is one dimensional and in particular there exists $\gamma\in\mathbb{R}^m$ such that $\image(B) = \{\gamma t: t\in\mathbb R\}$.
+%
+This implies that the graph $\mathscr G(\mathcal W)$ can be expressed 
+%
+\begin{equation*}
+  \mathscr G(\mathcal W) = \{(t,z)\in\mathbb R^{1+n}:a_i z\leq c_i-\gamma_i t \; \forall i\in\mathbb N_m\} ,
+\end{equation*}
+%
+where $\mathcal W(t)$ is empty for all $t > t^\ast$ for some $t^\ast$ and $\mathcal W(t)$ is a scaled version of $\{ z : Az\leq c\}$ for all $t \leq t^\ast$.
+Hence the conditions of Theorem~\ref{thm:p:convexity:graph} are again satisfied.}
+%
+
+\revision{Now assume that $\text{rank}(B)=r \geq 1$. In this case
+%  $\image(B) = \{\gamma_1t_1+\cdots +\gamma_rt_r : t_1,\ldots,t_r \in \mathbb R\}$ for  some $\gamma_1, \ldots \gamma_r\in\mathbb{R}^m$.
+  $\image(B) = \{\Gamma t : t \in \mathbb R^r\}$ for  some $\Gamma \in\mathbb{R}^{m\times r}$,
+  %
+  and $\mathscr{G}(\mathcal W)$ can be expressed
+  % 
+\begin{equation*}
+  \mathscr G(\mathcal W) = \Bigl\{(t,z)\in\mathbb R^{r+n}:a_i z\leq c_i-\sum_{j=1}^r \gamma_{i,j} t_j \; \forall i\in\mathbb N_m\Bigr\},
+\end{equation*}
+%
+where $\gamma_{i,j}$ is the $(i,j)$th element of $\Gamma$.
+%
+Whenever $\text{rank}(B)\geq 2$ therefore, the graph $\mathscr G(\mathcal W)$ is given by a convex polyhedron that has vertices in the parameter space, which implies that the graph is locally strictly convex and $\mathcal W(p)$ therefore violates Theorem~\ref{thm:p:convexity:graph}.}
 \qed

### 2018-03-24 reply_to_reviewers.tex
Revised version submitted to DCG on 24 March 2018 - see reply_to_reviewers.tex for details of the revision

\documentclass[11pt, a4paper]{article}

\usepackage[tmargin=20 mm,lmargin=25 mm,rmargin=25 mm,bmargin=25 mm]{geometry}
\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage[hidelinks]{hyperref}
\usepackage{enumerate}
\usepackage{overpic}
\usepackage{mathrsfs}

%\usepackage{times}
\usepackage{xcolor} %colori
\newcommand{\corrB}[1]{{\color{blue} #1}}  %comandi per correzioni
\newcommand{\corrR}[1]{{\color{red} #1}}            %comandi per correzioni
\newcommand{\corrV}[1]{{\color{green} #1}}          %comandi per correzioni

% \newcommand{\comment}[1]{\textit{#1}}
% \newcommand{\reply}[1]{{\color{blue}{#1}}}

\newcommand{\todo}[1]{\textcolor{blue}{#1}}
\newcommand{\highlight}[1]{\textcolor{red}{#1}}
\newcommand{\comment}[1]{{%
\begin{sffamily}\leavevmode\color{black}#1
\end{sffamily}}}%

\def\baselinestretch{1.1}
\def\vv{\vspace{\baselineskip}}
\def\v{\vspace{2mm}}

\begin{document}

\raisebox{-\height}[0mm][0mm]{\includegraphics[scale=0.4]{ox_brand_cmyk_pos_rect}}

\hspace{105mm}%
\raisebox{-7.7mm}[0mm][0mm]{\begin{tabular}{@{}l@{}}
Department of Engineering Science\\
University of Oxford\\
Oxford, OX1 3PJ, UK\\
% \begin{tabular}[t]{@{}ll@{}}
% tel: & +44 1865 273000\rule{0pt}{12pt}\\ 
% e-mail: & \texttt{mark.cannon@eng.ox.ac.uk}
% \end{tabular}
{mark.cannon@eng.ox.ac.uk}
\\
\today\rule{0pt}{25pt}
\end{tabular}}

\vspace{30mm}

\begin{tabular}{@{}l@{}} 
Dr.~Kenneth Clarkson\\
Co-Editor-in-Chief\\
Discrete \& Computational Geometry
\end{tabular}

\vspace{15mm}

\noindent Dear Dr.\ Clarkson,

\textbf{Manuscript ID DCGE-D-17-00022, ``Explicit Operations on Parametrised Polyhedra''\\
by Rainer Manuel Schaich and Mark Cannon}

Please find attached a revised manuscript taking into account the reviewers' comments. Changes are in blue to facilitate identification.

In particular:

\begin{itemize}
\item[--] We provide better motivation for the idea of the parametric Pontryagin difference in the Introduction, and give clearer and more intuitive explanations for our results throughout the paper.
\item[--] We have corrected Definition 3 (previously called Definition 2) and re-written Lemma 1 (previously called Theorem 1) to address the reviewers' concerns about the conditions for parametric convexity, and we have corrected Theorem 3 (previously called Corollary 2) according to the suggestion of the second reviewer. We have likewise simplified and clarified the proof of Theorem 4 (previously called Corollary 3), as requested by the second reviewer.
\item[--] We have improved the clarity and precision of the text throughout the paper.
\end{itemize}

%replies to the editor's and reviewers' reports  
The attached replies to the reviewers give detailed point-by-point responses to the review comments.

Yours sincerely,

\includegraphics[scale=0.08]{MRCannon_black_signature.jpg}

Mark Cannon

\newpage

% \vv

% \centerline{\rule{0.9\textwidth}{0.25pt}}

\subsection*{Review 1}

\textbf{Comment 1.1:}
\comment{[Overview] This paper introduces parametric convexity as a property of set-valued maps and shows how it can be used for set-valued maps whose images are polyhedra.
I really like the concept of parametric convexity, this is something new under the sun. However, the writeup needs a substantial revision for this paper to become suitable for DCG. The paper is missing a story, and statements as well as proofs tend to be unclear. I also have doubts concerning the correctness of the main result, as it builds on a technical result (Theorem 1) that seems false, at least in the way it is presented now.
I therefore recommend to reject the paper, but ask the authors to re-submit, should they be able to fix the problems indicated below and tell a coherent story around it.
Here is the story that I would tell after reading the paper. Maybe the authors can draw some inspiration from it\dots}

\v
\textbf{Response 1.1:}
We would like to thank the reviewer for this overall positive assessment and for providing helpful and constructive suggestions for improving the paper.

We have acted on the reviewer's advice to improve the motivation for the paper with a simple example illustrating the concept of the parametric Pontryagin difference. This is now included in the Introduction.

We have clarified a number of statements throughout the paper, introducing Definition 1, correcting Definition 3 and re-writing Lemma 1 and Theorems 3 and 4. We have also simplified and clarified the proof of Theorem 4 by introducing two new lemmas (Lemma 2 and Lemma~3).

\v
\textbf{Comment 1.2:}
\comment{
[Characterization of parametric convexity?] Theorem 1 (which should
actually be a lemma, as it is a technical tool) claims to give a characterization 
of parametric convexity in the case where $P$ is continuous and all ``slices'' $P(y)$ are convex\dots In fact, I didn’t understand the proof in the paper at all. Therefore, I also could not identify a version of Theorem 1 that is true. The issue is somewhat severe, since several corollaries and also the main result are drawn from this characterization.
}

\v
\textbf{Response 1.2:}
The revised the paper includes corrections to Definition 3 (previously called Definition 2) and Lemma 1 (previously called Theorem 1) that address the reviewer's concerns about the characterization of parametric convexity. In particular, the statement of Lemma 1 now includes the condition that $\mathcal W(p)$ must contain $0$, which prevents the particular problem pointed out by the reviewer for the case in which $\mathcal W(p)$ is a singleton for all $p$, and the proof of Lemma 1 has been entirely re-written.

\v
\textbf{Comment 1.3:}
\comment{
Generally, you need to be more precise. An example is Corollary 3. Apart from the fact that it is a bit unusual to call the central result ``Corollary 3'', it has the following issues: When you say that the number of vertices and rays is constant, this can mean several things. It can mean $O(1)$, or it can mean some fixed number (which is what you need). Also, you should say what the $b_{i,k}$ and $c_{i,k}$ are, currently, they are just ``free variables''. Also, if you say, ``within any partition'', you mean ``within any member of the partition''. When you say ``polytopic'', you mean ``polyhedric'', and whatever you say, it should be defined what you mean.}

\v
\textbf{Response 1.3:}
Corollary~3 is replaced with Theorem~4 in the revised paper. In this and the supporting Lemmas 2 and 3, we have been careful to state that the number of vertices is assumed to be equal to a given integer rather than simply constant. The revised paper explains the parameters that define the polyhedral maps in Theorem 3 and Theorem 4 (which is now stated in terms of the map given in equation (4.2)), and gives their dimensions. We have corrected the references to the partition of $Y$ and have replaced the term ``polytopic'' with ``polyhedral'' throughout the paper.

\v
\textbf{Comment 1.4:}
\comment{
p5, l16: (3.2) does not require the graph to be non-convex. If the graph was a hyperplane, say, you could still have (3.2).}

\v
\textbf{Response 1.4:}
This has been corrected in the revised paper (last paragraph on p.5).

\v
\textbf{Comment 1.5:}
\comment{
p3, l33: when you say that you use the Perles conjecture, you should (a) mention that the conjecture has has been proved, and (b) cite Blind and Mani who first proved it. At least the version you need, there does not seem to be a standard meaning of the Perles conjecture.}

\v
\textbf{Response 1.5:}
Done (in the second paragraph on p.4 and the proof of Corollary 1 on p.11).

\v
\textbf{Comment 1.6:}
\comment{
p4, l47-49: this implication is unclear to me. If the Minkowski sum $\lambda \mathcal W (p_1) \oplus (1 - \lambda)\mathcal W(p_2)$ is linearly separable from the slice $\mathcal W(\lambda y_1 + (1 - \lambda)y_2)$, then I see no argument here. Even if this is not the case, one would have to argue more.}

\v
\textbf{Response 1.5:}
We agree that this was unclear and its replacement in the revised paper  (Lemma~1) has an entirely new proof.

\newpage
\subsection*{Review 2}

\textbf{Comment 2.1:}
\comment{One has a feeling (based only on visualization of very low dimensional instances) that the authors probably have a correct algorithm for their computations, but the presentation of the proof is not good. The parts of Definition 2 related to the ``orientation cone'' are wrong, and it appears that the proof of Theorem 1 is wrong, too. The proof on page 8 is hard to follow. The style of rambling notes would be better replaced by lemmas, with clearer statements of what is to be proved.}

\v
\textbf{Response 2.1:}
Definition 3 (called Definition 2 in the previous version of the paper) has been corrected in the revised paper, and the ``orientation cone'' that was previously used has been replaced with a reference to the more standard ``normal cone''. Lemma 1 (previously called Theorem 1) has been rewritten and its proof has been corrected. The proof that the reviewer refers to on page 8, which has been replaced with the proof of Theorem 4 in the revised paper, has also been completely rewritten. To simplify and clarify the arguments we have introduced two intermediate results, Lemma 2 and Lemma 3.

\textbf{Comment 2.2:}
\comment{
Page 1, line 46: Delete the ``a'' from for a its.\\
Page 2, line 32: Delete the extra ``the'' in the the.\\
Page 2, line 37: only on $\Omega$.\\
Page 2, paragraph from line 32 to line 43: Some sentences here link unrelated definitions by commas when it would be better to separate them into smaller sentences.}

\v
\textbf{Response 2.2:}
Done

\v
\textbf{Comment 2.3:}
\comment{
Page 3, line 8: ``\dots given by the graph of a continuous function.'' What function is this?}

\v
\textbf{Response 2.3:}
We agree that this statement was unclear and we have removed it from the revised paper.

\v
\textbf{Comment 2.4:}
\comment{
Page 3, line 17: then there exists}

\v
\textbf{Response 2.4:}
Corrected.

\v
\textbf{Comment 2.5:}
\comment{
Page 3, line 47: If the containment goes the other way, this is called a convex set-valued function. Wasowicz, in arxiv.org/pdf/1611.02584.pdf, calls set-valued functions with the containment as in this Definition concave.
}

\v
\textbf{Response 2.5:}
We thank the reviewer for pointing out this reference, which is included in the revised paper.

\v
\textbf{Comment 2.6:}
\comment{
Page 4, line 22: The orientation cone defined here is not a cone if $z$ is a vertex of $\mathcal W(p)$.
}

\v
\textbf{Response 2.6:}
The orientation cone in the previous version of the paper has been replaced with a reference to the normal cone in Definition 3.

\v
\textbf{Comment 2.7:}
\comment{
Page 4, line 28: Why should it contain “all linear combinations thereof?”
}

\v
\textbf{Response 2.7:}
This statement has been removed from Remark~1, which now refers to the normal cone.

\v
\textbf{Comment 2.8:}
\comment{
Page 4, line 34: I do not believe that Theorem 1 is true with the given definition of $\mathcal N$. If $\mathcal N$ were the normal cone of $\mathcal W(p)$ at $z$, then it might be true.\\
Page 5, line 1: Why is it necessary to find a vector in the intersection of these two ``cones?'' Parametric convexity is what was to be proved, and that has been done.\\
Page 5, line 13: Why does it follow that $\mathcal W$ cannot be parametrically convex? If you let $\mathcal W(y) = [0,1] \times [0,1]$ for all $y \in [0,1]$, $z_1 = (1,1/2)$ and $z_2 = (1/2,1)$, then $\mathcal N_{\mathcal W} (0,z_1) \cap \mathcal N_{\mathcal W}(1,z_2) \neq \emptyset$ but $(1/2)(0,z_1) + (1/2)(1, z_2) \in int(\mathscr G(\mathcal W))$ and $\mathcal W$ is parametrically convex.}

\v
\textbf{Response 2.8:}
The reviewer is correct that the previous version of the paper had an error in Theorem~1. This has been replaced with Lemma 1 in the revised paper, which is stated in terms of normal cones. The proof of Lemma 1 is has been completely reconstructed, and it does not suffer from the problems that the reviewer mentions here.

\v
\textbf{Comment 2.9:}
\comment{
Page 5, line 42: It would be useful to give a definition of the usual Pontryagin difference, in order to contrast it with the parametric one.
}

\v
\textbf{Response 2.9:}
This is now done in the section on notation  at the end of the Introduction

\v
\textbf{Comment 2.10:}
\comment{
 Page 6, line 32: ``this is always possible if $S' = S \ominus \mathcal W(S)$ has a non- empty interior.'' This is a condition for constructing $S$, but it involves $S$ itself. Why can’t $\{z_1\} \oplus \mathcal W(z_1)$ be contained in the interior of $\{z_2\} \oplus \mathcal W(z_2)$, for example?
}

\v
\textbf{Response 2.10:}
This part of the proof shows that parametric convexity is necessary for $ S \ominus \mathcal W(S)$ to be convex for all convex sets $S$ (this is emphasised more clearly in the revised paper), therefore we only need to be able to construct one convex $S$ for which $ S \ominus \mathcal W(S)$ is non-convex and we are free to choose $z_1$ and $z_2$.

\v
\textbf{Comment 2.11:}
\comment{
Page 7, line 11: It seems like the boundary would still be locally affine if $B$ contained one nonzero row, or if $B$ were a rank one matrix.
}

\v
\textbf{Response 2.11:}
We agree and have corrected this statement (Theorem 3) in the revised paper.

\v
\textbf{Comment 2.12:}
\comment{Page 7, line 11: Why are the roles of $b$ and $c$ interchanged between Corollary 2 and Corollary 3?}

\v
\textbf{Response 2.12:}
This has been changed in the revised paper so that parameters $b$ and $c$ have the same roles throughout Sections 4 and 5.

\v
\textbf{Comment 2.13:}
\comment{
Page 7, line 21: It would be helpful to get a definition of a generic piecewise affine polytopic set-valued map. Does it only mean that each $\mathcal W(p)$ is simple? The statement in the introduction is vague.}

\v
\textbf{Response 2.13:}
This is now defined (Definition 1) in Section 2

\v
\textbf{Comment 2.14:}
\comment{
Page 7, line 30: What is the index set for $k$?
}

\v
\textbf{Response 2.14:}
The index set for $k$ is now stated in the revised paper.

\v
\textbf{Comment 2.15:}
\comment{
Page 7, line 45: $\mathscr G(\mathcal W)$ consists of pairs $(p,z)$.}

\v
\textbf{Response 2.15:}
This has been corrected.

\v
\textbf{Comment 2.16:}
\comment{Page 8, line 18: What does it mean for two vertices to merge?}

\v
\textbf{Response 2.16:}
This terminology was rather imprecise and the revised does not refer to vertices merging, but refers to changes in the number of vertices of $\mathcal W(p)$ instead.

\v
\textbf{Comment 2.17:}
\comment{Page 8, line 20: Should it be for $p$ such that $fp = g$?}

\v
\textbf{Response 2.17:}
The revised paper provides a new proof of Theorem 4, which no longer uses this argument.

\v
\textbf{Comment 2.18:}
\comment{Page 9, line 7: W(p) is a set-valued map. W(p1) and W(p2) are sets.}

\v
\textbf{Response 2.18:}
This has been corrected in the revised paper.

\v
\textbf{Comment 2.19:}
\comment{Page 11, line 8: What does admissible mean? Does $w^\ast$ have to be in $\mathcal W(p)$? Later, “feasible” is used.}

\v
\textbf{Response 2.19:}
References to admissible/feasible $w$ have been replaced with $w\in\mathcal W(p)$ in the revised paper.

\v
\textbf{Comment 2.20:}
\comment{Page 11, line 19: It would help to see a definition of the term shape.}

\v
\textbf{Response 2.20:}
The reference to ``the shape of the solution over $p$'' has been replaced with ``the dependence of the solution on $p$''.

\v
\textbf{Comment 2.21:}
\comment{Page 11, line 31: an element-wise\\
Page 13, line 11: we require a\\
Page 17, line 27: The same authors have a 2007 paper in Journal of Optimization Theory and Applications with almost the same name. Presumably it is an improved and more accessible version.}

\v
\textbf{Response 2.20:}
Done.

\newpage

\subsection*{Review 3 (included in the Editor's email)}

\textbf{Comment:}
\comment{
An informal quick comment by another expert may be of interest,
and I include it in case it might be helpful:

"I went quickly through the paper. Certainly, it contains interesting results, but the
way it is written hides the most interesting result in my opinion. The most interesting
result for me is at the last sentence of Section 3, "Pontriyagin difference \dots\ is itself
polyhedral." This statement gives a strong incentive to find an algorithm. Without this,
one cannot hope to compute the difference. Why don't the authors write this at the
beginning and motives the notion such as continuity and parametric convexity of
set-valued maps as they are necessary conditions for the polyhedrality of the difference?
Anyway, the paper is pretty good, assuming the proofs are correct."
}

\v
\textbf{Response:}
We thank the reviewer for this positive assessment. We feel that the property that the parametric Pontryagin difference between a convex polyhedral set and a piecewise affine polyhedral set-valued map is polyhedral is not so surprising, given that the usual Pontryagin difference between two polyhedral sets is polyhedral. We are also unclear about what the reviewer means by an incentive to find an algorithm [for computing the parametric Pontryagin difference], since the paper does discuss the computational tools needed to determine the parametric Pontryagin difference in Section 5. In fact two computational methods are proposed, based respectively on vertex enumeration and projection.

\end{document}

### 2018-03-24 AutomaticaDraft.tex
Revised version submitted to DCG on 24 March 2018 - see reply_to_reviewers.tex for details of the revision

--- 2017-01-09 draft.tex
@@
-\documentclass[final]{elsarticle}
+\documentclass[twocolumn]{autart}
 
@@
 
-\usepackage{amsmath,amsthm,amssymb,mathrsfs}
-
-\journal{Computational Geometry: Theory and Applications}
+\usepackage{amsmath,amssymb,mathrsfs}
+% \usepackage{amsthm}
+
+% \journal{Computational Geometry: Theory and Applications}
 
@@
 
-\newcounter{thmcount}
-\renewcommand{\thethmcount}{\arabic{thmcount}}
+% \newcounter{thmcount}
+% \renewcommand{\thethmcount}{\arabic{thmcount}}
 \renewcommand{\theequation}{\arabic{section}.\arabic{equation}}
@@
 
-\newtheorem{thm}[thmcount]{Theorem}
-\newtheorem{cor}[thmcount]{Corollary}
-\newtheorem{prop}[thmcount]{Proposition}
-
-\theoremstyle{remark}
-\newtheorem{rem}[thmcount]{Remark}
-
-\theoremstyle{definition}
-\newtheorem{defi}[thmcount]{Definition}
-\newtheorem{alg}[thmcount]{Algorithm}
+% \newtheorem{thm}[thmcount]{Theorem}
+% \newtheorem{cor}[thmcount]{Corollary}
+% \newtheorem{prop}[thmcount]{Proposition}
+
+% \theoremstyle{remark}
+% \newtheorem{rem}[thmcount]{Remark}
+
+% \theoremstyle{definition}
+% \newtheorem{defi}[thmcount]{Definition}
+% \newtheorem{alg}[thmcount]{Algorithm}
 
@@
 %% or include affiliations in footnotes:
-\author{Rainer M. Schaich\fnref{akn}}
-\ead{rainer.schaich@eng.ox.ac.uk}
-\fntext[akn]{Supported by the EPSRC DTA and the Worcester College Martin Senior Scholarship}
-
-\author{Mark Cannon\fnref{coa}}
-\ead{mark.cannon@eng.ox.ac.uk}
-\fntext[coa]{Corresponding author}
+\author{Rainer M. Schaich}\ead{rainer.schaich@eng.ox.ac.uk},
+% \thanksref{Supported by the EPSRC DTA and the Worcester College Martin Senior Scholarship},
+\author{Mark Cannon}\ead{mark.cannon@eng.ox.ac.uk}
+% \fntext[akn]{Supported by the EPSRC DTA and the Worcester College Martin Senior Scholarship}
+% \fntext[coa]{Corresponding author}
 
@@
 %
-\begin{proof}
+\begin{pf}
 %
@@
 It follows that $\mathcal W$ cannot be parametrically convex.
-\end{proof}
+\end{pf}
 %
@@
 %
-\begin{proof}
+\begin{pf}
 First note that $r(p,z)$ is assumed to be a convex function of $z$ for any given value of $p$ so that $\mathcal W(p)$ is a convex set for each $p\in\mathbb R^d$.
@@
 Conversely, if $r(p,z)$ is concave in $p$ for all $p\in\mathbb R^d$, then the conditions of Theorem~\ref{thm:p:convexity:graph} necessarily hold.
-\end{proof}
+\end{pf}
 %
@@
 %
-\begin{proof}
+\begin{pf}
 To prove convexity of $S^\prime =  S\ominus \mathcal W( S)$ when $\mathcal W$ is parametrically convex we pick any $z_1,z_2\in S^\prime$, then
@@
 %
-\end{proof}
+\end{pf}
 %
@@
 %
-\begin{proof}
+\begin{pf}
 If $B\neq 0$, then the graph
@@
 is convex and violates the conditions of Theorem~\ref{thm:p:convexity:graph}.
-\end{proof}
+\end{pf}
 %
@@
 %
-\begin{proof}
+\begin{pf}
 For clarity this proof is divided in 3 parts:
@@
 \vskip-1.15\baselineskip
-\end{proof}
+\end{pf}
 %
@@
 %
-\begin{proof}
+\begin{pf}
 Two polyhedra are combinatorially equivalent if there exists a bijection between all their faces which preserves the inclusion, see e.g.~\cite{Ziegler:1995}.
@@
  use a locally redundant representation $\mathcal W(p) = \conv_\kappa\{v_\kappa(p)\}$.
-\end{proof}
+\end{pf}
 %
@@
 
-\section*{References}
-
 \bibliography{Bibliography}

### 2018-03-24 dcg-draft.tex
Revised version submitted to DCG on 24 March 2018 - see reply_to_reviewers.tex for details of the revision

@@
 \providecommand{\abs}[1]{\left|#1\right|}
-\providecommand{\span}{\text{span}}
-\providecommand{\conv}{\text{conv}}
-\providecommand{\epi}{\text{epi}}
-\providecommand{\rk}[1]{\text{rank}\left(#1\right)}
 \DeclareMathOperator{\rank}{rank}
@@
 \DeclareMathOperator{\image}{im}
+\DeclareMathOperator{\vertices}{vert}
+\DeclareMathOperator*{\conv}{conv}
+\DeclareMathOperator{\epi}{epi}
 
@@
 
-\title{Explicit Operations on Parametrised Polytopes}%\thanks{Grants or other notes
+\title{Explicit Operations on Parametrised Polyhedra}%\thanks{Grants or other notes
 %about the article that should go on the front page should be
@@
 %
-For generic piecewise polyhedral set-valued maps we show that parametric convexity is equivalent to a constant combinatorial structure of all its realisations.
+For generic piecewise polyhedral set-valued maps we show that parametric convexity is equivalent to a fixed combinatorial structure of all its realisations.
 %
@@
 
-\keywords{Parametric convexity \and Piecewise affine set-valued map \and Pontryagin difference \and Parametrised polytopes}
+\keywords{Parametric convexity \and Piecewise affine set-valued map \and Pontryagin difference \and Parametrised polyhedra}
 
@@
 It was implicitly reintroduced in the context of
-differential games in~\cite{Pontryagin:1966}, where it was used to characterise safe sets for which strategies could be found which keep elements inside some second set for all possible adversary actions.
-%
-Since its introduction, the usage of the Pontryagin difference has been extended beyond applications in differential games to various scenarios in which safe sets are needed that withstand some perturbation.
-%
-See for example~\cite{blanchini:2007} for a its use as a robust
-control analysis tool in several different contexts and under the name
+differential games in~\cite{Pontryagin:1966}, where it was used to characterise safe sets for which there exist strategies for restricting system parameters to desired sets for all possible adversary actions.
+%
+Since its introduction, the usage of the Pontryagin difference has been extended beyond applications in differential games to various scenarios in which safe sets are needed to withstand unknown disturbances.
+%
+For example~\cite{blanchini:2007} describes its use as a robust
+control analysis tool in several different contexts under the name
 (set-)erosion. It has also found use in morphological image analysis, e.g.~\cite{Haralick:1987}.
@@
 
-When the Pontryagin difference has to be performed explicitly by numerical algorithms, it is usually assumed that the respective sets are polytopic, since it is not possible to operate on general sets explicitly.
+When the Pontryagin difference has to be performed explicitly by numerical algorithms, it is usually assumed that the respective sets are polyhedral, since it is not possible to operate on general sets explicitly.
 %
 Algorithms to determine the Pontryagin difference between two
-polytopes do not require more complex computation than the solving of
+polyhedra do not require more complex computation than the solution of
 linear programs~\cite{Kolmanovsky:1998,Kerrigan:2003}, and their
@@
 The sets on which these operations can be performed are fixed
-predetermined polytopes but, due to their physical interpretation in
+predetermined polyhedra but, due to their physical interpretation in
 terms of safe sets, it can be desirable to extend the class of sets on which these operations can be performed.
@@
 For this purpose we consider the case in which the subtrahend is a
-set-valued map with a polytopic realisation.
+set-valued map with a polyhedral realisation.
 
@@
 %
-The set-valued maps we consider are parametrised polytopes with a property we introduce as \emph{parametric convexity} which allows us to guarantee that the \emph{parametric Pontryagin difference} is convex for all convex minuend sets.
-%
-We provide the computational framework to allow us to perform parametric Pontryagin differences explicitly.
+The set-valued maps we consider are parametrised polyhedra with a property we introduce as \emph{parametric convexity} which allows us to guarantee that the \emph{parametric Pontryagin difference} is convex for all convex minuend sets.
+%
+We also describe computational methods that allow the parametric Pontryagin difference to be determined explicitly.
+
+\revision{To motivate the main issues addressed by this paper using a very simple example, consider the problem of determining the safe set for the state $x$ of a system in order to ensure that the successor state $x^+ = x + w$ lies in a given set $S$, where $w$ is the action of an adversary that satisfies $w\in\mathcal W$ for some known set $\mathcal W$.
+The safe set for $x$ in this problem is precisely the Pontryagin difference between $S$ and $\mathcal W$.
+%
+Now suppose that the adversary action $w$ is not independent of $x$ but instead belongs to a set $\mathcal W(x)$ that depends explicitly on $x$.
+In this case the safe region is the set of points $x$ satisfying $x+w\in S$ for all $w\in \mathcal W(x)$, which is by definition the parametric Pontryagin difference between the set $S$ and the set-valued map $\mathcal W(x)$.
+%
+To be of use as a computational tool, the Pontryagin difference between a convex set $S$ and a set-valued map $\mathcal W(x)$ should be convex for a well-defined class of maps $\mathcal W(x)$; the paper characterizes this class by introducing the concept of and conditions for parametric convexity.
+%
+In many applications the sets of interest are either polyhedral or bounded by polyhedra.
+The paper determines the conditions under which a polyhedral set-valued map is parametrically convex, discusses computational methods for checking parametric convexity, and describes how to compute the parametric Pontryagin difference between a polyhedron and a polyhedral set-valued map.
+}
 
@@
 %
-Section~\ref{sec:computational:methods} elaborates on how to determine whether a polyhedral map is in fact parametrically convex and how to perform operations on such set-valued maps, these concepts are then illustrated in Section~\ref{sec:numerical:examples} by two examples and finally we conclude the paper in Section~\ref{sec:conclusion}.
-
-Throughout this paper we refer to the the real $d$-dimensional parameter space as $Y\subseteq\mathbb R^d$, the $n$-dimensional realisation space as~$Z\subseteq\mathbb R^n$ and its power set~$\mathscr P(Z)$.
-%
-We denote the integer range~$\{1,\dots,m\}$ by~$\mathbb N_m$ and index sets by $\mathcal A,\,\mathcal J$ or $\mathcal I$, the complement of a subset of an index set $\mathcal I\subset\mathcal A$ is denoted by $\bar{\mathcal I}=\mathcal A\setminus\mathcal I$, the objects $a_{\mathcal I}$ and $b_{\mathcal I}$ denote the matrix and the column vector with rows given by the row vectors $a_i$ and the scalar values $b_i$ with $i\in\mathcal I$.
-%
-By $f\vert_\Omega$ we mean $f$ evaluated only $\Omega$, a ball centred around $c$ of radius $r$ is denoted by $B_r(z)=\{x:\norm{x-z}_2\leq\epsilon\}$ with the Euclidean norm $\norm{\cdot}_2$.
-%
-The Minkowski sum~\cite{Minkowski:1911} of the sets $X_1,X_2$ is denoted by $X_1\oplus X_2$, for a $d_2$ dimensional set $X$ the projection onto $\mathbb R^{d_1}$ with $d_1\leq d_2$ is denoted by $\pi_{d_1}(X) = \{x\in\mathbb R^{d_1}:\exists \tilde x\in\mathbb R^{d_2-d_1} (x,\tilde x)\in X\}$.
-%
-For a polytopic set $X$ the set of its vertices is denoted by $\text{vert}(X)$.
+Section~\ref{sec:computational:methods} elaborates on how to determine whether a polyhedral map is in fact parametrically convex and how to perform operations on such set-valued maps, these concepts are then illustrated in Section~\ref{sec:numerical:examples} by numerical examples and finally we conclude the paper in Section~\ref{sec:conclusion}.
+
+Throughout this paper we refer to the real $d$-dimensional parameter space as $Y\subseteq\mathbb R^d$, the $n$-dimensional realisation space as~$Z\subseteq\mathbb R^n$ and its power set~$\mathscr P(Z)$.
+%
+We denote the integer range~$\{1,\dots,m\}$ as~$\mathbb N_m$, and symbols $\mathcal A$, $\mathcal I$ are used to denote index sets.
+%, the complement of a subset of an index set $\mathcal A\subset\mathcal I$ is denoted $\bar{\mathcal A}=\mathcal I\setminus\mathcal A$.
+%, the objects $a_{\mathcal I}$ and $b_{\mathcal I}$ denote the matrix and the column vector with rows given by the row vectors $a_i$ and the scalar values $b_i$ with $i\in\mathcal I$.
+%
+By $f\vert_\Omega$ we mean $f$ evaluated only on $\Omega$.
+The $n$-ball of radius $r$ centred at $c$ is denoted $B_r^n(c)=\{x\in\mathbb R^n :\norm{x-c}_2\leq r\}$, where $\norm{\cdot}_2$ is the Euclidean norm.
+%
+\revision{The Minkowski sum~\cite{Minkowski:1911} of sets $X_1,X_2\subset\mathbb R^n$ and their Pontryagin difference are respectively denoted
+\begin{align*}
+X_1\oplus X_2 &=\{x_1 + x_2 : x_1\in X_1, \, x_2\in X_2 \} , \\
+X_1\ominus X_2 &=\{x\in\mathbb R^n : x + x_2 \in X_1, \, \forall x_2\in X_2\} .
+% X_1\oplus X_2 &=\{x\in\mathbb R^n : \exists x_1\in X_1, \, x_2\in X_2 \text{ such that } x = x_1+x_2 \} . \\
+% X_1\ominus X_2 &=\{x\in\mathbb R^n : x+x_2 \in X_1, \, \forall x_2\in X_2\} .
+\end{align*}
+%
+The projection of a set $X\subset \mathbb R^{n_2}$ onto $\mathbb R^{n_1}$, with $n_1\leq n_2$, is denoted 
+\[
+\pi_{n_1}(X) = \{x\in\mathbb R^{n_1}: (x,\tilde x)\in X, \, \tilde x\in\mathbb R^{n_2-n_1} \}.
+\]
+%
+We use the terms `polyhedron' and `polyhedral set' interchangeably to denote any set that can be expressed as the intersection of finitely many closed half-spaces in $\mathbb{R}^n$, for arbitrary $n$.
+The set of all vertices of a polyhedral set $X$ is denoted $\vertices(X)$.}
 %
@@
 
-Throughout the paper we deal with set-valued maps, i.e.
-functions that map an element of a metric space~$Y$ to a subset of a metric space~$Z$, that is $f:Y\mapsto\mathscr P(Z), Y\ni y\rightarrow f(y)\subset Z$.
-%
-A detailed presentation on properties of set-valued maps is beyond the scope of this paper and we refer to~\cite{Aubin:2009}, here we only assume that the set-valued map is continuous in the sense that its \emph{graph}
+The paper makes extensive use of the concept of a set-valued map; this is a function $f$ that maps an element of the metric space~$Y$ to a subset of the metric space~$Z$, i.e.\ $f:Y\mapsto\mathscr P(Z), Y\ni y\rightarrow f(y)\subset Z$.
+%
+We refer the reader to~\cite{Aubin:2009} for a detailed discussion of the properties of set-valued maps. Here we only assume that the set-valued map is continuous in the sense that its \emph{graph} 
 %
@@
 %
-has a continuous boundary, i.e. for every bounded point $(y,z)\in\partial\mathscr G(f)$ the boundary $\partial\mathscr G(f)$ is locally given by the graph of a continuous function.
-%
-We only consider set-valued maps with convex images, i.e. maps for which $z_1,z_2\in f(y)\Rightarrow \lambda z_1+(1-\lambda)z_2\in f(y)$ for all $\lambda\in[0,1]$ holds for all $y\in Y$.
-
-An important subset of such set-valued maps are such that their realisations are polytopic, i.e.
-$f(y)$ is a polytope for all $y\in Y$, in particular we study maps which depend on the \emph{parameter} in a piecewise affine way.
-%
-The graph of such maps is given by a union of polytopes, they have been studied in~\cite{Finzel:2000}.
-%
-We will make statements about \emph{generic} such maps, that is properties which are structurally stable in the sense that if~$f(y)$ has a particular property than there exists an open neighbourhood $U\ni y$ such that $f(\tilde y)$ has the same property for all $\tilde y\in U$, furthermore the set of points for which the property does not hold is of measure zero.
-%
-In the course of this paper it will be self evident what the set of points is, where the property of interest fails, in particular a lower dimensional polyhedron and we therefore omit a measure theoretic treatment of our assumption.
-
-The particular property we require is \emph{simplicity}, for each $y\in Y$ the set $f(y)$ is a polytope and each of its vertices~$v(y)$ is supported by a minimal number of hyperplanes, i.e.
-there exists a linear system defining the set~$f(y) = \{z:A(y)z\leq b(y)\}$ and each vertex $v(y)$ is defined by $n$ hyperplanes $A_{\mathcal I}(y)v(y)=b_{\mathcal I}(y)$ and $A_{\bar{\mathcal I}}(y)v(y)<b_{\bar{\mathcal I}}(y)$.
-%
-It is easy to see, that if $A(\cdot)$ and $b(\cdot)$ are continuous in $y$, then $\mathcal I$ locally defines a vertex, i.e.
-the combinatorial structure of a simple polytope is structurally stable and therefore being simple is a generic property of a polytope.
-
-The induced graph~$G(P)$ of a polytope~$P$ is the graph with vertices and edges that coincide with the vertices and edges of the polytope itself~\cite{Bondy:2008}.
-%
-In this paper we only use one property of induced graphs, namely the \emph{Perles Conjecture}~\cite{Kalai:1988}:
+has a continuous boundary $\partial\mathscr G(f)$.
+%, so that for every point $(y,z)\in\partial\mathscr G(f)$ the boundary $\partial\mathscr G(f)$ is locally given by the graph of a continuous function.
+%
+We consider only set-valued maps with convex images, namely maps with the property that, for all $y\in Y$, we have $\lambda z_1+(1-\lambda)z_2\in f(y)$ for all $\lambda\in[0,1]$ if $z_1,z_2\in f(y)$.
+%
+An important class of set-valued maps are those with polyhedral realisations, so that $f(y)$ is a polyhedron for all $y\in Y$, and in particular we study polyhedral set-valued maps which depend on the \emph{parameter} $y$ in a piecewise affine way.
+%
+The graph of a  piecewise affine polyhedral set-valued map is given by a union of polyhedra~\cite{Finzel:2000}.
+
+\revision{In Sections~\ref{sec:polyhedral:maps} and~\ref{sec:computational:methods}
+of this paper we consider \emph{generic} polyhedral set-valued maps, which are defined as follows.}
+
+\begin{definition}[Generic polyhedral set-valued map]\label{def:generic_polyhedral_set}
+\revision{The polyhedral set-valued map $f(y)$ is said to be generic if $f(y)$ is a \emph{simple} polyhedron for all $y\in Y$ (except possibly on a subset of $Y$ of zero measure), and if $f(y)$ is \emph{structurally stable}.
+For given $y\in Y$, the polyhedral set $f(y) = \{z: a_i(y)z\leq b_i(y)\, \forall i\in \mathcal I\}\subset \mathbb R^n$ is simple if each of its vertices is supported by a minimal number of hyperplanes, i.e.~if for each vertex $v(y)$ there exists an index set $\mathcal A\subset \mathcal I$, with $\lvert \mathcal A\rvert = n$, such that $a_i(y)v(y)=b_i(y)$ for all $i\in\mathcal A$ and $a_i(y)v(y)<b_i(y)$ for all $i\in \mathcal I \setminus \mathcal A$.
+%
+Furthermore $f(y)$ is structurally stable if the combinatorial structure of $f(y)$ is unchanged when the functions $a_i(y)$, $b_i(y)$ are replaced by perturbed versions $a_i(y) + \epsilon u^{\!\top}$, $b_i(y)+\epsilon s$, for arbitrary $u\in B_1^n(0)$ and $s\in B_1^1(0)$,
+whenever $\epsilon> 0$ is sufficiently small.}
+\end{definition}
+
+% \revision{In Sections~\ref{sec:polyhedral:maps} and~\ref{sec:computational:methods}
+% of this paper we consider \emph{generic} polyhedral set-valued maps, by which we mean set-valued maps with the properties that $f(y)$ is a \emph{simple} polyhedron for all $y\in Y$ (except possibly on a subset of $Y$ of zero measure), and that $f(y)$ is \emph{structurally stable}.
+The polyhedral set $f(y) = \{z: a_i(y)z\leq b_i(y)\, \forall i\in \mathcal I\}\subset \mathbb R^n$ is simple if each of its vertices is supported by a minimal number of hyperplanes, i.e.~if for each vertex $v(y)$ there exists an index set $\mathcal A\subset \mathcal I$, with $\lvert \mathcal A\rvert = n$, such that $a_i(y)v(y)=b_i(y)$ for all $i\in\mathcal A$ and $a_i(y)v(y)<b_i(y)$ for all $i\in \mathcal I \setminus \mathcal A$.
+% %
+% Furthermore we say that $f(y)$ is structurally stable if the combinatorial structure of $f(y)$ does not vary as $y$ varies over the interior of $Y$.}
+
+%
+% We note that $f(y)$ is simple almost everywhere in $Y$ if and only if it has a fixed number of vertices and rays for all $y\in Y$ except possibly on a subset of $Y$ with measure zero (i.e.~ a lower-dimensional polyhedron).}
+%
+%in the sense that if $f(y)$ is simple, then there exists a neighbourhood, $U$, of $y$ such that $f(\tilde y)$ is simple for all $\tilde y\in U$, and furthermore any subset of $Y$ on which $f(y)$ is not simple must be of measure zero (i.e.~a lower-dimensional polyhedron).}
+
+% It is easy to see that if $A(\cdot)$ and $b(\cdot)$ are continuous in $y$, then $\mathcal I$ locally defines a vertex, i.e.
+the combinatorial structure of a simple polyhedron is structurally stable and therefore being simple is a generic property of a polyhedron.
+% zero measure.
+%
+%In our analysis it will be self-evident what the set of points is, where the property of interest fails, in particular a lower dimensional polyhedron and we therefore omit a measure theoretic treatment of our assumption.
+%
+% The particular property we require is \emph{simplicity}, namely that for each $y\in Y$ the set $f(y)$ is a polyhedron and each of its vertices~$v(y)$ is supported by a minimal number of hyperplanes, i.e.~there exists a linear system defining the set $f(y) = \{z:A(y)z\leq b(y)\}$ and each vertex $v(y)$ is defined by $n$ hyperplanes $A_{\mathcal I}(y)v(y)=b_{\mathcal I}(y)$ and $A_{\bar{\mathcal I}}(y)v(y)<b_{\bar{\mathcal I}}(y)$.
+% %
+% It is easy to see that if $A(\cdot)$ and $b(\cdot)$ are continuous in $y$, then $\mathcal I$ locally defines a vertex, i.e.
+the combinatorial structure of a simple polyhedron is structurally stable and therefore being simple is a generic property of a polyhedron.
+
+The induced graph~$G(P)$ of a polyhedron~$P$ is the graph with vertices and edges that coincide with the vertices and edges of the polyhedron itself~\cite{Bondy:2008}.
+%
+In this paper we only use one property of induced graphs, 
+\revision{namely the \emph{Perles Conjecture} proved in~\cite{blind87} and~\cite{Kalai:1988}, which can be stated as follows:}
 \emph{For a simple polytope~$P$ the graph~$G(P)$ determines the combinatorial structure of~$P$.}
@@
 
-In this section we define the property of \emph{parametric convexity} in the context of set-valued maps. 
-%
-This property is then used to demonstrate the convexity of a generalised Pontryagin difference operation (see e.g.~\cite{Hadwiger:1950,blanchini:2007}). 
+In this section we first define the property of \emph{parametric convexity} in the context of set-valued maps,
+%
+then we use this property to demonstrate the convexity of a generalised Pontryagin difference operation (see e.g.~\cite{Hadwiger:1950,blanchini:2007}). 
 %
@@
 %
-Notice that Definition~\ref{def:parametric:convexity} does not require convexity of~$\mathcal W(p)$. 
-%
-However, recall that we will only consider maps~$\mathcal W$ for which $\mathcal W(p)$ is convex for all fixed $p\in Y$.
-%
-A similar definition was given in~\cite{Hadwiger:1957} for scalar families of sets ($d=1$), however the results presented are not directly related.
+Although Definition~\ref{def:parametric:convexity} does not require convexity of~$\mathcal W(p)$, we only consider maps~$\mathcal W$ for which $\mathcal W(p)$ is convex for all fixed $p\in Y$ in the remainder of this paper.
+%
+\revision{We note that a similar definition is given in~\cite{Hadwiger:1957} for scalar families of sets ($d=1$), and set-valued maps satisfying~(\ref{eq:def:parametrically:convex}) are called \emph{concave} in~\cite{wasowicz16}, however in both cases the results presented are not directly related to the topic of this paper.}
 
@@
 \[
-  \revision{\mathcal N_{\mathcal W} (p,z) = \{\zeta \in\mathbb R^n: \zeta^T (y - z) \leq 0, \;  \forall y\in \mathcal W(p) \} .}
+  \revision{\mathcal N_{\mathcal W} (p,z) = \{v \in\mathbb R^n: v^\top (y - z) \leq 0, \;  \forall y\in \mathcal W(p) \} .}
 \]
@@
 %
-\revision{Note that the normal cone in Definition~\ref{def:graph:of:map} is defined in the space of the \emph{set variable} $z\in Y$ rather than \emph{graph variable} $(p,z)\in Y\times Z$.
-%
-Furthermore, the normal cone $\mathcal N_{\mathcal W} (p,z)$ is the set of normals to all hyperplanes that contain $z$ but no other points in $\mathcal W(p)$.}
+\revision{The normal cone $\mathcal N_{\mathcal W} (p,z)$  in  Definition~\ref{def:graph:of:map} belongs to the same space as $z$ rather than the space of the graph variable $(p,z)$; it consists of normals of hyperplanes in $\mathbb R^n$ that contain $z$ but no points in the interior of $\mathcal W(p)$.}
 %
@@
 %
-\begin{theorem}\label{thm:p:convexity:graph}
+\begin{lemma}\label{lem:p:convexity:graph}
   \revision{A set-valued map $\mathcal W$ satisfying $\mathcal W(p)\ni 0$ for all $p\in Y$
@@
 %
-\end{theorem}
-%
-\begin{proof}
-  %
-  \revision{Consider the set $S$, defined for given $\lambda\in (0,1)$ and $p_1,p_2\in Y$ by
+\end{lemma}
+%
+\begin{proof}\def\W{\mathcal{W}}\def\N{\mathcal{N}}
+% 
+  \revision{
+    Consider the set $S$, defined for given $\lambda\in (0,1)$ and $p_1,p_2\in Y$ by
     \[
@@
     \]
-  % \begin{align*}
-  %   S &= \lambda \mathcal{W}(p_1) \oplus (1-\lambda) \mathcal{W}(p_2) \\
-  %     &= \bigl\{ z : \lambda z_1 + (1 - \lambda) z_2, \ z_1 \in\mathcal W(p_1), \ z_2 \in\mathcal W(p_2) \bigr\} .
-  % \end{align*}
     We first show that $z\in \partial S = S \setminus \interior(S)$ if and only if
-  % \begin{equation}\label{eq:Scond}
-  %   z = \lambda z_1 + (1 - \lambda) z_2
-  %   \quad \text{and} \quad
-  %   \mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset 
+    $z = \lambda z_1 + (1 - \lambda) z_2$ for some $z_1\in\partial \mathcal W(p_1)$ and $z_2\in\partial \mathcal W(p_2)$ such that $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$.}
+
+  \revision{If $z\in\partial S$, then there must exist $\zeta\in\mathbb R^n$ such that $z + \epsilon \zeta \notin S$ for all $\epsilon > 0$, which implies that it is not possible to find $z_1^\prime\in \mathcal{W}(p_1)$ and $z_2^\prime\in \mathcal{W}(p_2)$ such that $z + \epsilon \zeta =  \lambda z_1^\prime + (1 - \lambda) z_2^\prime$ for all $\epsilon > 0$.
+Hence $z_1\in\partial\W(p_1)$ and $z_2\in\partial\W(p_2)$ are necessary conditions for $z\in\partial S$.}
+
+\revision{We therefore assume that $z = \lambda z_1 + (1-\lambda) z_2$ with $z_i\in\partial\W(p_i)$, $i=1,2$.
+Then $z+\zeta\in S$ if and only if there exists $\zeta_1$ or $\zeta_2$ such that $\zeta = \lambda\zeta_1$ or $(1-\lambda)\zeta_2$,  with $\zeta_i\in \N_\W^\ast(p_i, z_i)$, where $\N_\W^\ast(p_i, z_i)$ is the polar cone:
+\[
+% \zeta_i\in 
+\N_\W^\ast(p_i,z_i) = \bigl\{ \zeta : v_i^\top\zeta \leq 0 \ \ \forall v_i\in\N_\W(p_i,z_i) \bigr\} .
+\]
+Therefore $z+\zeta\in S$ if and only if
+$\zeta\in\N_\W^\ast(p_1,z_1)\cup \N_\W^\ast(p_2,z_2)$.
+% since if $\zeta \in \N_\W^\ast(p_i, z_i)$ for $i=1$ or $2$,
+% then $\zeta_1$ or $\zeta_2$ exists such that $\zeta = \lambda\zeta_1$ or $(1-\lambda)\zeta_2$, with $z_i+ \zeta_i\in\W(p_i)$ for $i=1$ or $2$.
+It follows that $v$ lies in the normal cone to $S$ at $z$ if and only if 
+\[
+v^\top \zeta \leq 0 \ \ \forall \zeta\in\N_\W^\ast(p_1,z_1) \cup \N_\W^\ast(p_2,z_2),
+\]
+or equivalently, if and only if, for all $\zeta_i\in\N_\W^\ast(p_1,z_i)$,
+%such that $v_i^T\zeta_i \leq 0$, $\forall v_i \in \N_W(p_i,z_i)$, 
+$i=1,2$, we have
+\begin{equation}\label{eq:normal_cone_cond}
+v^\top \bigl( \mu \zeta_1 + (1-\mu) \zeta_2 \bigr) \leq 0 \ \ \forall \mu\in [0, 1].
+\end{equation}
+  % \revision{Specifically, if $z\in \partial S$ then $z\in S$ and there exists $\zeta\in\mathbb R^n$ such that $z + \epsilon \zeta \notin S$ for all $\epsilon > 0$.
+  % %
+  % Therefore we must have $z = \lambda z_1 + (1-\lambda ) z_2$ for $z_1\in\partial \mathcal W(p_1)$ and $z_2\in\partial \mathcal W(p_2)$, and furthermore there exists $\nu\in \mathbb R^n$ such that for all $\mu \in [0,1]$ we have
+  % \begin{equation}\label{eq:normal_cone_cond}
+  %   \nu^T \bigl( \mu \zeta_1 + (1-\mu) \zeta_2 \bigr) \leq 0 
   % \end{equation}
-  $z = \lambda z_1 + (1 - \lambda) z_2$ for some $z_1\in\partial \mathcal W(p_1)$ and $z_2\in\partial \mathcal W(p_2)$ such that $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$.}
-
-  \revision{Specifically, if $z\in \partial S$ then $z\in S$ and there exists $\zeta\in\mathbb R^n$ such that $z + \epsilon \zeta \notin S$ for all $\epsilon > 0$.
-  %
-  From this it follows that $z = \lambda z_1 + (1-\lambda ) z_2$ for $z_1\in\partial \mathcal W(p_1)$ and $z_2\in\partial \mathcal W(p_2)$ and there exists $\nu\in \mathbb R^n$ such that for all $\mu \in [0,1]$ we have
-  \begin{equation}\label{eq:normal_cone_cond}
-    \nu^T \bigl( \mu \zeta_1 + (1-\mu) \zeta_2 \bigr) \leq 0 
-  \end{equation}
-  for all $\zeta_1$ and $\zeta_2$ such that $\nu_1^T\zeta_1 \leq 0$ and $\nu_2^T\zeta_2 \leq 0$ for all $\nu_1\in\mathcal N_{\mathcal W}(p_1)$ and $\nu_2\in\mathcal N_{\mathcal W}(p_2)$.
+  % for all $\zeta_1$ and $\zeta_2$ such that $\nu_1^T\zeta_1 \leq 0$ and $\nu_2^T\zeta_2 \leq 0$ for all $\nu_1\in\mathcal N_{\mathcal W}(p_1,z_1)$ and $\nu_2\in\mathcal N_{\mathcal W}(p_2,z_2)$.
 Note that these conditions are equivalent to the requirement that the normal cone to $S$ at $z$ is non-empty.}
-
-\revision{Clearly we must have $\nu\in \mathcal N_{\mathcal W}(p_1)$ (since $\mu = 1$ in (\ref{eq:normal_cone_cond}) gives $\nu^T\zeta_1 \leq 0$) and similarly $\nu\in \mathcal N_{\mathcal W}(p_2)$ (since $\mu = 0$ in (\ref{eq:normal_cone_cond}) gives $\nu^T\zeta_2 \leq 0$), and hence $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$ is necessary for $z\in\partial S$.
-  %
-  Furthermore $\nu\in \mathcal N_{\mathcal W}(p_1)\cap \mathcal N_{\mathcal W}(p_2)$ is also sufficient to ensure (\ref{eq:normal_cone_cond}) for all $\mu\in[0,1]$, and hence also sufficient for $z\in\partial S$.}
-  %
-
-  \revision{If $\lambda z_1 + (1-\lambda ) z_2 \in\partial S$, then (\ref{eq:graph:def:p:convexity}) is equivalent to $\mathcal W\bigl(\lambda p_1 + (1-\lambda) p_2 \bigr) \subseteq S$, and the proof is therefore completed by applying the preceding argument for all $(p_1,z_1) \in\partial\mathscr G(\mathcal W)$ and $(p_2,z_2)\in\partial\mathscr G(\mathcal W)$, and all $\lambda\in (0,1)$.}
+Clearly $v$ must lie in $\mathcal N_{\mathcal W}(p_1,z_1)$ (since $\mu = 1$ in (\ref{eq:normal_cone_cond}) gives $v^\top\zeta_1 \leq 0$) and similarly $v\in \mathcal N_{\mathcal W}(p_2,z_1)$ (since $\mu = 0$ in (\ref{eq:normal_cone_cond}) gives $v^\top\zeta_2 \leq 0$), and hence $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$ is necessary for $z\in\partial S$.
+  %
+  Furthermore $v\in \mathcal N_{\mathcal W}(p_1,z_1)\cap \mathcal N_{\mathcal W}(p_2,z_2)$ is also sufficient to ensure (\ref{eq:normal_cone_cond}) for all $\mu\in[0,1]$, and hence also sufficient for $z\in\partial S$.}
+  %
+
+  \revision{Given that $0\in\W(p)$ for all $p\in Y$, we must have $0\in\W\bigl(\lambda p_1 + (1-\lambda)p_2\bigr)$ and $0\in S$.
+Therefore condition (\ref{eq:graph:def:p:convexity}), when invoked for all $z\in\partial S$, is equivalent to  $\mathcal W\bigl(\lambda p_1 + (1-\lambda) p_2 \bigr) \subseteq S$.
+The proof is completed by applying the preceding argument for all $p_1,p_2\in Y$ and all $\lambda\in (0,1)$.}
 \qed
+% If $\lambda z_1 + (1-\lambda ) z_2 \in\partial S$, then (\ref{eq:graph:def:p:convexity}) is equivalent to $\mathcal W\bigl(\lambda p_1 + (1-\lambda) p_2 \bigr) \subseteq S$, and the proof is therefore completed by applying the preceding argument for all $(p_1,z_1) \in\partial\mathscr G(\mathcal W)$ and $(p_2,z_2)\in\partial\mathscr G(\mathcal W)$, and all $\lambda\in (0,1)$.
+%   \qed
 % %
@@
 
-Condition~\eqref{eq:graph:def:p:convexity} requires that the graph $\mathscr G(\mathcal W)$ is non-convex.
+\revision{%
+Condition~\eqref{eq:graph:def:p:convexity} fails whenever the graph $\mathscr G(\mathcal W)$ is strictly convex.}
 %
@@
 %
-\begin{corollary}\label{thm:inequalities:convex:concave}
+\begin{theorem}\label{thm:inequalities:convex:concave}
 %
@@
 then $\mathcal W$ is parametrically
-convex iff the function $r$ is concave in $p\in\mathbb R^d$.
-%
-\end{corollary}
+convex if and only if the function $r$ is concave in $p\in\mathbb R^d$.
+%
+\end{theorem}
 %
@@
 $\lambda (p_1,z_1) + (1-\lambda) (p_2,z_2) \in\interior (\mathscr G(\mathcal W))\vert_{\mathcal C}$ for all $\lambda\in(0,1)$ since
-$\mathscr G(\mathcal W)\vert_{\mathcal C}$ is strictly convex in $p$.
+$\mathscr G(\mathcal W)\vert_{\mathcal C}$ is assumed to be strictly convex in $p$.
 %
@@
 %
-Conversely, if $r(p,z)$ is concave in $p$ for all $p\in\mathbb R^d$, then the conditions of Theorem~\ref{thm:p:convexity:graph} necessarily hold.
+Conversely, if $r(p,z)$ is concave in $p$ for all $p\in\mathbb R^d$, then the conditions of Lemma~\ref{lem:p:convexity:graph} necessarily hold.
 \qed
@@
 %
-Later we will show that the parametric Pontryagin difference between a polyhedral set and a piecewise polytopic set-valued map is itself polyhedral.
+In Section~\ref{sec:computational:methods}
+we show that the parametric Pontryagin difference between a polyhedral set and a piecewise affine polyhedral set-valued map is itself polyhedral.
 %
@@
 %
-In this section we discuss set-valued maps~$\mathcal W$ for which every realisation~$\mathcal W(p)$ is polyhedral and in particular we study~$\mathcal W$ which depend on $p\in Y$ in a piecewise affine way.
-%
-To the authors' best knowledge the literature on piecewise polyhedral sets is limited to~\cite{Finzel:2000}, however properties of general set-valued maps are known and applicable, see e.g.~\cite{Aubin:2009}.
-%
+In this section we discuss set-valued maps~$\mathcal W$ for which~$\mathcal W(p)$ is polyhedral for all $p\in Y$, and in particular we consider the case that the dependence of $\mathcal W(p)$ on $p$ is piecewise affine.
+%
+To the authors' knowledge the literature on piecewise affine polyhedral sets is limited to~\cite{Finzel:2000}, however properties of general set-valued maps are known and applicable, see e.g.~\cite{Aubin:2009}.
+%
+
 \begin{remark}
-%
-Notice that the boundary of a polytope is almost everywhere locally convex (i.e. concave but not strictly concave) and locally strictly convex around lower dimensional faces (vertices, edges, etc.).
+We note that the boundary of a polyhedral set is almost everywhere locally convex (i.e.
+concave but not strictly concave) and locally strictly convex around lower dimensional faces (vertices, edges, etc.).
 %
@@
 %
-As long as the boundary $\partial\mathscr G(\mathcal W)$ is locally affine in $p\in Y$, Corollary~\ref{thm:inequalities:convex:concave} applies. 
-%
-Conversely if the boundary $\partial\mathscr G(\mathcal W)$ is locally given by more than one affine function in $p\in Y$ (determined by linear inequalities), then it is locally strictly convex and can therefore not be parametrically convex.
+As long as the boundary $\partial\mathscr G(\mathcal W)$ is locally affine in $p\in Y$, Theorem~\ref{thm:inequalities:convex:concave} applies. 
+%
+Conversely if the boundary $\partial\mathscr G(\mathcal W)$ is locally given by more than one affine function in $p$ (determined by linear inequalities), then it is locally strictly convex and therefore cannot be parametrically convex.
 \end{remark}
 %
-\begin{corollary}\label{thm:polytopic:set:not:p:convex}
-  \revision{The polytopic parametric set-valued map $\mathcal W(p):=\{z: a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\}$
-    is  parametrically convex if and only if the matrix $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$ is such that $\rank(B) \leq 1$.}
+\begin{theorem}\label{thm:polytopic:set:not:p:convex}
+  \revision{The polyhedral parametric set-valued map $\mathcal W(p):=\{z\in \mathbb R^n : a_i z \leq b_i  + c_i p \; \forall i\in\mathbb N_m\}$, where $a_i\in\mathbb R^{1\times n}$, $b_i \in \mathbb R$ and $c_i \in \mathbb R^{1\times d}$ for $i\in\mathbb N_m$ are given parameters, is necessarily parametrically convex if $C=0$ and cannot be parametrically convex if $\rank( C ) > 1$, where $C = (\begin{matrix} c_1^\top & \cdots & c_m^\top\end{matrix})^\top$.}
+% and only if the matrix $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$ is such that $\rank(B) \leq 1$.}
 %is not parametrically convex for any $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$ such that $\rank (B) >1$.}
-\end{corollary}
+\end{theorem}
 %
 \begin{proof}
-\revision{First assume that $B=0$. In this case the graph $\mathscr G(\mathcal W)$ is constant for all $p$, i.e.
+\revision{First assume that $C=0$. In this case the graph $\mathscr G(\mathcal W)$ is independent of $p$, i.e.
 %
 \begin{equation*}
-	\mathscr G(\mathcal W) = \{(p,z):a_i z\leq c_i \; \forall i\in\mathbb N_m\},
+	\mathscr G(\mathcal W) = \{(p,z):a_i z\leq b_i \; \forall i\in\mathbb N_m\},
 \end{equation*}
 %
-which clearly satisfies the  conditions of Theorem~\ref{thm:p:convexity:graph} for parametric convexity.
-%
-Next assume $\rank(B)=1$.
-This implies that the image,  $\image(B)$, of $B$ is one dimensional and in particular there exists $\gamma\in\mathbb{R}^m$ such that $\image(B) = \{\gamma t: t\in\mathbb R\}$.
-%
-This implies that the graph $\mathscr G(\mathcal W)$ can be expressed 
-%
+which clearly satisfies the  conditions of Theorem~\ref{thm:inequalities:convex:concave}
+%Lemma~\ref{lem:p:convexity:graph} 
+for parametric convexity.
+%
+% Next assume $\rank(B)=1$.
+This implies that the image,  $\image(B)$, of $B$ is one-dimensional and in particular there exists $\gamma\in\mathbb{R}^m$ such that $\image(B) = \{\gamma t: t\in\mathbb R\}$.
+% %
+% This implies that the graph $\mathscr G(\mathcal W)$ can be expressed 
+% %
+% \begin{equation*}
+%   \mathscr G(\mathcal W) = \{(t,z)\in\mathbb R^{1+n}:a_i z\leq c_i-\gamma_i t \; \forall i\in\mathbb N_m\} ,
+% \end{equation*}
+% %
+% where $\mathcal W(t)$ is empty for all $t > t^\ast$ for some $t^\ast$, and $\mathcal W(t)$ is a scaled version of $\{ z : a_i z\leq c_i \; \forall i\in\mathbb{N}_m\}$ for all $t \leq t^\ast$.
+% Hence the conditions of Theorem~\ref{thm:inequalities:convex:concave}
+% %Lemma~\ref{lem:p:convexity:graph} 
+% are again satisfied.}
+% %
+%
+Now assume that $\text{rank}(C)=r> 1$. In this case $\image(C) = \{\Gamma t : t \in \mathbb R^r\}$ for  some $\Gamma \in\mathbb{R}^{m\times r}$,
+  %
+  and $\mathscr{G}(\mathcal W)$ can be expressed
+  % 
+% \begin{equation*}
+%   \mathscr G(\mathcal W) = \Bigl\{(t,z)\in\mathbb R^{r+n}: \begin{pmatrix} a_{\mathbb N_m} & -\Gamma \end{pmatrix}  \begin{pmatrix} z \\ t \end{pmatrix} \leq b_{\mathbb N_m} \Bigr\} \end{equation*}
 \begin{equation*}
-  \mathscr G(\mathcal W) = \{(t,z)\in\mathbb R^{1+n}:a_i z\leq c_i-\gamma_i t \; \forall i\in\mathbb N_m\} ,
+  \mathscr G(\mathcal W) = \Bigl\{(p,z) : a_i z \leq b_i + \sum_{j=1}^r \gamma_{i,j} t_j \; \forall i\in\mathbb N_m,\; t =\Gamma^\dagger Cp \Bigr\},
 \end{equation*}
 %
-where $\mathcal W(t)$ is empty for all $t > t^\ast$ for some $t^\ast$ and $\mathcal W(t)$ is a scaled version of $\{ z : Az\leq c\}$ for all $t \leq t^\ast$.
-Hence the conditions of Theorem~\ref{thm:p:convexity:graph} are again satisfied.}
-%
-
-\revision{Now assume that $\text{rank}(B)=r \geq 1$. In this case
-%  $\image(B) = \{\gamma_1t_1+\cdots +\gamma_rt_r : t_1,\ldots,t_r \in \mathbb R\}$ for  some $\gamma_1, \ldots \gamma_r\in\mathbb{R}^m$.
-  $\image(B) = \{\Gamma t : t \in \mathbb R^r\}$ for  some $\Gamma \in\mathbb{R}^{m\times r}$,
-  %
-  and $\mathscr{G}(\mathcal W)$ can be expressed
-  % 
-\begin{equation*}
-  \mathscr G(\mathcal W) = \Bigl\{(t,z)\in\mathbb R^{r+n}:a_i z\leq c_i-\sum_{j=1}^r \gamma_{i,j} t_j \; \forall i\in\mathbb N_m\Bigr\},
-\end{equation*}
-%
-where $\gamma_{i,j}$ is the $(i,j)$th element of $\Gamma$.
-%
-Whenever $\text{rank}(B)\geq 2$ therefore, the graph $\mathscr G(\mathcal W)$ is given by a convex polyhedron that has vertices in the parameter space, which implies that the graph is locally strictly convex and $\mathcal W(p)$ therefore violates Theorem~\ref{thm:p:convexity:graph}.}
+where $\gamma_{i,j}$ is the $(i,j)$th element of $\Gamma$ and $\Gamma^\dagger = (\Gamma^\top\Gamma)^{-1}\Gamma^\top$.
+%
+But this implies that the graph $\mathscr G(\mathcal W)$ is locally strictly convex, and hence $\mathcal W(p)$ violates the conditions of Theorem~\ref{thm:inequalities:convex:concave} in this case.}
+ % given by a convex polyhedron that has vertices in the parameter space, which implies that the graph is locally strictly convex and $\mathcal W(p)$ therefore violates Lemma~\ref{lem:p:convexity:graph}.}
 \qed
@@
 %
-We now present the central theorem of this work, which holds for piecewise affine polytopic set-valued maps which are generic, which implies two things, their realisation is simple and further no more than one structural component changes at a time.
-%
-The second assumption will become clearer in the proof of the central statement for piecewise affine polytopic set-valued maps and makes the statement of Theorem~\ref{thm:p:convexity:graph} more specific.
-%
-\begin{corollary}\label{thm:p:convexity:PWA:set:constant:num:verts}
-The generic piecewise affine polytopic parametric set-valued valued map 
-%
+
+\revision{In the special case of $\rank(C)=1$, the map $\mathcal W(p)=\{ z : a_i z \leq b_i + c_i p \; \forall i \in \mathbb N_m\}$ considered in Theorem~\ref{thm:polytopic:set:not:p:convex} may or may not be parametrically convex.
+For example, if $\image(C) = \{ \Gamma t : t\in\mathbb R\}$, with $\Gamma = (\begin{matrix} b_1 & \cdots & b_m\end{matrix})^\top$, then $\mathscr G(\mathcal W)$ is a translated polyhedral cone,
+\[
+\mathscr G(\mathcal W) = \{ (p , z) : a_i z \leq b_i t \; \forall i\in\mathbb N_m, \; t = \Gamma^\dagger C p + 1\} ,
+\]
+(where $\Gamma^\dagger = \Gamma^\top/(\Gamma^\top\Gamma)$),
+which necessarily satisfies the conditions of Theorem~\ref{thm:inequalities:convex:concave}.
+On the other hand, if $\Gamma = (\begin{matrix} 0 & \cdots & 0 & b_m\end{matrix})^\top$, then $\mathscr G(\mathcal W)$ can be expressed
+\begin{equation}\label{eq:graph:non-generic:1-d}
+\mathscr G(\mathcal W) = \{ (p ,z): a_i z \leq b_i  \; \forall i\in\mathbb N_{m-1}, \; a_m z \leq b_m t ,\; t = \Gamma^\dagger C p + 1\} 
+\end{equation}
+(where $\Gamma^\dagger = (\begin{matrix} 0 & \cdots & 0 & b_m^{-1}\end{matrix})$).
+In this case $\mathcal W(p)$ cannot be parametrically convex whenever the set $\{ z\in\mathbb R^n : a_iz \leq b_i \; \forall i\in\mathbb N_{m-1}\}$ is compact, since $\mathscr G(\mathcal W)$ is then locally strictly convex.
+The case of $\rank(C)=1$ is a special case of Theorem~\ref{thm:p:convexity:PWA:set:constant:num:verts}, which is given next.
+In fact this example provides a useful insight into Theorem~\ref{thm:p:convexity:PWA:set:constant:num:verts}, since if $a_i\neq a_j$ for all $i,j\in\mathbb N_m$, then by inspection of (\ref{eq:graph:non-generic:1-d}) it can be seen that
+%$\mathcal W(p)$ is non-generic, in the sense that 
+the number of vertices of $\mathcal W(p)$ varies with $p$.
+A key contribution of Theorem~\ref{thm:p:convexity:PWA:set:constant:num:verts} (which is stated in terms of piecewise affine set-valued maps, so $a_i\neq a_j$ for all $i,j\in\mathbb N_m$ can be assumed without loss of generality) is that $\mathcal W(p)$ is parametrically convex in this special case if and only if the number of vertices of $\mathcal W(p)$ is fixed for all $p\in Y$ (with the possible exception of a zero measure subset of $Y$).}
+
+\revision{Theorem~\ref{thm:p:convexity:PWA:set:constant:num:verts} applies to piecewise affine polyhedral set-valued maps defined by
 \begin{equation}\label{eq:definition:PWA:polytopic:set:general}
-  \mathcal W(p) := \Bigl\{z\in\mathbb R^n: a_i z \leq \max_{k}\{b_{i,k} + c_{i,k}p\} \; \forall i\in\mathbb N_m \Bigr\}
-\end{equation}
-%
-is parametrically convex iff the number of vertices, $v_\kappa(p)$, and rays, $r_\eta(p)$, of~$\mathcal W(p)$ is constant for almost all $p\in Y$.
-\end{corollary}
-%
-\begin{proof}
-For clarity this proof is divided into three parts:
-\begin{enumerate}
-\item Note that $h_i(p) = \max_{k} \{b_{i,k} + c_{i,k}p\}$ is a multi-parametric linear program (mpLP),
-the solution of which is a piecewise affine function $h_i(p) = b_{i,k^\ast_i} + c_{i,k^\ast_i}p$, where $k^\ast_i(p)$ is piecewise constant on a polyhedral complex, see e.g.~\cite{spjotvold:2005}.
-%
-This means that there exists a finite partition of $Y\subseteq\mathbb R^d$ into convex polyhedra 
+  \mathcal W(p) := \Bigl\{z\in\mathbb R^n: a_i z \leq \max_{k\in\mathbb N_q}\{b_{i,k} + c_{i,k}p\} \; \forall i\in\mathbb N_m \Bigr\} 
+\end{equation}
+where $a_i\in\mathbb R^{1\times n}$, $b_{i,k} \in \mathbb R$ and $c_{i,k} \in \mathbb R^{1\times d}$ for $i\in\mathbb N_m$ and $k\in\mathbb N_q$ are given parameters.
+Here the right hand side of each inequality defining $\mathcal W(p)$ is a multi-parametric linear program (mpLP):  $\phi_i(p) = \max_{k\in\mathbb N_q} \{b_{i,k} + c_{i,k}p\}$,
+the solution of which is a continuous piecewise affine function, $\phi_i(p) = b_{i,k^\ast_i} + c_{i,k^\ast_i}p$, where $k^\ast_i(p)$ is piecewise constant on a polyhedral complex, see e.g.~\cite{spjotvold07}.
+%
+This means that there exists a finite partition of $Y\subseteq\mathbb R^d$ into closed convex polyhedra 
 $\mathcal P_j$ such that $\bigcup_{j\in\mathcal I} \mathcal P_j = Y$ and 
@@
 \begin{equation*}
-  \mathscr G(\mathcal W) = \bigcup_{j\in\mathcal I} \left\{z: a_i z \leq b_{i,k_i^\ast} + c_{i,k_i^\ast}p \; \forall i \in\mathbb N_m \right\}\bigr\vert_{\mathcal P_{j}}
+  \mathscr G(\mathcal W) = \bigcup_{j\in\mathcal I} \left\{(p,z): a_i z \leq b_{i,k_i^\ast} + c_{i,k_i^\ast}p \; \forall i \in\mathbb N_m \right\}\bigr\vert_{\mathcal P_{j}} .
 \end{equation*}
-%
-and it follows that if the number of vertices or rays changes within any partition $\mathcal P_j$ then $\mathscr
-G(\mathcal W)\vert_{\mathcal P_j}$ is a strictly convex polyhedron and Corollary~\ref{thm:polytopic:set:not:p:convex} applies.
-%
-\item Our attention is therefore concentrated on the boundaries of partitions $\mathcal P_j$, at points $p\in\mathcal P_{j_1} \cap \mathcal P_{j_2}$ where 
-%some mpLP changes its solution, i.e. 
-$\bigl(b_{i,k_i^\ast} + c_{i,k_{j_1}^\ast} p\bigr)\bigr\rvert_{\mathcal P_{j_1}} = 
-\bigl(b_{i,k_{j_2}^\ast} + c_{i,k_{j_2}^\ast} p\bigr)\bigr\rvert_{\mathcal P_{j_2}}$.
-%
-Notice that a vertex $v_\kappa(p)$ is defined by \emph{active} and \emph{inactive} inequalities, namely $\mathcal A_\kappa(p)$ and
-$\bar{\mathcal A}_\kappa(p)$ respectively, where
-%
-\begin{equation*}\begin{split}
-  a_i v_\kappa(p) &= b_{i,k_i^\ast} + c_{i,k_i^\ast} p \quad\forall i\in\mathcal A_\kappa(p)\\
-  a_i v_\kappa(p) &< b_{i,k_i^\ast} + c_{i,k_i^\ast} p \quad\forall i\in\bar{\mathcal A}_\kappa(p) .
-\end{split}\end{equation*}
-%
-Since $\mathcal W(p)$ is simple almost everywhere in~$Y$, i.e. each vertex is defined by exactly $n$ active inequalities, we have $\abs{\mathcal A_\kappa(p)}=n$ for all $p\in Y$ and all $\kappa$.
-%
-Furthermore, since~$\mathcal W(p)$ is generic, only one element of ${\bf{k}}^\ast\vert_{\mathcal P_{j_1}}$
-and ${\bf{k}}^\ast\vert_{\mathcal P_{j_2}}$ for neighbouring $\mathcal P_{j_1}$ and $\mathcal P_{j_2}$ differs, that is, there exists a single index $i\in\mathbb N_m$ such that $k_i^\ast\vert_{\mathcal P_{j_1}}\neq k_i^\ast\vert_{\mathcal P_{j_2}}$.
-%
-Hence, in order for the number of vertices to change, there must be a hyperplane $fp=g$, such that the number of vertices for $fp \leq g$ is 
-$N$ and for $fp>g$ is at least $N+1$.
-%
-It follows from the previous discussion that $\{p:fp=g\} = \textup{aff}\{\mathcal P_{j_1}\cap\mathcal P_{j_2}\}$ for some $j_1\neq j_2$.
-%
-In order for vertices $v_{\kappa_1}(p)$ and $v_{\kappa_2}(p)$ to merge, the index sets $\mathcal A_{\kappa_1}(p)$ and $\mathcal A_{\kappa_2}(p)$ have to differ by only one 
-element, i.e.~$\mathcal A_{\kappa_1}(p) = \mathcal J\cup \{s\}$ and $\mathcal A_{\kappa_2}(p) = \mathcal J\cup\{u\}$ if $fp>g$.
-%
-Furthermore, for $p$ such that $fp\leq g$ we have $v_{\kappa_1}(p)=v_{\kappa_2}(p)$, implying that $\mathcal A_{\kappa_1}(p) = 
-\mathcal A_{\kappa_2}(p)$.
-%
-Since only one change in the active index set is considered (due to non-degeneracy assumptions), we must have
-$\mathcal A_{\kappa_1}(p) = \mathcal A_{\kappa_2}(p) = \mathcal J \cup \{s,u\}$.
-%
-Hence on the hyperplane $fp=g$, both the maximising index ${\bf{k}}^\ast(p)$ and the active index sets $\mathcal A_{\kappa_1}(p)$ 
-and $\mathcal A_{\kappa_2}(p)$ must change, which implies that this problem is degenerate.
-%
-\item In order for a degenerate graph $\mathscr G(\mathcal W)$ to be parametrically convex, the vertices $v_{\kappa_1}(p)$ and $v_{\kappa_2}(p)$ must be identical for $fp\leq g$, and in particular their dependence on $p$ has to be identical.
-%
-This can be expressed using the implicit function theorem as follows
-%
+A linear inequality defining $\mathcal W(p)$ is \emph{active} at $(p,z)\in\partial\mathscr G (\mathcal W)$ if it holds with equality, and \emph{inactive} if it holds with strict inequality.
+We denote the set of active constraints at any point $(p,z)\in\partial\mathscr G (\mathcal W)$ as the index set $\mathcal A (p,z)$ defined by
 \begin{align*}
-  \frac{d}{dp}\left(  a_{\mathcal J\cup \{s\}} v_{\kappa_1}(p) - b_{\mathcal J\cup \{s\}} - 
-  c_{\mathcal J\cup \{s\},{\bf{k}}^\ast} p\right) &= 0\\
-  \frac{d}{dp}\left(  a_{\mathcal J\cup \{u\}} v_{\kappa_2}(p) - b_{\mathcal J\cup \{u\}} - 
-  c_{\mathcal J\cup \{u\},{\bf{k}}^\ast} p\right) &= 0
+&a_i z = b_{i,k_i^\ast} + c_{i,k_i^\ast} p \quad\forall i \in \mathcal A (p,z) \\
+&a_i z < b_{i,k_i^\ast} + c_{i,k_i^\ast} p \quad \forall i \in \mathbb N_m \setminus \mathcal A (p,z) .
 \end{align*}
-%
-which implies
-\begin{align*}
-  a_{\mathcal J\cup \{s\}} \frac{dv_{\kappa}}{dp} &= c_{\mathcal J\cup \{s\},{\bf{k}}^\ast}\\
-  a_{\mathcal J\cup \{u\}} \frac{dv_{\kappa}}{dp} &= c_{\mathcal J\cup \{u\},{\bf{k}}^\ast}
-\end{align*}
-%
-and since we can assume that the inequalities are non-redundant for some right hand side, we find that 
-%
-\begin{equation}\label{eq:derivative:condition:on:index:sets}
-  \frac{dv_\kappa}{dp} = a_{\mathcal J\cup \{s\}}^{-1}c_{\mathcal J\cup \{s\},{\bf{k}}^\ast} = 
-  a_{\mathcal J\cup \{u\}}^{-1}c_{\mathcal J\cup \{u\},{\bf{k}}^\ast}
-\end{equation}
-%
-has to hold for the degenerate graph to remain parametrically convex.
-%
-To complete the proof we note that~\eqref{eq:derivative:condition:on:index:sets} is a degenerate condition, in the sense that an arbitrarily small perturbation will result in $v_{\kappa_1}(p) \neq v_{\kappa_2}(p)$, and we therefore disregard this possibility.
-\qed
-\end{enumerate}
-\end{proof}
-%
-It is worth pointing out that Corollary~\ref{thm:p:convexity:PWA:set:constant:num:verts} can be reformulated in a numerically useful way:
-%
-\begin{corollary}\label{thm:combinatorical:equivalence:alternative}
-The generic set~$\mathcal W(p)$ defined by~\eqref{eq:definition:PWA:polytopic:set:general} is parametrically convex if and only if it is combinatorially equivalent for any $p_1,p_2\in Y\subseteq\mathbb R^d$ almost everywhere, i.e.\ $\mathcal W(p_1)\cong\mathcal W(p_2)$.
-\end{corollary}
-%
+Before stating Theorem~\ref{thm:p:convexity:PWA:set:constant:num:verts} we first give two intermediate results.}
+
+%Finally we note that any zero measure subset of $Y\subseteq\mathbb R^d$ referred to in the following statements about piecewise affine polyhedral maps necessarily has the form of a polyhedral set of dimension less than $d$.}
+
+%In the following statements we use the terminology \emph{almost everywhere} in $Y$ to indicate all points in $Y$ except a subset of $Y$ of zero measure, namely a lower-dimensional polyhedral subset of $Y$.}
+
+%Theorem~\ref{thm:p:convexity:PWA:set:constant:num:verts} is stated in terms of generic piecewise affine polyhedral maps, which implies that their realisation is simple and no more than one structural component can change at a time as $p$ varies.
+
+%
+%The second assumption will become clearer in the proof of the central statement for piecewise affine polytopic set-valued maps and makes the statement of Lemma~\ref{lem:p:convexity:graph} more specific.
+%
+
+% \begin{lemma}\label{lem:sep_hyperplane}
+% \revision{Let the affine polyhedral map (\ref{eq:definition:PWA:polytopic:set:general}) be such that $\lvert \vertices\bigl(\mathcal W(p)\bigr) \rvert = \nu$ for all $p\in Y$ except a zero measure subset of $Y$.
+Then
+
+% for any $(p_i,z_i)\in \partial \mathscr G (\mathcal W)$, $i=1,2$ we have $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$ if and only if $\mathcal A(p_1,z_1) \cap \mathcal A(p_2,z_2)\neq \emptyset$.}
+
+\begin{lemma}\label{lem:active_set}
+\revision{For a given integer $\nu$, let the piecewise affine polyhedral set-valued map (\ref{eq:definition:PWA:polytopic:set:general}) satisfy $\lvert \vertices (\mathcal W(p) ) \rvert = \nu$ for all $p\in Y$ except a zero measure subset of $Y$.
+Then, for any $(p_1,z_1)\in \partial \mathscr G (\mathcal W)$ and $(p_2,z_2)\in \partial \mathscr G (\mathcal W)$, we have $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$ if and only if $\mathcal A(p_1,z_1) \cap \mathcal A(p_2,z_2)\neq \emptyset$.}
+\end{lemma}
+
 \begin{proof}
-Two polyhedra are combinatorially equivalent if there exists a bijection between all their faces which preserves the inclusion, see e.g.~\cite{Ziegler:1995}.
-%
-It is clear that as long as all complexes in proof~\ref{thm:p:convexity:PWA:set:constant:num:verts}, $\mathcal A_\kappa(p)=\mathcal A_\kappa$ are constant, all faces of $\mathcal W(p)$ are defined as intersections of the same set of half spaces.
-%
-Although the shape of~$\mathcal W(p)$ might change its, combinatorial structure does not, furthermore the combinatorial structure of $\mathcal W(p)$ is not affected by changes of the right hand side.
-%
-The Perles Conjecture~\cite{Kalai:1988} states that the combinatorial structure of a simple polytope is uniquely determined by its graph, that is, as long as the induced graph of~$\mathcal W(p)$ remains unchanged so does its combinatorial structure.
-%
-The induced graph of a polytope is given by the vertices and the edges of a polytope, and since we have that the number of vertices remains unchanged throughout~$Y$ for $\mathcal W(p)$, the induced graph $G(\mathcal W(p))$ has to have a constant number of vertices.
-%
-This is only possible if it is constant itself or it abruptly changes multiple edges, however changing multiple edges involves changing multiple active sets which is a degenerate case.
-%
-Notice that this result only applies to sets with full measure, where $\mathcal W(p)$ is non-degenerate.
-%
-It is possible that there exist zero-measure sets (points, lines, $d-1$-hyperplanes) in~$Y$ where $\mathcal W$ becomes singular, meaning not simple
-and vertices may merge, however due to the fact that for parameters outside such sets the combinatorial structure is fixed, we can find a  continuous selection through these sets, in any sense we like.
-%
-This means in particular that we ignore the fact that locally $v_{\kappa_1}=v_{\kappa_2}$ and can
- use a locally redundant representation $\mathcal W(p) = \conv_\kappa\{v_\kappa(p)\}$.
+\revision{
+The definition of the active set $\mathcal A(p,z)$ implies that the normal cone at $(p,z)\in \partial \mathscr G (\mathcal W)$ is given by 
+\begin{equation}\label{eq:normal_cone_face_normals}
+\mathcal N_{\mathcal W}(p,z) = \sum_{i\in\mathcal A(p,z)} \lambda_i a_i, \quad \lambda_i \geq 0 \ \ \forall i\in\mathcal A(p,z) ,
+\end{equation}
+and it follows immediately that $\mathcal A(p_1,z_1) \cap \mathcal A(p_2,z_2)\neq \emptyset$ is a sufficient condition for $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$, for any $(p_i,z_i)\in \partial \mathscr G (\mathcal W)$, $i=1,2$.
+%
+We show next that this condition is also necessary for $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$.
+%
+Specifically, if the number of vertices of $\mathcal W(p)$ is fixed for all $y\in Y$, then for each $i\in\mathcal A(p_1,z_1)$: (i) there must exist $z\in\mathcal W(p_2)$ such that $i\in\mathcal A(p_2,z)$; and (ii) if $i\not\in\mathcal A(p_2,z_2)$, then there must exist $u\in\mathbb R^n$ such that
+\begin{equation}\label{eq:separating_hyperplane}
+a_i u \geq 0 \quad \text{and} \quad a_j u < 0 \ \ \forall j\in \mathcal A(p_2,z_2).
+\end{equation}
+Note that properties (i) and (ii) also hold if $\lvert\vertices(\mathcal W(p))\rvert$ is fixed for all $p\in Y$ except a zero measure subset of $Y$ since the right hand side of each inequality defining $\mathcal W(p)$ is continuous in $p$.
+% Specifically, the assumption that the number of vertices of $\mathcal W(p)$ is fixed for all $p\in Y$ except possibly a zero-measure subset of $Y$ implies that for each $i\in\mathcal A(p_1,z_1)$ there must exist $z\in\mathcal W(p_2)$ such that $i\in\mathcal A(p_2,z)$, and furthermore, if $i\not\in\mathcal A(p_2,z_2)$, then there must exist $u\in\mathbb R^n$ such that
+% \begin{equation}\label{eq:separating_hyperplane}
+% a_i u \geq 0 \quad \text{and} \quad a_j u < 0 \ \ \forall j\in \mathcal A(p_2,z_2).
+% \end{equation}
+Now suppose that $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$.
+In this case (\ref{eq:normal_cone_face_normals}) implies that there must exist $i\in\mathcal A(p_1,z_1)$ such that
+\begin{equation}\label{eq:overlapping_normal_cones}
+a_i = \sum_{j\in\mathcal A(p_2,z_2)} \lambda_j a_j, \quad \lambda_j \geq 0 \ \ \forall j\in\mathcal A(p_2,z_2) ,
+\end{equation}
+%but we must also have $i\not\in\mathcal A(p_2,z_2)$ 
+and if $\mathcal A(p_1,z_1)\cap\mathcal A(p_2,z_2) = \emptyset$, then we must also have $i\not\in\mathcal A(p_2,z_2)$.
+But (\ref{eq:separating_hyperplane}) would then contradict (\ref{eq:overlapping_normal_cones}), and it follows that
+$\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$ 
+only if $\mathcal A(p_1,z_1)\cap\mathcal A(p_2,z_2) \neq \emptyset$.}
 \qed
 \end{proof}
-%
-This allows for efficient numerical treatment, since we know how the vertices are defined, i.e.~$\mathcal A_\kappa = const$.
-%
-We will illustrate how we exploit this property in Section~\ref{sec:computational:methods} and~\ref{sec:numerical:examples}.
+
+\begin{lemma}\label{lem:vert_change}
+\revision{Let $p_i$ for $i=1,2$ be such that the piecewise affine polyhedral map (\ref{eq:definition:PWA:polytopic:set:general}) satisfies $\lvert \vertices(\mathcal W(p)) \rvert = \nu_i$ for some integer $\nu_i$,
+%for all $p$ in an open neighbourhood of $p_i$. 
+for all $p\in U_i\subset Y$, where $U_i$ is an open set containing $p_i$. 
+If $\nu_1\neq \nu_2$ and $\mathcal W(p)$ is generic in the sense of Definition~\ref{def:generic_polyhedral_set}, then $\mathcal W(p)$ cannot be parametrically convex.}
+\end{lemma}
+
+\begin{proof}
+\revision{%
+Under the conditions of the lemma, the number of vertices of $\mathcal W(p)$ must change as $p$ moves along any path in $Y$ from $U_1$ to $U_2$.
+Therefore $\lvert \vertices (\mathcal W(p)) \rvert$ must change at a point $p$ that lies either in the interior of an element, $\mathcal P_j$ $j\in\mathcal I$, of the partition of $Y$, or on a boundary, $\mathcal P_j\cap\mathcal P_k$, for $j,k\in\mathcal I$.
+%
+However the latter case cannot occur if $\mathcal W(p)$ is generic because it would imply a structural instability (since arbitrarily small perturbations in the parameters $a_i,b_{i,k_i^\ast},c_{i,k_i^\ast}$ would cause a change in the combinatorial structure of $\mathcal W(p)$), which is not admissible under Definition~\ref{def:generic_polyhedral_set}.
+%
+On the other hand, if $\lvert \vertices (\mathcal W(p)) \rvert$ changes at a point $p$ in the interior of $\mathcal P_j$, then $\mathscr G(\mathcal W)\vert_{\mathcal P_j}$ is locally a strictly convex polyhedron, and Theorem~\ref{thm:inequalities:convex:concave} implies that $\mathcal W(p)$ cannot be parametrically convex in this case.} \qed
+\end{proof}
+
+The main result of this section is given next.
+% derived from Lemmas~\ref{lem:active_set} and~\ref{lem:vert_change}.
+
+\begin{theorem}\label{thm:p:convexity:PWA:set:constant:num:verts}
+The generic piecewise affine polyhedral map (\ref{eq:definition:PWA:polytopic:set:general})
+is parametrically convex \revision{if and only if there exists an integer $\nu$ such that 
+$\lvert\vertices(\mathcal W(p))\rvert = \nu$
+%$\mathcal W(p)$ has a fixed number of vertices 
+for all $p\in Y$ except a zero measure subset of $Y$.}
+%with the possible exception of a subset of $Y$ of zero measure.}
+\end{theorem}
+%
+
+\begin{proof}
+\revision{
+The necessity of the requirement that the number of vertices of $\mathcal W(p)$ is fixed 
+%for some given $\nu$, $\lvert \vertices\bigl(\mathcal W(p)\bigr) \rvert =\nu$ 
+for all $p\in Y$ (except possibly on a zero measure subset of $Y$) follows directly from Lemma~\ref{lem:vert_change}.
+Sufficiency can be demonstrated using Lemmas~\ref{lem:p:convexity:graph} and~\ref{lem:active_set}.
+Thus if $(p_1,z_1),(p_2,z_2)\in\partial \mathscr G(\mathcal W)$ and $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W} (p_2, z_2) \neq \emptyset$, then Lemma~\ref{lem:active_set} implies that there exists an index, $h$, that belongs to both $\mathcal A(p_1,z_1)$ and $\mathcal A(p_2,z_2)$.
+Expressing $\mathcal W(p)$ as
+\[
+\mathcal W(p) = \{ z : r(p,z) \leq 0\}, \ \ 
+r(p,z) = \max_{i\in\mathbb N_m} \bigl\{ a_i z - \max_{k\in\mathbb N_q} \{ b_{i,k} + c_{i,k} p \} \bigr\},
+\]
+we therefore have $r(p_j,z_j) = a_h z_j - \max_{k\in\mathbb N_q} (b_{h,k} + c_{h,k} p_j ) = 0$ for $j = 1,2$ and
+\begin{align*}
+&r\bigl(\lambda p_1 + (1\!-\!\lambda) p_2, \lambda z_1 + (1\!-\!\lambda) z_2\bigr) \\
+&= 
+\max_{i\in\mathbb N_m} \Bigl\{ a_i \bigl(\lambda z_1 + (1\!-\!\lambda) z_2\bigr) - \max_{k\in\mathbb N_q} \bigl\{ b_{i,k} + c_{i,k}\bigl(\lambda p_1 + (1\!-\!\lambda) p_2\bigr) \bigr\} \Bigr\} \\
+&\geq
+\max_{i\in\mathbb N_m} \Bigl\{  a_i \bigl(\lambda z_1 + (1\!-\!\lambda) z_2\bigr)
+- \lambda \max_{k\in\mathbb N_q} \{ b_{i,k} + c_{i,k} p_1\} 
+- (1\!-\!\lambda) \max_{k\in\mathbb N_q} \{ b_{i,k} + c_{i,k} p_2\} \Bigr\} \\
+&\geq
+\lambda \bigl ( a_h z_1 - \max_{k\in\mathbb N_q} \{ b_{h,k} + c_{h,k} p_1\} \bigr) + (1\!-\!\lambda) \bigl( a_h z_2 - \max_{k\in\mathbb N_q} \{ b_{h,k} + c_{h,k} p_2\} \bigr) \\
+&\geq 0
+\end{align*}
+for all $\lambda\in (0,1)$.
+It follows that $\lambda(p_1,z_1)+(1-\lambda) (p_2,z_2) \notin \interior (\mathscr G(\mathcal W))$ for all $\lambda\in (0,1)$, and hence $\mathcal W(p)$ meets the conditions of Lemma~\ref{lem:p:convexity:graph} for parametric convexity.}
+\qed
+\end{proof}
+
+%
+Theorem~\ref{thm:p:convexity:PWA:set:constant:num:verts} can be reformulated in a computationally useful way as follows.
+%
+\begin{corollary}\label{thm:combinatorical:equivalence:alternative}
+The generic piecewise affine polyhedral map (\ref{eq:definition:PWA:polytopic:set:general})
+is parametrically convex if and only if $\mathcal W(p_1)$ and $\mathcal W(p_2)$ are combinatorially equivalent for all $p_1,p_2\in Y$ except a zero measure subset of $Y$.
+%, i.e.\ $\mathcal W(p_1)\cong\mathcal W(p_2)$.
+\end{corollary}
+%
+\begin{proof}
+Two polyhedra are combinatorially equivalent if there exists a bijection between their faces (vertices, edges, facets, etc) which preserves the inclusion relationships between them, see e.g.~\cite{Ziegler:1995}.
+%
+\revision{It is clear that if the number of vertices of $\mathcal W(p)$ is fixed for all $p\in Y$, then although the shape of~$\mathcal W(p)$ might change, all facets of $\mathcal W(p)$ are defined by the same set of hyperplanes for all $p\in Y$.
+%its combinatorial structure does not.
+%
+The induced graph of a polytope is defined by the vertices and the edges of the polytope, and therefore the induced graph, $G(\mathcal W(p))$, of $\mathcal W(p)$, must be independent of $p$ if $\lvert\vertices(\mathcal W(p))\rvert$ is fixed for all $p\in Y$.
+%
+The Perles Conjecture, as proved in~\cite{Kalai:1988}, shows that the combinatorial structure of a simple polytope is determined uniquely by its induced graph; hence if $G(\mathcal W(p))$ does not vary with $p$, then neither does the combinatorial structure of $\mathcal W(p)$, and it follows that $\mathcal W(p_1)$ and $\mathcal W(p_2)$ are combinatorially equivalent for all $p_1,p_2\in Y$.
+Conversely, if $\lvert\vertices(\mathcal W(p))\rvert$ varies with $p$, then $\mathcal W(p_1)$ and $\mathcal W(p_2)$ cannot be combinatorially equivalent for all $p_1,p_2\in Y$.
+%
+% This is only possible if it is constant itself or it abruptly changes on multiple edges, however changing multiple edges involves changing multiple active sets which is a degenerate case.
+%
+Although the preceding argument ignores the possibility that $\mathcal W(p)$ is non-simple on a zero-measure subset of $Y$, we can define a continuous selection through these sets since the combinatorial structure of $\mathcal W(p)$ is by assumption fixed for values of $p$ arbitrarily nearby.}
+%
+%This means in particular that we ignore the fact that locally $v_{\kappa_1}=v_{\kappa_2}$ and can  use a locally redundant representation $\mathcal W(p) = \conv_\kappa\{v_\kappa(p)\}$.
+\qed
+\end{proof}
+
+%
+Corollary~\ref{thm:combinatorical:equivalence:alternative}
+allows for efficient numerical methods, since combinatorial equivalence for all $p\in Y$ implies that each vertex is defined by a fixed active set independently of $p$.
+%
+Sections~\ref{sec:computational:methods} and~\ref{sec:numerical:examples} illustrate how this property can be exploited computationally.
 %
@@
 %
-We have also seen that for a set-valued map with polyhedral realisations $\mathcal W(p)$, the number of vertices and rays must not change throughout the parameter space~$Y$ in order that $\mathcal W(p)$ is parametrically convex.
+We have also seen that for a set-valued map with polyhedral realisations $\mathcal W(p)$, the number of vertices must not change throughout the parameter space~$Y$ in order that $\mathcal W(p)$ is parametrically convex.
 %
@@
 %
-For notational convenience let $\phi_i(p) = \max_k\{b_{i,k}+c_{i,k}p\}$ denote the right hand side of~\eqref{eq:definition:PWA:polytopic:set:general}, i.e.
+For notational convenience let $\phi_i(p) = \max_{k\in\mathbb N_q}\{b_{i,k}+c_{i,k}p\}$ denote the right hand side of~\eqref{eq:definition:PWA:polytopic:set:general}, i.e.
 $\mathcal W(p) = \{z\in\mathbb R^n: a_i z\leq \phi_i(p)\;\forall i\in\mathbb N_m\}$.
@@
 $$
-	\epi(\phi_i) = \{(p,t)\in Y\times\mathbb R: \phi_i(p)\leq t\}
+	\epi(\phi_i) := \{(p,t)\in Y\times\mathbb R: \phi_i(p)\leq t\}
 $$
@@
 \begin{equation}\label{eq:conv:hull:facet:of:epigraph}
-F_j = \underset{f}{\conv}\left\{\left(\begin{array}{c}p_{j,f}\\ t_{j,f}\end{array}\right)\right\}
-\end{equation}
-%
-of $\epi(\phi_i)$ there exists a maximiser~$k_j$ such that~$\phi_i$ is defined by~$\phi_i(p)=b_{i,k_j}+c_{i,k_j}p$ for all $p\in\pi_d(F_j)$ or equivalently~$\phi_i(p)=\sum_{f}\lambda_f t_{j,f}$ with ${\bf{0}}\leq\lambda\leq{\bf{1}}$ such that $p=\sum_{f}\lambda_f p_{j,f}$.
-%
-Notice that if~\eqref{eq:conv:hull:facet:of:epigraph} is redundant, i.e.
-not all elements are vertices of $F_j$, then the statement is still true, and we can write $\phi_i(p)$ as a convex combination of points.
-
-Let~$\mathcal C$ be a polyhedral complex such that in each $d$-dimensional element~$\mathcal P_j\in\mathcal C$ the set-valued map is given by $\mathcal W(p) = \{z\in\mathbb R^n:a_i z\leq b_{i,k_j} + c_{i,k_k} p\}$.
-%
-It is worth pointing out that any such polyhedral complex is not assumed to be minimal, since the minimal such complex could have non-convex elements, those elements can however be partitioned such that every element of the non-minimal $\mathcal C$ are convex polyhedra.
+F_j = \conv_f \left\{\left(\begin{array}{c}p_{j,f}\\ t_{j,f}\end{array}\right)\right\}
+\end{equation}
+%
+of $\epi(\phi_i)$ there exists a maximiser~$k_j$ such that~$\phi_i$ is defined by~$\phi_i(p)=b_{i,k_j}+c_{i,k_j}p$ for all $p\in\pi_d(F_j)$ or equivalently~$\phi_i(p)=\sum_{f}\lambda_f t_{j,f}$ where the coefficients
+$\lambda_f \in [0,1]$ satisfy 
+% ${\bf{0}}\leq\lambda\leq{\bf{1}}$ 
+$p=\sum_{f}\lambda_f p_{j,f}$ and $\sum_f\lambda=1$.
+%
+%Notice that we can write $\phi_i(p)$ as a convex combination of points even if~\eqref{eq:conv:hull:facet:of:epigraph} is redundant (i.e.~if not every point in the convex combination on the rhs of~\eqref{eq:conv:hull:facet:of:epigraph} is a vertex of $F_j$).
+
+Let~$\mathcal C$ be a polyhedral complex such that in each $d$-dimensional element~$\mathcal P_j\in\mathcal C$ the set-valued map is given by $\mathcal W(p) = \{z\in\mathbb R^n:a_i z\leq b_{i,k_j} + c_{i,k_j} p\}$.
+%
+It is worth pointing out that any such polyhedral complex is not assumed to be minimal, since the minimal complex could have non-convex elements, those elements can however be partitioned so that every element of the non-minimal $\mathcal C$ is a convex polyhedron.
 %
@@
 %
-\begin{equation}
-  E=\left\{(p,t_1,\dots,t_m)\in Y\times\mathbb R^{m}:\phi_i(p)\leq t_i\right\}
-\end{equation}
+\[%\begin{equation}
+  E :=\left\{(p,t_1,\dots,t_m)\in Y\times\mathbb R^{m}:\phi_i(p)\leq t_i\right\}
+\]%\end{equation}
 %
@@
 $$\begin{aligned}
-	\bigcup_{P\in\mathcal C}\text{vert}(P) = \bigcup_{(\ast)} \text{vert}(\pi_d(F)) = \bigcup_{i\in\mathbb N_m}\pi_d(\text{vert}(\epi(\phi_i))),
+	\bigcup_{{P}\in\mathcal C}\vertices({P}) = \bigcup_{(\ast)} \vertices(\pi_d(F)) = \bigcup_{i\in\mathbb N_m}\pi_d(\vertices(\epi(\phi_i))),
 \end{aligned}$$
@@
 %
-It is now obvious that the graph $\mathscr G(\mathcal W\vert_{\mathcal P_j})$ on each $d$-dimensional element $\mathcal P_j\in\mathcal C$ is entirely defined by the values of $\mathcal W(p_j)$ at the vertices $p_j\in\text{vert}(\mathcal P_j)$.
-%
-In each~$\mathcal P_j$ we have $\mathcal W(p) = \{z: a_i z\leq \sum_f \lambda_f t_{i,j,f}, \sum_f\lambda_f p_{j,f}=p, \sum_f\lambda=1,{\bf{0}}\leq\lambda\leq{\bf{1}}\; \forall i\in\mathbb N_m\}$
-%
-Therefore, if~$\mathcal A_\kappa\subset\mathbb N_m$ such that~$\abs{\mathcal A_\kappa}=d$ and $a_\kappa v_\kappa = t_{\kappa,j}$ defines a vertex for $\mathcal W(p_j)$, then $a_\kappa v_\kappa = \sum_f \lambda_f t_{\kappa,f}$ defines a vertex for $\mathcal W(p)$.
-
-The proposed algorithm to determine parametric convexity of a given piecewise affine polyhedral description~$\mathcal W(p)$ as in~\eqref{eq:definition:PWA:polytopic:set:general} can therefore be summarised as follows:
-%
-Firstly, compute all vertices~$\text{vert}(E)$.
-%
-Next, check whether the number of vertices is constant on $\mathcal D = \pi_d\left(\text{vert}(E)\right)$, i.e. 
-%
-$$\abs{\text{vert}(\mathcal W(p))} = c_{\mathcal D} \quad \forall p\in\mathcal D$$
+It is now obvious that the graph $\mathscr G(\mathcal W)\vert_{\mathcal P_j}$ on each $d$-dimensional element $\mathcal P_j\in\mathcal C$ is entirely defined by the values of $\mathcal W(p_j)$ at the vertices $p_j\in\vertices(\mathcal P_j)$.
+%
+In each~$\mathcal P_j$ we have $\mathcal W(p) = \{z: a_i z\leq \sum_f \lambda_f t_{i,j,f}, \sum_f\lambda_f p_{j,f}=p, \sum_f\lambda=1, \lambda_f\in[0,1]\; \forall i\in\mathbb N_m\}$
+%
+Therefore, if~$\mathcal A\subset\mathbb N_m$ such that~$\abs{\mathcal A}=d$ and $a_i v = t_{i,j}$ $\forall i\in\mathcal A$ defines a vertex $v$ of $\mathcal W(p_j)$, then $a_i v = \sum_f \lambda_f t_{i,f}$ $\forall i \in \mathcal A$ defines a vertex $v$ of $\mathcal W(p)$.
+
+The proposed algorithm to determine parametric convexity of a given piecewise affine polyhedral description~$\mathcal W(p)$ as in~\eqref{eq:definition:PWA:polytopic:set:general} can be summarised as follows:
+%
+First, compute all vertices~$\vertices(E)$.
+%
+Next, check whether the number of vertices is constant on $\mathcal D = \pi_d\left(\vertices(E)\right)$, i.e. 
+%
+$$\abs{\vertices(\mathcal W(p))} = c_{\mathcal D} \ \ \forall p\in\mathcal D$$
 %
 for some constant $c_{\mathcal D}$. If this is the case, then
-Corollary~\ref{thm:p:convexity:PWA:set:constant:num:verts} holds and
+Theorem~\ref{thm:p:convexity:PWA:set:constant:num:verts} holds and
 $\mathcal W(p)$ is parametrically convex.
-Furthermore enumerating the vertices of $\mathcal W(p)$ for any fixed $p\in Y$ yields all vertices defining index sets $\mathcal A_\kappa\subset\mathbb N_m$ which remain unchanged for all $p\neq\tilde p\in Y$ according to Corollary~\ref{thm:combinatorical:equivalence:alternative}.
+Furthermore, enumerating the vertices of $\mathcal W(p)$ for any fixed $p\in Y$ yields all vertices defining active sets $\mathcal A\subset\mathbb N_m$ which remain unchanged for all $p\in Y$ according to Corollary~\ref{thm:combinatorical:equivalence:alternative}.
 %
@@
 %
-In particular for the set $S=\{p\in\mathbb R^d:\Lambda_i p\leq\lambda_i,i\in\mathbb N_q\}$ each facet $P_i=\{p:\Lambda_i p=\lambda_i\wedge\Lambda_j p\leq\lambda_j,j\neq i\}$ defines facets of the set difference.
-%
-Namely each point~$p$ on the boundary of $S\ominus\mathcal W(S)$ is such that there exists an admissible $w^\ast$ such that $p+w^\ast$ lies on the boundary of $S$.
-%
-Computing the set $S\ominus\mathcal W(S)$ therefore reduces to computing points~$p$ for which an admissible $w^\ast$ exists to produce~$p+w^\ast\in P_i$ for some $i\in\mathbb N_q$.
-%
-In order to find such points we use the inequality they have to satisfy:
-%
-\begin{equation}\begin{split}
-  \Lambda_i(p+w)\leq\lambda_i\forall w\in\mathcal W(p)\\
+In particular, for the set $S=\{p\in\mathbb R^d:\Lambda_i p\leq\lambda_i \, \forall i\in\mathbb N_q\}$ each facet $P_i=\{p:\Lambda_i p=\lambda_i \wedge \Lambda_j p\leq\lambda_j \, \forall j\neq i\}$ can be used to determine facets of the set difference.
+%
+Namely each point~$p$ on the boundary of $S\ominus\mathcal W(S)$ is such that there exists $w^\ast\in\mathcal W(p)$ so that $p+w^\ast$ lies on the boundary of $S$.
+%
+Computing the set $S\ominus\mathcal W(S)$ therefore reduces to computing points~$p$ for which $w^\ast\in\mathcal W(p)$ exists to produce~$p+w^\ast\in P_i$ for some $i\in\mathbb N_q$.
+%
+In order to find such points we use the inequalities:
+%
+\[%\begin{equation}
+\begin{split}
+  \Lambda_i(p+w)\leq\lambda_i\ \forall w\in\mathcal W(p)\\
   \Lambda_i p+\underbrace{\max_{w\in\mathcal W(p)}\Lambda_i w}_{(\dagger)}\leq\lambda_i
-\end{split}\end{equation}
+\end{split}
+\]%\end{equation}
 %
 The term~$(\dagger)$ is a mpLP, however we are less interested in the
-objective value of~$(\dagger)$ than the shape of its solution
-over~$p$, since this defines the shape of the set of points 
-that can only just be taken to $P_i$ for an extremal value of $w\in\mathcal W(p)$ and hence form the boundary of $S\ominus \mathcal W(S)$.
+objective value of~$(\dagger)$ than the \revision{dependence of its solution
+on~$p$}, since this defines the set of points 
+that can only just be taken to $P_i$ for an extremal value of $w\in\mathcal W(p)$ and thus form the boundary of $S\ominus \mathcal W(S)$.
 %
@@
 %
-\begin{equation}
+\[%\begin{equation}
   \begin{pmatrix}w_1\\ \vdots\\ w_N\end{pmatrix} = \underbrace{\begin{pmatrix}T_1\\ \vdots\\ T_N\end{pmatrix}}_T t(p)
-\end{equation}
-%
-defines all vertices of $\mathcal W(p) = \conv\{w_1(t(p)),\dots,w_N(t(p))\}$ for a element-wise convex piecewise affine function $t(p)$.
+\]%\end{equation}
+%
+defines all vertices of $\mathcal W(p) = \conv\bigl\{w_1(t(p)),\dots,w_N(t(p))\bigr\}$ for an elementwise convex piecewise affine function $t(p)$.
 %
@@
 %
-By including this constraint in~\eqref{eq:rewriting:pontryagin:diff:without:facet:constraint}, we obtain a linear program that is only feasible on the points which can be taken to $P_i$ for feasible $w$:
+By including this constraint in~\eqref{eq:rewriting:pontryagin:diff:without:facet:constraint}, we obtain a linear program that is only feasible on the points which can be taken to $P_i$ for $w\in\mathcal W(p)$:
 %
@@
 %
-\begin{equation}
-  (p,t,\tau)\in\tilde P_i=\left\{(p,t,\tau):\begin{array}{rcl}
+\[%\begin{equation}
+  (p,t,\tau)\in\tilde P_i :=\left\{(p,t,\tau):\begin{array}{rcl}
   \Lambda_iT_jt&\leq&\tau\\
@@
    \right\}
-\end{equation}
+\]%\end{equation}
 %
@@
 %
-The simplest way to use~\eqref{eq:boundary:S:ominus:WS} is to use a vertex description of $\tilde P_i$:
+The simplest way to use~\eqref{eq:boundary:S:ominus:WS} is through a vertex description of $\tilde P_i$:
 %
 \begin{equation}\label{the:way:we:compute:p:pontryagin:differences}
-  \text{vert}(S\ominus\mathcal W(S)) =
-  \bigcup_{i\in\{1,\dots,q\}}\pi_d(\text{vert}(\tilde P_i)) .
+  \vertices(S\ominus\mathcal W(S)) =
+  \bigcup_{i\in\{1,\dots,q\}}\pi_d(\vertices(\tilde P_i)) .
 \end{equation}
@@
 %
-\begin{equation}
-  L = \left\{(p,t,\tau):\begin{array}{rcl}
+\[%\begin{equation}
+  L := \left\{(p,t,\tau):\begin{array}{rcl}
   \Lambda_iT_jt&\leq&\tau_i\\
@@
   \right\} .
-\end{equation}
-%
-The set~$L$ contains all points $p$ for which there exists a feasible $w\in\mathcal W(p)$ such that $p+w\in S$ and hence $\pi_d(L)=S\ominus\mathcal W(S)$, which does not require a vertex enumeration.
+\]%\end{equation}
+%
+This set contains all points $p$ for which there exists $w\in\mathcal W(p)$ such that $p+w\in S$ and hence $\pi_d(L)=S\ominus\mathcal W(S)$, which does not require a vertex enumeration.
 %
@@
 \section{Numerical Examples}\label{sec:numerical:examples}
-\subsection{Norm bound sets}\label{ssec:example:one}
+\subsection{Norm-bound sets}\label{ssec:example:one}
 %
@@
 %
-In fact, we find the~$n$ vertices given by the solution to
+In fact the~$n$ vertices of $\mathcal W(x)$ are  given by the solution of
 %
@@
 
-In order to apply the method described in Section~\ref{ssec:computation:p:pontryagin:difference} we a require map $T$ such that 
+In order to apply the method described in Section~\ref{ssec:computation:p:pontryagin:difference} we require a map $T$ such that 
 %
@@
 %
-holds, but this becomes trivial as $t=\max_{k\leq n} \{F_kx\}$ is a scalar.
-% 
-The sets $\tilde P_i$ and $L$ are given by
+holds, and this becomes trivial as $t=\max_{k\leq n} \{F_kx\}$ is a scalar.
+% 
+The sets $\tilde P_i$ and $L$ are then given by
 %
@@
 
-For the choice~$\kappa=0.2$ and~$n = 35$ the set~$X\ominus\mathcal W(X)=\pi_2(L)=$\linebreak $\conv\{\cup_{i\in\{1,\dots,4\}}\pi_2(\text{vert}(\tilde P_i)\}$ is illustrated in Figure~\ref{fig:example:parametric:pontryagin:difference}.
+For the choice~$\kappa=0.2$ and~$n = 35$ the set~$X\ominus\mathcal W(X)=\pi_2(L)=$\linebreak $\conv\{\cup_{i\in\{1,\dots,4\}}\pi_2(\vertices(\tilde P_i)\}$ is illustrated in Figure~\ref{fig:example:parametric:pontryagin:difference}.
 
@@
 
-\subsection{Elementwise bound sets}\label{exp:second:example}
+\subsection{Elementwise-bound sets}\label{exp:second:example}
 %
@@
 %
-We want to approximate the maximal positive invariant set for a system of the type~$x^+=Ax + f(x)$ for $x\in\mathcal X$, i.e.
-the largest set of points~$\mathcal X^\infty\subseteq\mathcal X$ such that $x\in\mathcal X^\infty\Rightarrow x^+\in\mathcal X^\infty$, see e.g.~\cite{blanchini:2007}.
-%
-For general nonlinear systems~$x^+=Ax + f(x)$ the maximal positive invariant set cannot be calculated, but assume we find piecewise affine bounds on the nonlinearity, i.e.
-$\min_{k\leq M_i}\{h_{i,k}^x x + h_{i,k}^c\}\leq f_i(x)\leq\max_{k\leq N_i}\{H_{i,k}^x x + H_{i,k}^c\}$ for all $x\in\mathcal X$ and all elements of~$f(x)$.
-%
-We can now study the system $x^+=Ax+w$ with $w\in\mathcal W(x) = \{w:\min_{k\leq M_i}\{h_{i,k}^x x + h_{i,k}^c\}\leq w_i\leq\max_{k\leq N_i}\{H_{i,k}^x x + H_{i,k}^c\}\,\forall i\in\mathbb N_d\}$.
-%
-To bound the maximal positive invariant set for the nonlinear system we compute the maximal robust positive invariant set for the perturbed linear system $x^+=Ax+w$, i.e.
+We want to approximate the maximal positive invariant set for a system of the type
+\begin{equation}\label{eq:nonlinear_system}
+x^+=Ax + f(x),
+\end{equation}
+(where $x$ denotes the system state and $x^+$ the successor state)
+for $x\in\mathcal X$, i.e. the largest set of points~$\mathcal X^\infty\subseteq\mathcal X$ such that $x\in\mathcal X^\infty$ implies $x^+\in\mathcal X^\infty$, see e.g.~\cite{blanchini:2007}.
+%
+
+For general nonlinear systems~$x^+=Ax + f(x)$ the maximal positive invariant set cannot be calculated, but assuming piecewise affine bounds on the nonlinearity,
+\[
+\min_{k\leq M_i}\{h_{i,k}^x x + h_{i,k}^c\}\leq f_i(x)\leq\max_{k\leq N_i}\{H_{i,k}^x x + H_{i,k}^c\}
+\] 
+for all $x\in\mathcal X$ and each element of~$f(x)$,
+%
+we can study the system $x^+=Ax+w$ with 
+\[
+w\in\mathcal W(x) = \Bigl\{w:\min_{k\leq M_i}\{h_{i,k}^x x + h_{i,k}^c\}\leq w_i\leq\max_{k\leq N_i}\{H_{i,k}^x x + H_{i,k}^c\}\,\forall i\in\mathbb N_d\Bigr\}.
+\]
+%
+To bound the maximal positive invariant set of the system~(\ref{eq:nonlinear_system}) we compute the maximal robust positive invariant set for the perturbed linear system $x^+=Ax+w$, i.e.
 the set of states~$\mathscr X^\infty\subseteq\mathcal X$ such that $x\in\mathscr X^\infty$ implies $x^+\in\mathscr X^\infty$ for all possible $w\in\mathcal W(x)$.
 %
-The algorithm to determine the maximal robust positive invariant sets recursively intersects the current set iterate~$X_l$ with the set of all possible successor states starting from the current iterate $X_{l+1}=X_l\cap\left\{\bigcup_{x\in X_l,w\in\mathcal W(x)}\{Ax+w\}\right\}$.
-%
-We will only present a single step of this procedure.
-%
-Notice that for a constant set-valued map~$\mathcal W(x) = \mathcal W$ the iteration can be summarised as $X_{l+1} = X_l\cap A^{-1}(X_l\ominus\mathcal W)$, for a set valued map a similar compact notation also holds, however it is more confusing than helpful:~$X_{l+1}=X_l\cap(A^{-1}X_l\ominus A^{-1}\mathcal W(A^{-1}X_l))$.
-
-In order to illustrate the proposed treatment of the nonlinearities we use the two dimensional system~$x^+=x+f(x)$ where the nonlinearity is given by
-%
-\begin{subequations}
-\begin{equation}
-  f_1(x) = \frac{1}{10}\left(\frac{x_1}{2}+x_2\right)^3
-\end{equation}
-\begin{equation}
-  f_2(x) = \frac{1}{2}\arcsin\left(g_1\left(x_1-\frac{x_2}{2}\right)+g_2\left(x_1-\frac{x_2}{2}\right) \right)
-\end{equation}
-\end{subequations}
-%
-with $g_1(t)=\sigma(t)\sqrt{\frac{t}{2}}$, $g_2(t)=\sigma(-t)\frac{t}{2}$ where $\sigma(t)$ denotes the Heaviside function
+The algorithm to determine the maximal robust positive invariant sets recursively intersects the current set iterate~$X_l$ with the set of all possible successor states starting from the current iterate, so that $X_{l+1}=X_l\cap\left\{\bigcup_{x\in X_l,w\in\mathcal W(x)}\{Ax+w\}\right\}$.
+%
+We illustrate the procedure by describing a single iteration of the algorithm.
+%
+% Notice that for a constant set-valued map~$\mathcal W(x) = \mathcal W$ the iteration can be summarised as $X_{l+1} = X_l\cap A^{-1}(X_l\ominus\mathcal W)$, for a set valued map a similar compact notation also holds, however it is more confusing than helpful:~$X_{l+1}=X_l\cap(A^{-1}X_l\ominus A^{-1}\mathcal W(A^{-1}X_l))$.
+
+To demonstrate the proposed treatment of the nonlinearities we use the two-dimensional system~$x^+=x+f(x)$, where the nonlinearity is given by $f = [f_1 \ \ f_2]^\top$,
+%
+%\begin{subequations}
+\begin{align*}
+  f_1(x) &= \frac{1}{10}\left(\frac{x_1}{2}+x_2\right)^3 \\
+  f_2(x) &= \frac{1}{2}\arcsin\left(g_1\left(x_1-\frac{x_2}{2}\right)+g_2\left(x_1-\frac{x_2}{2}\right) \right)
+\end{align*}
+%\end{subequations}
+%
+with $g_1(t)=\sigma(t)\sqrt{\frac{t}{2}}$, $g_2(t)=\sigma(-t)\frac{t}{2}$ where $\sigma(t)$ denotes the Heaviside function.
 %\sigma\left(x_1-\frac{x_2}{2}\right)\sqrt{\frac{x_1-\frac{x_2}{2}}{2}} + \sigma\left(-\left(x_1-\frac{x_2}{2}\right)\right)\frac{x_1-\frac{x_2}{2}}{2}
-$$
-  \sigma(t) = \left\{\begin{array}{crcl}1& t&\geq&0\\ 0 &t&<&0 \end{array}\right.
-$$
+\[
+  \sigma(t) = \begin{cases} 1 & t \geq 0 \\ 0 & t < 0 \end{cases}
+%\left\{\begin{array}{crcl}1& t&\geq&0\\ 0 &t&<&0 \end{array}\right.
+\]
 %
@@
 %
-with $t_1=\max_k\{H_{1,k}^x x+H_{1,k}^c\},\; t_3=\max_k\{H_{2,k}^x x+H_{2,k}^c\},\; t_2=-\max_k\{-h_{1,k}^x x-h_{1,k}^c\}$ and $t_4=-\max_k\{-h_{1,k}^x x-h_{1,k}^c\}$.
+with $t_1=\max_k\{H_{1,k}^x x+H_{1,k}^c\}$, $t_3=\max_k\{H_{2,k}^x x+H_{2,k}^c\}$, $t_2={-\max_k}\{-h_{1,k}^x x-h_{1,k}^c\}$ and $t_4={-\max_k}\{-h_{1,k}^x x-h_{1,k}^c\}$.
 %
@@
 \begin{equation}
-\Lambda_i(Ax+w^\ast)=\lambda_i\quad \Lambda_j(Ax+w^\ast)\leq\lambda_j,j\neq i
-\end{equation}
-%
-where $w^\ast$ is the maximiser of the defining mpLP $\max_{w\in\mathcal W(x)}\Lambda_iw$, i.e. one of the aforementioned vertices with their representation
+\Lambda_i(Ax+w^\ast)=\lambda_i, \quad \Lambda_j(Ax+w^\ast)\leq\lambda_j \ \forall j\neq i ,
+\end{equation}
+%
+where $w^\ast$ is the maximiser of the defining mpLP $\max_{w\in\mathcal W(x)}\Lambda_iw$, i.e.~one of the vertices defined by
 %
@@
 %
-With this the collection of facets generated by~$P_i$ is given by the projection
+The collection of facets generated by~$P_i$ is then given by the projection
 %
@@
 %
-Analogously to the previous example, instead of computing~$q$ projections from $3d+1$ onto $d$ we can perform a single projection with the same result:
+Analogously to the previous example, rather than computing~$q$ projections from $\mathbb R^{3d+1}$ onto $\mathbb R^d$, we can perform a single projection with the same result:
 %
@@
 %
-The resulting set for this 2 dimensional example is illustrated in Figure~\ref{fig:second:example:resulting:set}.
+The resulting set for this two-dimensional example is illustrated in Figure~\ref{fig:second:example:resulting:set}.
 
@@
 %
-\section{Conclusion}\label{sec:conclusion}
+\section{Conclusions}\label{sec:conclusion}
 %
@@
 %
-Using two simple examples we illustrated the potency of the proposed methodology.
-
-The parametric Pontryagin difference has been applied successfully in a robust control environment~\cite{Schaich:2015,Schaich:2015a} and this work will further to extend its scope of application.
+Using two simple examples we illustrate the potency of the proposed methodology.
+
+The parametric Pontryagin difference has been used successfully in robust control applications~\cite{Schaich:2015,Schaich:2015a} and this work will further extend its scope of application.
 

### 2018-03-30 ThmAboutRank1.tex
added file

\documentclass[a4paper]{scrartcl}

\usepackage[english]{babel}
\usepackage{amsmath,amssymb,amsthm,hyperref,graphicx,lpic,xcolor}
\usepackage[left=20mm,top=20mm,right=20mm,bottom=25mm]{geometry}
\usepackage{hyperref}
% \usepackage{showkeys}
\hypersetup{pdfauthor={Manuel Schaich}}

\usepackage{tikz}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning,patterns,decorations.pathreplacing,calc,shapes.geometric}

\tikzset{
    at xy split/.style 2 args={
        at={(#1,#2)}
    },
    a/.style={circle, draw=red},`'
    b/.style={rectangle, draw=blue}
}
\tikzset{myrad/.style 2 args={circle,inner sep=0pt,minimum width=(2*(sqrt(#1)*1 pt ) - \pgflinewidth,fill=#2,draw=#2,fill opacity=.5,opacity=.8}}
\usepackage{tikz-3dplot}
\usepackage{pgfplots}
\pgfplotsset{compat=1.7}

\graphicspath{{./Pix/}}
\pagestyle{plain}

\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
\DeclareFontShape{U}{mathx}{m}{n}{
      <5> <6> <7> <8> <9> <10> gen * mathx
      <10.95> mathx10 <12> <14.4> <17.28> <20.74> <24.88> mathx12
      }{}
\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
\DeclareFontSubstitution{U}{mathx}{m}{n}
\DeclareMathSymbol{\temp}{\mathbin}{mathx}{'341}
\newcommand{\bigominus}{\raisebox{10pt}{$\temp$}}

\providecommand{\norm}[1]{\left\|#1\right\|}
\providecommand{\abs}[1]{\left|#1\right|}
\providecommand{\span}{\text{span}}
\providecommand{\conv}{\text{conv}}
\providecommand{\ext}{\text{ext}}
\providecommand{\rank}{\text{rank}}

\providecommand{\revision}{}

\newtheorem{theorem}{Theorem}

\begin{document}

Currently, we have:

\begin{theorem}\label{thm:polytopic:set:not:p:convex}
  The polyhedral parametric set-valued map $\mathcal W(p):=\{z\in \mathbb R^n : a_i z \leq b_i  + c_i p \; \forall i\in\mathbb N_m\}$, 
  where $a_i\in\mathbb R^{1\times n}$, $b_i \in \mathbb R$ and $c_i \in \mathbb R^{1\times d}$ for 
  $i\in\mathbb N_m$ are given parameters, is necessarily parametrically convex if $C=0$ and cannot 
  be parametrically convex if $\rank( C ) > 1$, where 
  $C = (\begin{matrix} c_1^\top & \cdots & c_m^\top\end{matrix})^\top.$
% and only if the matrix $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$ is such that $\rank(B) \leq 1$.}
%is not parametrically convex for any $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$ such that $\rank (B) >1$.}
\end{theorem}

Consider the polytope
%
\[
	P = \{x\in\mathbb R^3: Ax\leq\mathbf{1}\}
\]
%
with
%
\[
	A = \begin{pmatrix} I_2 & \mathbf{1} \\
						-I_2 & \mathbf{1} \\
						I_2 & -\mathbf{1} \\
						-I_2 & -\mathbf{1}
						\end{pmatrix}
\]
%
I.e. the polytope illustrated in Figure~\ref{fig:P},
%
\begin{figure}
\centering
\tdplotsetmaincoords{65}{40}
\begin{tikzpicture}[tdplot_main_coords,scale=2]

\draw[blue] (  0.0000,   0.0000,   1.0000) -- (  1.0000,  -1.0000,   0.0000) -- (  1.0000,   1.0000,   0.0000) -- (  0.0000,   0.0000,   1.0000) -- cycle;

\draw[blue] (  0.0000,   0.0000,   1.0000) -- (  1.0000,   1.0000,   0.0000) -- ( -1.0000,   1.0000,   0.0000) -- (  0.0000,   0.0000,   1.0000) -- cycle;

\draw[blue] ( -1.0000,  -1.0000,   0.0000) -- ( -1.0000,   1.0000,   0.0000) -- (  0.0000,   0.0000,   1.0000) -- ( -1.0000,  -1.0000,   0.0000) -- cycle;

\draw[blue] ( -1.0000,  -1.0000,   0.0000) -- (  1.0000,  -1.0000,   0.0000) -- (  0.0000,   0.0000,   1.0000) -- ( -1.0000,  -1.0000,   0.0000) -- cycle;

\draw[blue] (  0.0000,   0.0000,  -1.0000) -- (  1.0000,   1.0000,   0.0000) -- (  1.0000,  -1.0000,   0.0000) -- (  0.0000,   0.0000,  -1.0000) -- cycle;

\draw[blue] (  0.0000,   0.0000,  -1.0000) -- ( -1.0000,   1.0000,   0.0000) -- (  1.0000,   1.0000,   0.0000) -- (  0.0000,   0.0000,  -1.0000) -- cycle;

\draw[blue] (  0.0000,   0.0000,  -1.0000) -- ( -1.0000,   1.0000,   0.0000) -- ( -1.0000,  -1.0000,   0.0000) -- (  0.0000,   0.0000,  -1.0000) -- cycle;

\draw[blue] (  0.0000,   0.0000,  -1.0000) -- (  1.0000,  -1.0000,   0.0000) -- ( -1.0000,  -1.0000,   0.0000) -- (  0.0000,   0.0000,  -1.0000) -- cycle;
\end{tikzpicture}
\caption{Polytope $P$.}\label{fig:P}
\end{figure}
%
clearly not parametrically convex when considering $z = (x_1,x_2)$ and $p = x_3$.
%
However, Theorem~\ref{thm:polytopic:set:not:p:convex} is satisfied.
%
Now consider the polytope $P_2 = \{x\in\mathbb R^4:-1\leq x_{1/2}+x_{3/4}\leq 1\}$, and consider $z=(x_1,x_2)$ and $p=(x_3,x_4)$ with $-\frac{1}{2}\leq p_{1/2}\leq \frac{1}{2}$.
%
This means 
%
\[
A = \begin{pmatrix}1& \\ &1 \\ -1& \\ &-1\end{pmatrix}, C = \begin{pmatrix} -1& \\ &-1  \\ 1& \\ &1\end{pmatrix}
\]
% 
For this particular choice we can write the vertex description of $W(p)$ as
%
\[
	W(p) = \conv \left\{ \begin{pmatrix}\pm(1-p_1)\\\pm (1-p_2)\end{pmatrix},\begin{pmatrix}\mp(1-p_1)\\\pm (1-p_2)\end{pmatrix}\right\}
\]
%
Therefore, $\rank(C)=2>1$ and Theorem~\ref{thm:polytopic:set:not:p:convex} claims that $W(p)$ is not parametrically convex. 
%
However, it is. 
%
For any subset of $p\in Y\subset \{p:-1<p_{1/2}<1\}$. 
%
It is a quite unexciting parametrically convex set-valued map but it is parametrically convex nevertheless, in particular $W(\lambda p_1) \oplus W((1-\lambda)p_2) = W(\lambda p_1+(1-\lambda)p_2)$.
%
\\[2em]
%
I think that in order to make a precise and useful statement we have to drop the notion of the explicit representation of $W(p)$ and use something along the lines of
%
\begin{theorem}
Let $P\subset Y\times Z$ be a polytope defined by
%
\[
	P = \{(p,z):Cp+Az\leq\mathbf{1}\}
\] 
%
and let 
%
\[
H_i = \{v\in\mathbb R^{d+n}h_iv=1\}, i\in\{1,\dots,t\}
\]
be its supporting hyperplanes.
%
The set-valued map $W(p) = \{z\in Z:Az\leq\mathbf{1}-Cp\}$ is parametrically convex iff all hyperplanes $H_i$ support $P$ on the entire set $Y\times Z$, i.e. $H_i\cap (Y\times Z) = H_i\cap P$.
\end{theorem}
%
The parametrically convex part of this statement follows pretty much immediately, however, it does exactly what we want, i.e. it excludes polytopes that have vertices in $p$ and has no condition on the rank of $C$.
%
On the other hand this seems quite abstract.
%
\\[2em]
%
The statement that used to follow with the three part proof that was not very well formulated I would have treated as you have and split it into smaller statements.
%
\end{document}
